---
title: "The Honda was cheap but the coffee was expensive: Validating comparison classes for vague language understanding"
bibliography: [comparison-class.bib, library.bib]
csl: "apa6.csl"
document-params: "10pt, letterpaper"

author-information: > 
    \author{{\large \bf Author 1} \\ \texttt{author1@university.edu} \\ Department of Psychology \\ Some University
    \And {\large \bf Author 2} \\ \texttt{author1@university.edu} \\ Department of Psychology \\ Some University}

abstract: 
    "The abstract should be one paragraph, indented 1/8 inch on both sides,
in 9 point font with single spacing. The heading Abstract should
be 10 point, bold, centered, with one line space below it. This
one-paragraph abstract section is required only for standard spoken
papers and standard posters (i.e., those presentations that will be
represented by six page papers in the Proceedings)."
    
keywords:
    "Add your choice of indexing terms or keywords; kindly use a semi-colon; between each term."
    
output: cogsci2016::cogsci_paper
---

```{r global_options, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(fig.width=3, fig.height=3, fig.crop = F, fig.pos = "tb", fig.path='figs/',
                      echo=F, warning=F, cache=F, message=F, sanitize = T)
```

```{r, libraries}
library(png)
library(grid)
library(ggplot2)
library(xtable)
library(tidyr)
library(dplyr)
library(rwebppl)
```

# Proposal

How can a cup of coffee be expensive while cheap cars populate the highways?
Adjectives like *cheap* and *expensive*, *cold* and *hot*, *tall* and *short* are vague descriptions of an underlying (quantitative) measure (e.g., price, temperature).
Vague language is ubiquitous in everyday conversation; much more common than actually saying numeric values...

Contemporary linguistic theories posit that the truth-conditional semantics of such vague utterances are simple thresholds on the measure.
For example, a cup of coffee is expensive if its price is greater than some number of dollars.
The crux of such arguments rest of the fact that this threshold is relative to some *comparison class* of other possible entities. 
For example, a cup of coffee can be expensive *relative to* other possible cups of coffee, or perhaps hot beverages sold at a local coffee shop.

@Lassiter2013 showed how this idea can be couched in a general pragmatic theory of language understanding.
In this Rational Speech Act theory, the truth-conditional threshold comes from an uninformative prior distribution (a flat distribution over all possible thresholds).
Listeners arrive at context-sensitive meanings by integrating their prior beliefs with general principles of communication (be truthful, be informative). 
The result is vague language understanding that displays context-sensitivity and admits borderline cases[@Lassiter2013; @Lassiter2015]. In this formal theory, the *comparison class* is assumed in the specification of a listener's prior belief distribution.

The comparison class can depend upon the target object (as in the examples above) as well as the physical context or the Question Under Discussion.
@Ebeling1994 demonstrate that 2-4 year olds understand the context-sensitivity of the words "big" and "little", finding the appropriate object whether the object is in a physical context ("big" compared to other objects in a scene), is in a functional context ("big" compared to its intended use), or out of context ("big" relative to a comparison class). 

In this paper we introduce a free-response paradigm for eliciting comparison classes for gradable adjectives.
We validate this technique by measuring listeners' prior belief distributions over the measure within the elicited comparison class (e.g., the price of cups of coffee).
By measuring a comparison class and a corresponding prior belief distribution, we can derive predictions for adjective interpretation across different contexts using the Rational Speech Act model.
We then test these predictions using a listener interpretation task.

# Outline 

## Experiments

See all the items [here](http://stanford.edu/~mtessler/comparison-class/experiments/js/examples-2.js), or see the listener experiment (with all the items) [here](http://stanford.edu/~mtessler/comparison-class/experiments/listener-1.html).

\begin{enumerate}

\item Stimuli
  \subitem Currently we have 40 unique items, made up of 6 scales x 2 (positive and negative form adjectives)
  \subitem Note we are using temperature that is perceived both through touching and temperature that is perceived in the whole body (so, touching objects vs. the weather). For the weather, it is really about speaker's beliefs (their own subjective comparison class; e.g. John think its cold because he's from southern california)
  \subitem 3 or 4 contexts by item (different targets of reference)
  \subitem Example: Gary buys a [television, book, iPhone] and picks it up. He says, ``This is heavy.'' 

\item \textbf{Comparison class elicitation}
  \subitem We've run a pilot using the paraphrase technique with the helper phrases "for a" and "relative to". "For a" produced more reliable results, so we'll use that going forward.
  \subitem Example: Gary buys a television and picks it up. He says, ``This is heavy.'' 
  \subitem \textbf{Dependent measure}: What do you think Gary meant? ... `` This is heavy \textbf{for a} ...'' (fill in the blank)
  \subitem \textbf{Data analysis}: Take modal response, or top 2, and use those in the prior elicitation task.

\item \textbf{Prior elicitation}
  \subitem This will refer to the comparison class. 
  \subitem \textbf{Dependent measure}: What do you think is the weight of a television? Provide number and units (units from a set from a drop-down menu).

\item \textbf{Language understanding (Listener task)}
  \subitem Same stimuli as the comparison class elicitation.
  \subitem \textbf{Dependent measure}: same as prior elicitation.

\end{enumerate}

# Model 

uRSA with lifted variable. 
Plug in different priors.

# Data anlaysis

Probably something similar to the habituals paper. 
Assume log-normals, do BDA on the prior data.

# Current concerns

\begin{enumerate}

\item In the Justine-way of doing these kinds of experiments, for the prior elicitation, we would have the same context sentence (``Gary buys a television and picks it up.'') without the adjective sentence, and ask about the likely weight.
What does our intermediate comparison class elicitation step buy us?

\item For many of the our items, it seems that the comparison class we're going to get is the class of the target objects (e.g., televisions, cups of coffee, weather in Southern California)... I have the feeling that some items (e.g., a 30 year old who is tall) have more general classes (e.g., tall for an adult, for a woman) while others (e.g., a 4 year old boy who is tall) have more specific classes (i.e., tall for a 4 year old). This example may be unique / idiosyncractic, but also may suggest that the comparison class needs to be a relative homogeneous category (e.g., 4 year olds are really different than 2 year olds, whereas 30 vs. 28 year olds not so much). If this is interesting, should we try to move our stimuli more in that direction? Any thoughts? 

\end{enumerate}




# First-Level Headings

For general information about authoring in markdown, see **[here](http://rmarkdown.rstudio.com/authoring_basics.html).**

First level headings should be in 12 point , initial caps, bold and
centered. Leave one line space above the heading and 1/4~line space
below the heading.

## Second-Level Headings

Second level headings should be 11 point , initial caps, bold, and
flush left. Leave one line space above the heading and 1/4~ line
space below the heading.

### Third-Level Headings

Third-level headings should be 10 point , initial caps, bold, and flush
left. Leave one line space above the heading, but no space after the
heading.

# Formalities, Footnotes, and Floats

Use standard APA citation format. Citations within the text should
include the author's last name and year. If the authors' names are
included in the sentence, place only the year in parentheses, as in
[-@NewellSimon1972a], but otherwise place the entire reference in
parentheses with the authors and year separated by a comma
[@NewellSimon1972a]. List multiple references alphabetically and
separate them by semicolons [@ChalnickBillman1988a; @NewellSimon1972a]. 
Use the et. al. construction only after listing all the authors to a
publication in an earlier reference and for citations with four or
more authors.

For more information on citations in R Markdown, see **[here](http://rmarkdown.rstudio.com/authoring_bibliographies_and_citations.html#citations).**

## Footnotes

Indicate footnotes with a number\footnote{Sample of the first
footnote.} in the text. Place the footnotes in 9 point type at the
bottom of the page on which they appear. Precede the footnote with a
horizontal rule.\footnote{Sample of the second footnote.}

## Figures

All artwork must be very dark for purposes of reproduction and should
not be hand drawn. Number figures sequentially, placing the figure
number and caption, in 10 point, after the figure with one line space
above the caption and one line space below it. If necessary, leave extra white space at
the bottom of the page to avoid splitting the figure and figure
caption. You may float figures to the top or bottom of a column, or
set wide figures across both columns.

## Two-column images

You can read local images using png package for example and plot 
it like a regular plot using grid.raster from the grid package. 
With this method you have full control of the size of your image. **Note: Image must be in .png file format for the readPNG function to work.**

You might want to display a wide figure across both columns. To do this, you change the `fig.env` chunk option to `figure*`. To align the image in the center of the page, set `fig.align` option to `center`. To format the width of your caption text, you set the `num.cols.cap` option to `2`.

```{r 2-col-image, fig.env = "figure*", fig.pos = "h", fig.width=4, fig.height=2, fig.align = "center", set.cap.width=T, num.cols.cap=2, fig.cap = "This image spans both columns. And the caption text is limited to 0.8 of the width of the document."}
img <- png::readPNG("figs/walrus.png")
grid::grid.raster(img)
```

## One-column images

Single column is the default option, but if you want set it explicitly, set `fig.env` to `figure`. Notice that the `num.cols` option for the caption width is set to `1`.

```{r image, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=2, fig.height=2, set.cap.width=T, num.cols.cap=1, fig.cap = "One column image."}
img <- png::readPNG("figs/lab_logo_stanford.png")
grid::grid.raster(img)
```


## R Plots

You can use R chunks directly to plot graphs. And you can use latex floats in the
fig.pos chunk option to have more control over the location of your plot on the page. For more information on latex placement specifiers see **[here](https://en.wikibooks.org/wiki/LaTeX/Floats,_Figures_and_Captions)**

```{r plot, fig.env="figure", fig.pos = "H", fig.align = "center", fig.width=2, fig.height=2, fig.cap = "R plot" }
x <- 0:100
y <- 2 * (x + rnorm(length(x), sd = 3) + 3)

ggplot2::ggplot(data = data.frame(x, y), 
       aes(x = x, y = y)) + 
  geom_point() + 
  geom_smooth(method = "lm")
```


## Tables

Number tables consecutively; place the table number and title (in
10 point) above the table with one line space above the caption and
one line space below it, as in Table 1. You may float
tables to the top or bottom of a column, set wide tables across both
columns.

You can use the xtable function in the xtable package.

```{r xtable, results="asis"}
n <- 100
x <- rnorm(n)
y <- 2*x + rnorm(n)
out <- lm(y ~ x)

tab1 <- xtable::xtable(summary(out)$coef, digits=c(0, 2, 2, 1, 2), 
                      caption = "This table prints across one column.")

print(tab1, type="latex", comment = F, table.placement = "H")
```

# Acknowledgements

Place acknowledgments (including funding information) in a section at
the end of the paper.

# References 

```{r}
# References will be generated automatically by Pandoc and included here.
# The following code is some latex to format the bibliography. Do not remove it.
```

\setlength{\parindent}{-0.1in} 
\setlength{\leftskip}{0.125in}
\noindent
