```{r}
# Load libraries.
library(knitr)
library(ggplot2)
```

```{r}
# Print data from adjective-elicitation-1 (with supercategories).
path_to_repository = "D:/Research/comparison-class"
data = read.csv(paste(path_to_repository, 
                      "/analysis/adjective-elicitation-1-supercategories.csv",
                      sep=""))
kable(data)
```

```{r fig.height=36, fig.width=20}
# Print distributions of supercategories for each degree.
ggplot(data, aes(x=supercategory, fill=adjective_form)) + geom_bar() + 
  facet_wrap(~degree, scales="free", nrow=4) + 
  theme(text=element_text(size=24), axis.text.x=element_text(angle=45, hjust=1.0, vjust=1.0))
```

# Supercategory Selection

The max supercategory in each degree tends to be the max by a large margin, so I usually chose those supercategories. I deviated from picking the max in the "weight" degree to avoid having "animals" as the supercategory for two degrees. For the "sound" degree, "public places" might need a different name. It's an extremely popular category but I couldn't think of a more apt name.

| Degree      | Supercategory    |
|-------------|------------------|
| Darkness    | time of day      | 
| Height      | people           |
| Price       | food             |
| Size        | animals          |
| Sound       | public places    |
| Temperature | seasons          |
| Time        | things you watch |
| Weight      | office supplies  |

# Subcategory Selection

```{r}
supercategories = c("time of day", "people", "food", "animals", "public places", "season", 
                    "things you watch", "office supplies")
data %>% 
  group_by(degree, supercategory) %>%
```
