---
title: "Adjective Elicitation"
author: "Michael Lopez-Brau"
date: "April 16, 2018"
---

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Load libraries.
library(knitr)
library(tidyverse)
```

## Updated Results

Manually categorized participant responses into supercategories.

```{r echo=FALSE}
path_to_repository = "D:/Research/comparison-class"
data = read.csv(paste(path_to_repository, 
                      "/analysis/adjective-elicitation-1-supercategories.csv",
                      sep=""))
kable(data)
```

## Plots

Plotted the distribution of supercategories for each degree.

```{r echo=FALSE, fig.height=36, fig.width=20}
ggplot(data, aes(x=supercategory, fill=adjective_form)) + geom_bar() + 
  facet_wrap(~degree, scales="free", nrow=4) + 
  theme(text=element_text(size=24), axis.text.x=element_text(angle=45, hjust=1.0, vjust=1.0))
```

# Supercategory Selection

The max supercategory in each degree tends to be the max by a large margin, so I usually chose those supercategories. I deviated from picking the max in the "weight" degree to avoid having "animals" as the supercategory for two degrees. For the "sound" degree, "public places" might need a different name. It's an extremely popular category but I couldn't think of a more apt name.

| Degree      | Supercategory    |
|-------------|------------------|
| darkness    | times of day     | 
| height      | people           |
| price       | food             |
| size        | animals          |
| sound       | public places    |
| temperature | seasons          |
| time        | things you watch |
| weight      | sports equipment |

# Subcategory Selection

List all of the responses (with some minor filtering). Below are the subcategories I chose: three per degree (one per adjective form) for a total of 24 subcategories.

```{r echo=FALSE, eval=FALSE}
supercategories = c("times of day", "people", "food", "animals", "public places", "seasons", 
                    "things you watch", "sports equipment")
data %>% 
  group_by(degree, supercategory) %>%
  filter(supercategory %in% supercategories) %>%
  arrange(degree, adjective, supercategory) %>%
  kable()
```

| Degree      | Subcategory (negative) | Subcategory (positive) | Subcategory (neutral) |
|-------------|------------------------|------------------------|-----------------------|
| darkness    | nights                 | days                   | evenings              |
| height      | kids                   | adults                 | teenagers             |
| price       | hot dogs               | steak                  | pork chops            |
| size        | ants                   | whales                 | dogs                  |
| sound       | libraries              | concerts               | offices               |
| temperature | Winter days            | Summer days            | Spring days           |
| time        | music videos           | movies                 | TV shows              |
| weight      | ping pong ball         | bowling ball           | basketball            |
