---
title: "Comparison class elicitation (final, preregistered)"
author: "MH Tessler"
date: "October 29, 2019"
---

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Load libraries.
library(knitr)
library(tidyverse)
library(jsonlite)
library(tidyboot)
library(tidytext)
library(lme4)
library(ggthemes)
library(brms)
library(stringr)
theme_set(theme_few())

# extended function to check matching between strings either way
containsString_responses <- function(strng, substrng, clean_str, us_substr) {
  return(ifelse(length(strsplit(strng, substrng)[[1]]) > 1, 1,
    ifelse(length(strsplit(us_substr, clean_str)[[1]]) > 1, 1, 0)
  ))
}
containsString <- function(strng, substrng) {
  return(ifelse(length(strsplit(strng, substrng)[[1]]) > 1, 1,
    ifelse(length(strsplit(substrng, strng)[[1]]) > 1, 1, 0)
  ))
}

my_stop_words <- stop_words %>%
  rowwise() %>%
  subset(!(stop_words$word %in% c(
    "rooms", "year", "years", "side", "sides", "area",
    "of", "up", "great", "things", "places", "thing",
    "room", "areas", "part", "parts", "works", "way", "ways",
    "-", "show", "shows", "goods", "novel", "back"
  )))
```

### Load data


```{r load data from json, eval = F}
data.path <- "../mturk/class-elicitation-prereg-final/production-results/"
result.files <- list.files(data.path, pattern = "json")

df.subject <- data.frame()
df.trials <- data.frame()
df.attention <- data.frame()
for (result_file in result.files) {
  result_json <- fromJSON(paste(data.path, result_file, sep = "/"))
  worker.id <- paste("workerid_", str_pad(match(result_file, result.files), 4, pad = "0"), sep = "")
  #  result_json$WorkerId
  condition <- result_json$answers$condition

  df.attention <- bind_rows(
    df.attention,
    data.frame(result_json$answers$catch_trials) %>%
      mutate(workerid = worker.id)
  )

  df.subject <- bind_rows(
    df.subject,
    data.frame(result_json$answers$subject_information) %>%
      mutate(
        workerid = worker.id,
        language = gsub("\"", "", language),
        enjoyment = gsub("\"", "", enjoyment),
        age = gsub("\"", "", age),
        gender = gsub("\"", "", gender),
        problems = gsub("\"", "", problems),
        comments = gsub("\"", "", comments)
      )
  )

  df.trials <- bind_rows(
    df.trials,
    data.frame(result_json$answers$trials) %>%
      mutate(workerid = worker.id)
  )
}


df.trials %>%
  group_by(workerid) %>%
  count() %>%
  group_by(n) %>%
  count()



# write_csv(df.trials, "../data/class-elicitation-prereg-final/class-elicitation-prereg-final-trials.csv")
# write_csv(df.subject, "../data/class-elicitation-prereg-final/class-elicitation-prereg-final-subject_information.csv")
# write_csv(df.attention, "../data/class-elicitation-prereg-final/class-elicitation-prereg-final-catch_trials.csv")
```


```{r load data from csv}
df.trials <- read_csv("../data/class-elicitation-prereg-final/class-elicitation-prereg-final-trials.csv")
df.subject <- read_csv("../data/class-elicitation-prereg-final/class-elicitation-prereg-final-subject_information.csv")
df.attention <- read_csv("../data/class-elicitation-prereg-final/class-elicitation-prereg-final-catch_trials.csv")
# df.frequencies <- read_csv("../data/pilot-classElicitation-free-4/webgram-freqs-unique-nps.csv")
```


### Exclusion criteria

```{r}

df.botcaptcha <- df.attention %>%
  filter(condition == "botcaptcha")

df.comprehension <- df.attention %>%
  filter(condition == "warm_up") %>%
  rowwise() %>%
  mutate(pass_comp = (
    containsString(tolower(response), "build") |
      containsString(tolower(response), "bulid") |
      containsString(tolower(response), "buid") |
      containsString(tolower(response), "skyscraper") |
      containsString(tolower(response), "skyscaper") |
      containsString(tolower(response), "structure") |
      containsString(tolower(response), "bulding") |
      containsString(tolower(response), "builing") |
      containsString(tolower(response), "bildin") |
      containsString(tolower(response), "towe")
  ))

# df.comprehension %>%
#   filter(!pass_comp) %>%
#   View()

df.memory <- df.attention %>%
  filter(condition == "memory_check") %>%
  group_by(workerid) %>%
  summarize(
    n_correct = sum(correct),
    pass_memory = n_correct >= 7
  )
```

```{r}
df.memory %>%
  group_by(n_correct) %>%
  count()
```
Participants are excluded if they answer less than 7 out of 10 memory check questions correctly or if they respond incorrectly on the warm-up trials.
```{r summarize catch trials}
df.attention.summary <- left_join(
  df.comprehension %>% select(workerid, pass_comp),
  df.memory %>% select(workerid, pass_memory)
) %>%
  mutate(pass_both = pass_comp & pass_memory)


df.attention.summary %>%
  group_by(pass_comp, pass_memory, pass_both) %>%
  count()
```



## Response processing


For automated checking of whether or not responses contain the supplied NP, we distill multi-word NPs (e.g., "six-pack of beer") to single words (e.g., "beer") that we think convey the essence of the subordinate category given the context. And so, if we see a response containing the word "beer", then it will be marked as *specific* (i.e., including the mentioned NP). One exception is that we excluded responses that used the word "similar"; we deemed these responses too underspecified/ambiguous (how similar is similar?). Just to confirm, in addition, we hand-check all responses. 

```{r filtered main trails}
df.trials.filtered <- df.trials %>%
  left_join(., df.attention.summary) %>%
  filter(pass_both) %>%
  rowwise() %>%
  mutate(
    np_match = tolower(np), # additional column where we put the NP to be matched against, such that the original NPs can be accessed if necessary
    np_match = gsub("bottle of top-shelf liquor", "liquor", np_match),
    np_match = gsub("piece of chocolate", "chocolate", np_match),
    np_match = gsub("piece of chalk", "chalk", np_match),
    np_match = gsub("six-pack of beer", "beer", np_match),
    np_match = gsub("bottle of wine", "wine", np_match),
    np_match = gsub("pine tree", "pine", np_match),
    np_match = gsub("redwood tree", "redwood", np_match),
    np_match = gsub("alpine tree", "alpine", np_match),
    np_match = gsub("bonsai tree", "bonsai", np_match),
    np_match = gsub("pick-up truck", "pick-up", np_match),
    np_match = gsub("relay race", "relay", np_match),
    np_match = gsub("triathlon race", "triathlon", np_match),
    np_match = gsub("sprinting race", "sprint", np_match),
    np_match = gsub("kettle ball", "ball", np_match),
    np_match = gsub("study hall", "study", np_match),
    np_match = gsub("electric car", "electric", np_match),
    np_match = gsub("bass guitar", "bass", np_match),
    np_match = gsub("choral concert", "choral", np_match),
    np_match = gsub("rap concert", "rap", np_match),
    np_match = gsub("white paint", "white", np_match),
    np_match = gsub("blue paint", "blue", np_match),
    np_match = gsub("black paint", "black", np_match),
    np_match = gsub("limousine", "limo", np_match),
    np_match = gsub("smartcar", "smart", np_match),
    np_match = gsub("japanese restaurant", "japanese", np_match),
    np_match = gsub("chinese restaurant", "chinese", np_match),
    np_match = gsub("korean restaurant", "korean", np_match),
    np_match = gsub("elderly person", "elder", np_match),
    np_match = gsub("oil paint", "oil", np_match),
    np_match = gsub("wall paint", "wall", np_match),
    np_match = gsub("shopping mall", "mall", np_match),
    np_match = gsub("chocolate fondue", "fondue", np_match),
    np_match = gsub("cell phone", "phone", np_match),
    np_match = gsub("bear den", "bear", np_match),
    np_match = gsub("fox den", "fox", np_match),
    np_match = gsub("mouse den", "mouse", np_match),
    np_match = gsub("downtown street", "downtown", np_match),
    np_match = gsub("side road", "side", np_match),
    np_match = gsub("back door", "back", np_match),
    np_match = gsub("patio door", "patio", np_match),
    np_match = gsub("front gate", "front", np_match),
    np_match = gsub("chocolate cake", "chocolate", np_match)
  )


n.total.responses <- df.trials.filtered %>%
  ungroup() %>%
  count() %>%
  pull(n)

df.trials.filtered %>%
  group_by(degree, np) %>%
  count()
```


```{r}
d.item.count <- df.trials.filtered %>%
  group_by(stim_id, np_expectations, adj_polarity) %>%
  count()
d.item.count

d.item.count %>%
  ungroup() %>%
  group_by(n) %>%
  count() %>%
  ggplot(., aes(x = n, y = nn)) +
  geom_col() +
  xlab("n responses per item") +
  ylab("n items")
```


```{r eval=F}
# d.item.n50 <- d.item.count %>%
#   filter(n >= 50)
#  write(
#    jsonlite::toJSON(d.item.n50, pretty = T),
#    file = "../experiments/js/prereg-cce-n50.json"
#  )
```

We exclude invalid responses: These are the responses the are just the name of the speaker, just the adjective, an adjectival sentence without a comparison class or non-sense words. These invalid responses were extracted manually.

```{r list of invalid responses}
invalid.responses <- c(
  "unsure",
  # all the adjectives
  "long", "short", "tall", "dark", "light", "fast", "quick", "slow",
  "hard", "soft", "loud", "noisy", "quiet", "bright", "bruises",
  "expensive", "cheap", "big", "small", "strong", "weak", "warm", "hot", "cold",
  "heavy", "wide", "narrow",
  # all the actor names
  "alexander", "alicia", "cheep", "daniel", "darker",
  "david",
  "eric", "gabriel", "anthony", "william", "john", "tom", "lucas",
  "michael", "cameron", "stephen",
  "lee", "greg", "robert", "chrales", "gary", "josh", "simon",
  # female names
  "angela", "jennifer", "monica", "melinda", "veronica", "alicia",
  "maya", "sophie", "kim", "laura", "julia",
  "michelle", "stephanie", "claire", "kathleen", "jasmine", "tanya",
  "mika", "natalia",
  # invalid responses
  "barbell snatch", "bank of america", "easy", "empire building", "chill", "chinn", "webside",
  "finished", "flexibility", "health", "hot cold",
  "lazy", "low", "cliaire", "feelings", "too small", "Too small",
  "public", "ripe", "silent", "baked", "burn", "more costly", "exacting",
  # filter out the sentences without a CC
  "A bottle of wine at a liquor store was expensive", "A piece of cotton in craft shop was light", "A piece of plastic in hardware store was soft",
  "A spider in an insect terrarium was big", "At the butchershop the chicken was expensive", "At the conference center it was noisy when she met her friend", "during the night its light out there",
  "hears the cry of a crow", "In Aquarium a tuna was big", "In botanical garden an alpine tree was short.", "In summer that day was cold", "In the freezer michelle hand was cold", "it has a lot of stuff",
  "It was noisy in the nearby city", "its not a hot and cold", "move furniture through the front gate of her house", "picks up a piece of silk.", "the coat is light in weight", "	The coat of poodle was dark",
  "the color of the script is light", "the daisy is dark in color", "The first bite of her ice cream was warm", "The first sip of juice was cold", "The furniture was narrow at the back door of his house", "The new place rental rate is expensive", "the pair of sandals are expensive", "	The piece of silk is light.",
  "the sound of the shower is strong", "The statue made of plastic was cheap", "the walls of the condo are strong", "While walking heard the cry of a rooster when it was quiet", "Basketball player was tall",
  "Friend's new rowboat was fast", "Friend's new smartcar is big", "his favorite poem was short", "it is not destructive", "it is not loud", "it is not sold expensively", "it s not wide", "its noisy in here",
  "its not a soft", "On Saturday it was cold", "STRIP MALL IS SHORT", "summer days are warm", "That baby was loud", "the adult walk quickly", "The airplane is slow.", "The bird is loud.", "the car drives by quietly", "the car is quite", "the child is not fussy", "The child walks slow.", "The coat of poodle was dark", "large", "lengthy", "Little",
  "the color is not much", "the day is cold", "the dog's body is long", "The environment is quiet.", "the floor is soft", "The flower is short.", "the food is expensive", "the fruit cake was light", "the information is  long", "The mall is short.", "The mattress s firm", "the melon was soft", "the mouse is small", "the pages are not many", "the pencil color is light", "The piece of silk is light.", "The country lane was narrow", "The new place rental rate is expensive.", "The poodle's coat is light.", "the powerboat makes no noise", "the rabbit is fast", "the sneakers are costly", "the statue is cheap", "the street is wide", "The weather is cold today.", "The suit was expensive", "The trash is light.", "The watermelon was light", "A rock concert was loud", "little",
  "the movie i hope", "all light of off", "sits on a blanket", "try a new water color",
  "driving on a downtown street", "The spider was small", "The music was Loud",
  "powerboat sound little quiet", "Horn was too loud", "Villa price was costly",
  "choral consert was too loud", "milkshake was so hot", "strip mall was tall",
  "plastic was so soft", "pork was too expensive", "price of raspberries expensive",
  "coat of a spaniel was little light", "village area was too quit to read",
  "elderly person was too quick", "conference room was too quiet", "instant pot was slow",
  "tile floor was soft", "chocolate cake color was too dark", "marshmallow was soft for eat",
  "Blue paint is dark", "pick-ip truck was long", "sits on a bedboard.", "tails on mice",
  "they are bold", "the blade spinning", "its finished", "not sure", "too slow",
  "black", "boiling", "coat of paints", "Empire State Building", "glare", "indvidual experience", "information", "It is not loud", "It was night", "It was strong", "itrs warm", "its hot", "its low", "its low cost", "its not hard", "its not mute", "its not slow", "its not soft", "its not speed", "its too sound", "its wide", "lengthy", "less wide", "melting", "More costly", "move", "muscles", "pcks", "Relationship", "sexy", "Silent", "the duration", "the distance", "the have muscles", "they are fit", "they run fast", "thrill", "though", "Very slow", "walking outside", "walking assistance tools", "word", "worthy", "tough", "picks up their trash can.", "all lights off", "amount", "high", "its long", "it cooks quickly", "little", "outside"
)
```


In order to improve matching of the provided repsonses to the subordinate NPs in the context sentences or the anticipated superordinate labels, we correct misspellings occurring in the provided responses. 
```{r list of commong mispellings}
misspellings_df <- read_csv("../data/class-elicitation-prereg-final/misspellings_dict.csv")
misspellings_set <- pull(misspellings_df, V2) %>% set_names(pull(misspellings_df, V1))
```


To further improve the response classification, we also replace some responses which are obviously synonymous to the provided subordinate or superoridnate NPs given the context.
```{r list of common synonyms}
synonym_df <- read_csv("../data/class-elicitation-prereg-final/synonym_dict.csv")
synonym_set <- pull(synonym_df, V2) %>% set_names(pull(synonym_df, V1))
```

To further improve the response classification, we lemmatize the plural responses (specifically, the irregular nouns and misspellings).
```{r list of lemmatizations}
# mostly Plural --> singulars
lemmatization_df <- read_csv("../data/class-elicitation-prereg-final/lemmatization_dict.csv")
lemmatization_set <- pull(lemmatization_df, V2) %>% set_names(pull(lemmatization_df, V1))
```

``` {r excludeInvalidResps}

# excluding invalid responses
d.tidy.resps.catch <- df.trials.filtered %>%
  filter((grepl("it's", response, ignore.case = T) |
    grepl("they're", response, ignore.case = T)))

# get invalid responses which are full sentences without any comparison class
d.tidy.resp.valid.resps <- anti_join(
  df.trials.filtered,
  d.tidy.resps.catch
) %>%
  rowwise() %>%
  mutate(
    stopPhrase = paste("the", np, "is", adj, sep = " "),
    stopPhrase2 = paste("the", np, "is",
      paste(adj, ".", sep = ""),
      sep = " "
    ),
    responseLength = lengths(str_split(response, " "))
  ) %>%
  filter((tolower(response) != stopPhrase) &
    (tolower(response) != stopPhrase2))

# get the long responses that were not matched above and filter them out manually
# d.tidy.resp.valid.resps %>% filter(responseLength >= 4) %>% View()

d.tidy.resp.valid.resps <- d.tidy.resp.valid.resps %>%
  rowwise() %>%
  # exclude responses which excatly match the ones in the following list
  subset(., !(response %in% invalid.responses))

n.valid.responses <- d.tidy.resp.valid.resps %>%
  ungroup() %>%
  count() %>%
  pull(n)

n.total.responses - n.valid.responses
# check
# d.tidy.resp.valid.resps %>%
#   filter(responseLength >= 4) %>%
#   View()
```

The responses are checked for misspellings, being invalid or synonymous to the provded NPs . 
```{r}
d.tidy.resp.valid.resps %>%
  mutate(response = as.character(response)) %>%
  ungroup() %>%
  mutate(
    response_spelling = str_replace_all(tolower(response), misspellings_set),
    response_synonym = str_replace_all(response_spelling, synonym_set),
    response_lemma = tolower(str_replace_all(response_synonym, lemmatization_set))
  ) %>%
  mutate(
    corrected_spelling = response != response_spelling,
    corrected_synonym = response_spelling != response_synonym,
    corrected_lemma = response_synonym != response_lemma
  ) -> d.tidy.resp.valid.resps

sum(d.tidy.resp.valid.resps$corrected_spelling)
sum(d.tidy.resp.valid.resps$corrected_spelling) / n.valid.responses
sum(d.tidy.resp.valid.resps$corrected_synonym)
sum(d.tidy.resp.valid.resps$corrected_synonym) / n.valid.responses
sum(d.tidy.resp.valid.resps$corrected_lemma)
sum(d.tidy.resp.valid.resps$corrected_lemma) / n.valid.responses
```

NB: This code no longer cleans the responses by removing stop words. That latter method produces issues for the "pick-up truck" (which it doesn't match correctly), times of day, and some responses involved "The + Singular_NP" (which are ambiguous and should be excluded).  


```{r}
d.tidy.resp.valid.resps %>%
  rowwise() %>%
  mutate(
    response_lemma = as.character(response_lemma),
    cleanedPhrase = paste("_", as.character(response_lemma), "_", sep = ""), # add buffer to allow for split to occur at beginning or end
    np_match = as.character(np_match),
    np_match = gsub('\"', "", np_match),
    np_match_us = paste("_", np_match, "_", sep = ""), # insert underscores for the matching the other way around
    super_us = paste("_", superordinate, "_", sep = ""),
    # check if response and seed NP match
    specific = # ifelse(
    # response_lemma == "times of day", # catch these responses because otherwise classified as subordinate for "day" / "strawberries" etc
    ifelse(response_lemma == "berries", 0,
      containsString_responses(
        as.character(cleanedPhrase),
        np_match,
        response_lemma,
        np_match_us
      )
    ),
    # check if response and anticipated superordinate match
    matchingSuper = containsString_responses(
      as.character(cleanedPhrase),
      as.character(superordinate),
      response_lemma,
      super_us
    )
  ) -> d.tidy.phrase.w.original2
```


```{r codeForSubCatTerms}

# clean produced responses to match NPs
# d.tidy.resp.valid.resps %>%
#   unnest_tokens(word, response_lemma)  %>%  # break responses into single words (one per line)
#   anti_join(my_stop_words) %>%  # remove stop words
#   group_by(workerid, trial_num) %>% # next four functions are to put phrases back together again
#   mutate(wordNumber = paste("word_", row_number(), sep = "")) %>%
#   spread(wordNumber, word) %>%
#   unite(phrase, starts_with("word_"), sep = " ") %>%
#   mutate(phrase = gsub(" NA", "", phrase)) %>%
#   left_join(
#     df.trials.filtered %>%
#       select(workerid, trial_num, response)
#     ) %>%
#   rename(cleanedPhrase = phrase, originalResponse = response) %>%
#   rowwise() %>%
#   mutate(
#     originalPhrase = as.character(cleanedPhrase),
#     cleanedPhrase = paste("_", as.character(cleanedPhrase), "_", sep = ""), # add buffer to allow for split to occur at beginning or end
#     np_match = as.character(np_match),
#     np_match = gsub('\"', "", np_match),
#     np_match_us = paste("_", np_match, "_", sep=""), # insert underscores for the matching the other way around
#     super_us = paste("_", superordinate, "_", sep=""),
#   # check if response and seed NP match
#     specific = ifelse(
#       originalPhrase == "times of day", # catch these responses because otherwise classified as subordinate for "day" / "strawberries" etc
#       ifelse(originalPhrase == "berries", 0, 0),
#       containsString_responses(
#         as.character(cleanedPhrase),
#         np_match,
#         originalPhrase,
#         np_match_us
#         )
#       ),
#   # check if response and anticipated superordinate match
#     matchingSuper = containsString_responses(
#       as.character(cleanedPhrase),
#       as.character(superordinate),
#       originalPhrase,
#       super_us)
#   ) -> d.tidy.phrase.w.original

# d.tidy.phrase.w.original %>%
#   group_by(stim_id, np_expectations, adj_polarity) %>%
#   count() %>%
#   View()
```

We extract all the automatically classified responses.
``` {r}
# remove responses with uncertainty marker "similar" for more restrictive analysis
# d.tidy.phrase.w.original %>%
#   filter(grepl("similar", originalResponse, ignore.case=T)) -> d.uncertain.resps # 15 responses

d.tidy.phrase.w.original2 %>%
  filter(grepl("similar", response_lemma, ignore.case = T)) -> d.uncertain.resps # 15 responses

d.tidy.clean.responses <- anti_join(
  d.tidy.phrase.w.original2,
  d.uncertain.resps
)

# extrcat the automatically matched data (out of 26.552 responses (post exclusion) 22.117 are matched )
d.matchedResponses <- d.tidy.clean.responses %>%
  filter((specific == 1) | (matchingSuper == 1))

n.automatic.responses <- d.matchedResponses %>%
  ungroup() %>%
  count() %>%
  pull(n)

n.automatic.responses
n.automatic.responses / n.valid.responses

# d.tidy.phrase.w.original %>%
#   select(workerid, trial_num, cleanedPhrase, specific, matchingSuper) %>%
#   rename(method_1 = specific, method_1_super = matchingSuper, method_1_cleanedPhrase = cleanedPhrase) %>%
#   right_join(., d.tidy.phrase.w.original2) %>%
#   mutate(match_specific = method_1 == specific,
#          match_super = method_1_super == matchingSuper,
#          mismatch = match_specific & match_super) -> d.tidy.phrase.w.original.compare
#
# d.tidy.phrase.w.original2
```

```{r}
# extract the consistent responses based on automatically classified data
# d.sub.counts <- d.matchedResponses %>%
#   group_by(stim_id, np_expectations, adj_polarity) %>%
#   count(specific)

# d.confident.phrase.specificMarking.bs.item <- d.matchedResponses %>%
#   group_by(stim_id, degree, superordinate,
#            np_expectations, np, adj_polarity) %>%
#   count(specific) %>%
#   mutate(nr = sum(n))

# d.sub.counts
#
# d.consistent.items <- d.sub.counts %>%
#   group_by(stim_id, np_expectations, adj_polarity) %>%
#   mutate(nr_dp = sum(n)) %>%
#   filter(n >= nr_dp-2) # extract the consistent items
#
# #d.consistent.items
# d.inconsistent.items <- anti_join(d.sub.counts, d.consistent.items)
# #d.inconsistent.items



# d.confident.phrase.specificMarking.bs.item %>%
#   filter((n == 0) | (n == nr))

# check the matched items where the mean of responses is 1 or 0
d.matchedResponses %>%
  group_by(stim_id, np_expectations, adj_polarity) %>%
  mutate(meanResp = mean(specific)) %>%
  filter((meanResp == 1) | (meanResp == 0)) %>%
  distinct(
    stim_id, np_expectations,
    np_match, adj_polarity, response_lemma, meanResp
  ) %>%
  View()

# it happns for some items where the number of matched responses is very low, e.g. for the NP "pick-up truck", positive adjective, only 3 responses out of 44 are matched automatically

# d.matchedResponses %>%
#   group_by(stim_id, np_expectations, adj_polarity) %>%
#   count() %>%
#   View()
```

We look at the responses that were not matched to our anticipated NPs and superordinates and the synonyms of the NPs. We judge if the deviating responses are synonymous to our anticipated NPs or our superordinates and adjust them. Some responses which occur often (based on manual analysis) are left unchanged to check if any unexpected response was the modal response for any particular condition. 

``` {r nonMatchedResps}
# look at the unique non-matched responses
d.tidy.resp.analysis <- anti_join(d.tidy.clean.responses, d.matchedResponses)

# d.tidy.resp.analysis <- d.tidy.phrase.w.original2 %>%
# filter(!((specific == 1) | (matchingSuper == 1)))

length(d.tidy.resp.analysis$response)

d.tidy.resp.analysis %>%
  distinct(superordinate, np, adj, np_match, response_lemma, cleanedPhrase, specific, matchingSuper) %>%
  View()
```



```{r}

# categorize the responses upon looking at the reponses not matching the NP nor the superordinate

# this is the more sketchy part of the classification
# also, responses that are synonyms of other non-matching responses are matched against each other in order to receive accurate modal responses

# first , the responses which are held to be subordinate responses are changed to the seed subordinate NPs


# sketchy synonyms
hand_classification_df <- read_csv("../data/class-elicitation-prereg-final/hand_classification_dict.csv") %>% 
  rowwise() %>%
  mutate(V2 = ifelse(is.na(V2), "", V2))
hand_classification <- pull(hand_classification_df, V2) %>% set_names(pull(hand_classification_df, V1))
```

``` {r}

# replace the sketchy synonyms
d.tidy.phrase.handClassified <- d.tidy.resp.analysis %>%
  mutate(
    response_lemma = as.character(response_lemma),
    response = as.character(response),
    response_lemma_hand = str_replace_all(response_lemma, hand_classification)
  ) %>%
  mutate(
    cleanedPhrase = paste("_", as.character(response_lemma_hand), "_", sep = ""),
    specific = containsString_responses(
      as.character(cleanedPhrase),
      as.character(np_match),
      response_lemma_hand,
      np_match_us
    ),
    matchingSuper = containsString_responses(
      as.character(cleanedPhrase),
      as.character(superordinate),
      response_lemma_hand,
      super_us
    )
  )

d.tidy.phrase.handClassified %>%
  filter((specific == 1) | (matchingSuper == 1)) -> d.tidy.phrase.handClassified.matched
```

``` {r}
d.tidy.phrase.handClassified %>%
  filter((specific == 0) & (matchingSuper == 0)) %>%
  rowwise() %>%
  mutate(
    response_lemma_hand = ifelse(superordinate == "cookware",
      gsub("pans", "frying pan", response_lemma_hand),
      response_lemma_hand
    ),
    response_lemma_hand = ifelse(superordinate == "cookware",
      gsub("dinner", "cookware", response_lemma_hand),
      response_lemma_hand
    ),
    response_lemma_hand = gsub("illunation", np_match, response_lemma_hand),
    response_lemma_hand = gsub("illumination", np_match, response_lemma_hand),
    response_lemma_hand = ifelse(superordinate == "desserts", gsub("chocolate", "chocolate fondue", response_lemma_hand), response_lemma_hand),
    response_lemma_hand = ifelse(superordinate == "furniture", gsub("beds", "bedboard", response_lemma_hand), response_lemma_hand),
    response_lemma_hand = ifelse(superordinate == "entertainment", gsub("films", "movie", response_lemma_hand), response_lemma_hand),
    response_lemma_hand = ifelse(superordinate == "waterways", gsub(
      "lake", np_match,
      response_lemma_hand
    ), response_lemma_hand),
    response_lemma_hand = ifelse(superordinate == "vehicles", gsub("trucks", "pick-up", response_lemma_hand), response_lemma_hand),
    response_lemma_hand = ifelse(superordinate == "people", gsub("walks", np_match, response_lemma_hand), response_lemma_hand),
    response_lemma_hand = ifelse(superordinate == "times of day",
      ifelse(response_lemma == "day", np_match,
        response_lemma_hand
      ), response_lemma_hand
    ),
    response_lemma_hand = ifelse(superordinate == "times of day",
      ifelse(response_lemma == "day", np_match, response_lemma_hand), response_lemma_hand
    ),
    response_lemma_hand = ifelse(superordinate == "writing utensils", gsub("ink", np_match, response_lemma_hand),
      response_lemma_hand
    ),
    response_lemma_hand = ifelse(superordinate == "birds", gsub("day", np_match, response_lemma_hand),
      response_lemma_hand
    ),
    response_lemma_hand = ifelse(superordinate == "food", gsub("day", np_match, response_lemma_hand),
      response_lemma_hand
    ),
    response_lemma_hand = ifelse(superordinate == "writing utensils", gsub("color", np_match, response_lemma_hand),
      response_lemma_hand
    ),
    response_lemma_hand = ifelse(superordinate == "seasons", gsub("past day", np_match, response_lemma_hand),
      response_lemma_hand
    ),
    response_lemma_hand = ifelse(superordinate == "insects", gsub("terrarium", np_match, response_lemma_hand),
      response_lemma_hand
    ),
    response_lemma_hand = ifelse(superordinate == "buildings", gsub(
      "apartments", "apartment building",
      response_lemma_hand
    ), response_lemma_hand),
    response_lemma_hand = gsub("brands", np_match, response_lemma_hand),
    response_lemma_hand = gsub("butchershop", np_match, response_lemma_hand),
    response_lemma_hand = ifelse(superordinate == "places", gsub("baths", "sauna", response_lemma_hand),
      response_lemma_hand
    ),
    response_lemma_hand = ifelse(np == "bottle of wine", gsub("bottles", "wine", response_lemma_hand),
      response_lemma_hand
    ),
    response_lemma_hand = ifelse(superordinate == "furniture", gsub("cans", "trash cans", response_lemma_hand),
      response_lemma_hand
    ),
    response_lemma_hand = ifelse(superordinate == "animals", gsub("zoo", np_match, response_lemma_hand),
      response_lemma_hand
    ),
    response_lemma_hand = ifelse(degree == "loudness", gsub("child", "baby", response_lemma_hand),
      response_lemma_hand
    ),
    response_lemma_hand = ifelse(degree == "weight", gsub("children", "kid", response_lemma_hand),
      response_lemma_hand
    ),
    response_lemma_hand = ifelse(np_match == "conference center", gsub("centers", "conference center", response_lemma_hand),
      response_lemma_hand
    ),
    response_lemma_hand = ifelse(degree == "weight", gsub("childern", "kid", response_lemma_hand),
      response_lemma_hand
    ),
    response_lemma_hand = ifelse(superordinate == "cakes", gsub("color", np_match, response_lemma_hand),
      response_lemma_hand
    ),
    response_lemma_hand = ifelse(degree == "temperature_h", gsub(
      "chocolate", "chocolate fondue",
      response_lemma_hand
    ), response_lemma_hand),
    response_lemma_hand = ifelse(degree == "darkness", gsub("duck", "dusk", response_lemma_hand),
      response_lemma_hand
    ),
    response_lemma_hand = gsub("compared store", np_match, response_lemma_hand),
    response_lemma_hand = ifelse(degree == "darkness", gsub("color", np_match, response_lemma_hand),
      response_lemma_hand
    ),
    response_lemma_hand = ifelse(degree == "darkness", gsub("fur color", np_match, response_lemma_hand),
      response_lemma_hand
    ),
    response_lemma_hand = ifelse(degree == "darkness", gsub("fur", np_match, response_lemma_hand),
      response_lemma_hand
    ),
    response_lemma_hand = ifelse(degree == "temperature_h", gsub("day", np_match, response_lemma_hand),
      response_lemma_hand
    ),
    response_lemma_hand = ifelse(degree == "loudness_n", gsub("day", np_match, response_lemma_hand),
      response_lemma_hand
    ),
    response_lemma_hand = ifelse(superordinate == "seasons", gsub("day this month", np_match, response_lemma_hand),
      response_lemma_hand
    ),
    response_lemma_hand = ifelse(degree == "price", gsub("day", np_match, response_lemma_hand), response_lemma_hand),
    response_lemma_hand = ifelse(degree == "price", gsub("flats", "apartments", response_lemma_hand),
      response_lemma_hand
    ),
    response_lemma_hand = ifelse(degree == "speed", gsub("kid", np_match, response_lemma_hand), response_lemma_hand),
    response_lemma_hand = ifelse(degree == "height", gsub("kid", np_match, response_lemma_hand), response_lemma_hand),
    response_lemma_hand = ifelse(degree == "loudness", gsub("kid", np_match, response_lemma_hand),
      response_lemma_hand
    ),
    response_lemma_hand = ifelse(degree == "strength", gsub("kid", np_match, response_lemma_hand),
      response_lemma_hand
    ),
    response_lemma_hand = ifelse(degree == "weight", gsub("kid", np_match, response_lemma_hand), response_lemma_hand),
    response_lemma_hand = ifelse(superordinate == "people", gsub("kid", np_match, response_lemma_hand), response_lemma_hand),
    response_lemma_hand = ifelse(degree == "width", gsub("lane", np_match, response_lemma_hand), response_lemma_hand),
    response_lemma_hand = ifelse(degree == "darkness", gsub("light", np_match, response_lemma_hand),
      response_lemma_hand
    ),
    # response_lemma_hand = ifelse(degree == "height",  gsub("mall", np_match, response_lemma_hand),
    #                          response_lemma_hand),
    response_lemma_hand = ifelse(np_match == "strip malls", gsub("mall", np_match, response_lemma_hand),
      response_lemma_hand
    ),
    response_lemma_hand = ifelse(degree == "speed_f", gsub("planes", np_match, response_lemma_hand),
      response_lemma_hand
    ),
    response_lemma_hand = ifelse(degree == "height", gsub("player", np_match, response_lemma_hand),
      response_lemma_hand
    ),
    response_lemma_hand = ifelse(degree == "temperature_h", gsub("rinks", np_match, response_lemma_hand),
      response_lemma_hand
    ),
    response_lemma_hand = ifelse(degree == "temperature_h", gsub("saturday", np_match, response_lemma_hand),
      response_lemma_hand
    ),
    response_lemma_hand = ifelse(superordinate == "animals", gsub("shade", np_match, response_lemma_hand),
      response_lemma_hand
    ),
    response_lemma_hand = ifelse(degree == "loudness_n", gsub("time", np_match, response_lemma_hand),
      response_lemma_hand
    ),
    response_lemma_hand = ifelse(degree == "temperature_h", gsub("time", np_match, response_lemma_hand),
      response_lemma_hand
    ),
    response_lemma_hand = ifelse(degree == "speed", gsub("time", np_match, response_lemma_hand), response_lemma_hand),
    response_lemma_hand = ifelse(degree == "price", gsub("time", np_match, response_lemma_hand), response_lemma_hand),
    response_lemma_hand = ifelse(superordinate == "birds", gsub("times of day", np_match, response_lemma_hand),
      response_lemma_hand
    ),
    response_lemma_hand = ifelse(degree == "darkness", gsub("time", "times of day", response_lemma_hand),
      response_lemma_hand
    ),
    response_lemma_hand = ifelse(degree == "price", gsub("store", np_match, response_lemma_hand), response_lemma_hand),
    response_lemma_hand = ifelse(degree == "price", gsub("shop", np_match, response_lemma_hand), response_lemma_hand),
    response_lemma_hand = ifelse(degree == "size", gsub("store", np_match, response_lemma_hand), response_lemma_hand),
    response_lemma_hand = ifelse(degree == "loudness_n", gsub("store", np_match, response_lemma_hand),
      response_lemma_hand
    ),
    response_lemma_hand = ifelse(degree == "length_duration", gsub("store", np_match, response_lemma_hand),
      response_lemma_hand
    ),
    response_lemma_hand = ifelse(degree == "temperature_h", gsub("sip", np_match, response_lemma_hand),
      response_lemma_hand
    ),
    response_lemma_hand = ifelse(superordinate == "animals", gsub("color", np_match, response_lemma_hand),
      response_lemma_hand
    ),
    response_lemma_hand = ifelse(superordinate == "cakes", gsub("color", np_match, response_lemma_hand),
      response_lemma_hand
    ),
    response_lemma_hand = ifelse(superordinate == "flowers", gsub("color", np_match, response_lemma_hand),
      response_lemma_hand
    ),
    response_lemma_hand = ifelse(superordinate == "materials", gsub("color", np_match, response_lemma_hand),
      response_lemma_hand
    ),
    response_lemma_hand = ifelse(superordinate == "birds", gsub("color", np_match, response_lemma_hand),
      response_lemma_hand
    ),
    response_lemma_hand = ifelse(superordinate == "birds", gsub("locations", np_match, response_lemma_hand),
      response_lemma_hand
    ),
    response_lemma = ifelse(degree == "darkness", gsub("times", "times of day", response_lemma_hand),
      response_lemma_hand
    ),
    response_lemma_hand = gsub("top shelf options", "liquor", response_lemma_hand),
    response_lemma_hand = ifelse(degree == "price", gsub("rent", "rentals", response_lemma_hand), response_lemma_hand),
    response_lemma_hand = ifelse(superordinate == "paints", gsub("color", "paint", response_lemma_hand),
      response_lemma_hand
    ),
    response_lemma_hand = ifelse(superordinate == "seasons", gsub("day", "seasons", response_lemma_hand),
      response_lemma_hand
    ),
    response_lemma_hand = ifelse(superordinate == "statues", gsub("material", "statues", response_lemma_hand),
      response_lemma_hand
    ),
    response_lemma_hand = ifelse(superordinate == "insects", gsub("bug", "insect", response_lemma_hand),
      response_lemma_hand
    ),
    response_lemma_hand = ifelse(superordinate == "cookware", gsub("cook", "cookware", response_lemma_hand),
      response_lemma_hand
    ),
    response_lemma_hand = ifelse(superordinate == "venues", gsub("auditoriums", "concert", response_lemma_hand),
      response_lemma
    ),
    response_lemma_hand = ifelse(degree == "speed", gsub("appliances", "cookware", response_lemma_hand), response_lemma_hand),
    response_lemma_hand = gsub("market", np_match, response_lemma_hand),
    response_lemma_hand = gsub("playing", np_match, response_lemma_hand),
    response_lemma_hand = gsub("saturday nights", np_match, response_lemma_hand),
    response_lemma_hand = ifelse(superordinate == "places", gsub("venues", "places", response_lemma_hand), response_lemma_hand),
    response_lemma_hand = ifelse(superordinate == "concerts", gsub("singing", "concerts", response_lemma_hand), response_lemma_hand),
    response_lemma_hand = ifelse(degree == "strength", gsub("body", "athlete", response_lemma_hand), response_lemma_hand),
    response_lemma_hand = ifelse(superordinate == "materials", gsub("cloth", "fabric", response_lemma_hand), response_lemma_hand),
    response_lemma_hand = ifelse(superordinate == "shoes", gsub("shes", "shoes", response_lemma_hand), response_lemma_hand),
    response_lemma_hand = ifelse(superordinate == "concerts", gsub("show", "concert", response_lemma_hand), response_lemma_hand),
    response_lemma_hand = ifelse(superordinate == "audios", gsub("show", "audio", response_lemma_hand), response_lemma_hand),
    response_lemma_hand = ifelse(superordinate == "statues", gsub("metal", "statue", response_lemma_hand), response_lemma_hand),
    response_lemma_hand = ifelse(superordinate == "cookware", gsub("method", "cookware", response_lemma_hand), response_lemma_hand),
    response_lemma_hand = ifelse(superordinate == "venues", gsub("night", np_match, response_lemma_hand), response_lemma_hand),
    response_lemma_hand = ifelse(superordinate == "doorways", gsub("opening", "doorway", response_lemma_hand), response_lemma_hand),
    response_lemma_hand = ifelse(superordinate == "dens", gsub("opening", "den", response_lemma_hand), response_lemma_hand),
    response_lemma_hand = ifelse(superordinate == "times of day", gsub("area", np_match, response_lemma_hand), response_lemma_hand),
    response_lemma_hand = ifelse(superordinate == "times of day", gsub("places", np_match, response_lemma_hand), response_lemma_hand),
    response_lemma_hand = ifelse(superordinate == "times of day", gsub("area", np_match, response_lemma_hand), response_lemma_hand),
    response_lemma_hand = ifelse(superordinate == "times of day", gsub("street", np_match, response_lemma_hand), response_lemma_hand),
    response_lemma_hand = ifelse(superordinate == "rentals", gsub("places", "rentals", response_lemma_hand), response_lemma_hand),
    response_lemma_hand = ifelse(superordinate == "food", gsub("dishes", "food", response_lemma_hand), response_lemma_hand),
    response_lemma_hand = ifelse(superordinate == "restaurants", gsub("places", "restaurants", response_lemma_hand),
      response_lemma_hand
    ),
    response_lemma_hand = ifelse(superordinate == "restaurants", gsub("places dinner", "restaurants", response_lemma_hand),
      response_lemma_hand
    ),
    response_lemma_hand = ifelse(superordinate == "alcoholic drinks", gsub("places", np_match, response_lemma_hand),
      response_lemma_hand
    ),
    response_lemma_hand = ifelse(superordinate == "doorways", gsub("path", "doorway", response_lemma_hand), response_lemma_hand),
    response_lemma_hand = ifelse(superordinate == "dens", gsub("passage", "den", response_lemma_hand), response_lemma_hand),
    response_lemma_hand = ifelse(superordinate == "roads", gsub("path", "road", response_lemma_hand), response_lemma_hand),
    response_lemma_hand = ifelse(superordinate == "waterways", gsub("path", "waterways", response_lemma_hand), response_lemma_hand),
    response_lemma_hand = ifelse(superordinate == "audios", gsub("performance", "audio", response_lemma_hand), response_lemma_hand),
    response_lemma_hand = ifelse(superordinate == "audios", gsub("music", "audio", response_lemma_hand), response_lemma_hand),
    response_lemma_hand = ifelse(superordinate == "materials", gsub("hardware", "materials", response_lemma_hand),
      response_lemma_hand
    ),
    response_lemma_hand = ifelse(superordinate == "audios", gsub("performance", "venues", response_lemma_hand), response_lemma_hand),
    response_lemma_hand = ifelse(superordinate == "locations", gsub("places in the house", "locations", response_lemma_hand),
      response_lemma_hand
    ),
    response_lemma_hand = ifelse(superordinate == "locations", gsub("places in the kitchen", "locations", response_lemma_hand),
      response_lemma_hand
    ),
    response_lemma_hand = ifelse(superordinate == "locations", gsub("refrigerator", "freezer", response_lemma_hand),
      response_lemma_hand
    ),
    response_lemma_hand = ifelse(superordinate == "doorways", gsub("places house", "doorways", response_lemma_hand),
      response_lemma_hand
    ),
    response_lemma_hand = ifelse(superordinate == "floors", gsub("surfaces", "floors", response_lemma_hand), response_lemma_hand),
    response_lemma_hand = ifelse(superordinate == "races", gsub("tracks", "races", response_lemma_hand), response_lemma_hand),
    response_lemma_hand = ifelse(superordinate == "restaurants", gsub("menu", "restaurants", response_lemma_hand),
      response_lemma_hand
    ),
    response_lemma_hand = ifelse(superordinate == "walls", gsub("building materials", "walls", response_lemma_hand),
      response_lemma_hand
    ),
     response_lemma_hand = ifelse(superordinate == "birds", gsub("park", np_match, response_lemma_hand),
      response_lemma_hand
    ),
    response_lemma_hand = ifelse(superordinate == "birds", gsub("forest", np_match, response_lemma_hand),
      response_lemma_hand
    ),
    response_lemma_hand = ifelse(cleanedPhrase == "_cries_", np_match, response_lemma_hand),
    response_lemma_hand = ifelse(cleanedPhrase == "_crying_", np_match, response_lemma_hand),
    response_lemma_hand = ifelse(cleanedPhrase == "_episodes_", np_match, response_lemma_hand),
    response_lemma_hand = ifelse(cleanedPhrase == "_car_", "cars", response_lemma_hand),
    response_lemma_hand = ifelse(cleanedPhrase == "_map_", "maps", response_lemma_hand),
    response_lemma_hand = ifelse(cleanedPhrase == "_pots_", "cookware", response_lemma_hand),
    response_lemma_hand = ifelse(cleanedPhrase == "_settings_", superordinate, response_lemma_hand),
    # response_lemma_hand = ifelse( cleanedPhrase == "_price_", np_match_us, cleanedPhrase),
    response_lemma_hand = ifelse(cleanedPhrase == "_pieces_", np_match, response_lemma_hand),
    response_lemma_hand = ifelse(np == "sauna", gsub("spa", "sauna", response_lemma_hand), response_lemma_hand),
    response_lemma_hand = ifelse(np == "bedboard", gsub("board", "bedboard", response_lemma_hand), response_lemma_hand),
    response_lemma_hand = gsub("shopping", np_match, response_lemma_hand),
    response_lemma_hand = gsub("works of art", superordinate, response_lemma_hand)

    # classification of those responses which were not caught above (looking at d.tidy.resp.analysis.update below): mostly adjusting synonymous responses to get accurate mode estinates
  ) %>%
  mutate(
    cleanedPhrase = paste("_", as.character(response_lemma_hand), "_", sep = ""),
    # response_lemma_cleaned = gsub("_", "", response_lemma),
    specific = containsString_responses(as.character(cleanedPhrase), as.character(np_match), response_lemma_hand, np_match_us),
    matchingSuper = containsString_responses(as.character(cleanedPhrase), as.character(superordinate), response_lemma_hand, super_us)
  ) -> d.tidy.phrase.handClassified2
```

To further clean the data set, we exclude the responses which mention the degree (n = 181) which is described by the adjectives (e.g. 'price' or 'temperature' ) since it does not provide a comparison class: e.g. we exclude responses like "It's warm relative to other temperatures".

``` {r}

# get the non-matched responses


d.tidy.phrase.handClassified2 %>% filter((specific == 0) & (matchingSuper == 0)) -> d.nonMatching.resps

# d.nonMatching.resps %>%
#   distinct(degree, superordinate, np, adj, np_match, response, response_lemma, response_lemma_hand, specific, matchingSuper) %>%
#   View()

d.tidy.phrase.handClassified2 <- d.tidy.phrase.handClassified2 %>% rbind(., d.tidy.phrase.handClassified.matched)

# the responses that are still classified as neither sub nor super do not match the anticipated responses and are mostly ones which occur fairly often. All of them are definitely not subordinate and will be classified as superordinate responses.

# here, the responses including the scale are caught  (229 responses)
d.scaleResps <- d.tidy.phrase.handClassified2 %>%
  rowwise() %>%
  mutate(
    degree_match = degree,
    degree_match = ifelse(degree == "temperature_h", "temperature", degree_match),
    degree_match = ifelse(degree == "speed_f", "speed", degree_match),
    degree_match = ifelse(degree == "loudness", "sound|noise", degree_match),
    degree_match = ifelse(degree == "loudness_n", "sound|noise", degree_match),
    degree_match = ifelse(degree == "length_duration", "length|duration", degree_match),
    degree_match = ifelse(degree == "strength", "weight", degree_match),
  ) %>% 
  filter(grepl( degree_match, response_lemma_hand, ignore.case= T) & !(grepl("bird|animal|strawberries|road|weightlifter" , response_lemma_hand)))  
# create full cleaned data set

# exclude the "degree" responses
d.AutoClassified <- d.matchedResponses %>% 
  select(workerid, stim_id, degree, context_sentence, superordinate, 
         np, np_expectations, adj, adj_polarity, np_match, response, 
         response_lemma, specific, matchingSuper)
d.HandClassified.subs.wCC <- anti_join(
  d.tidy.phrase.handClassified2, d.scaleResps
  ) %>% select(workerid, stim_id, degree, context_sentence, superordinate, 
               np, np_expectations, adj, adj_polarity, np_match, response, 
               response_lemma = response_lemma_hand, specific, matchingSuper)

d.HandClassified.marked.as.Super <- anti_join(
  d.tidy.phrase.handClassified2, d.scaleResps
  ) %>% mutate(specific = 0) %>%
  select(workerid, stim_id, degree, context_sentence, superordinate, 
               np, np_expectations, adj, adj_polarity, np_match, response, 
               response_lemma = response_lemma_hand, specific, matchingSuper)

# put the whole classified data together to get modal responses
d.tidy.resps.classified.full <- rbind(d.AutoClassified, d.HandClassified.subs.wCC)

# create a df where all hand-calssified items are treated as superordinates
d.tidy.resps.full.handClassified.as.super <- rbind(d.AutoClassified, d.HandClassified.marked.as.Super)

# some compounds should only be classified as superordinates
d.tidy.resps.classified.full <- d.tidy.resps.classified.full %>% mutate(
  specific = ifelse(response == "berries", 0, specific),
  specific = ifelse(response == "boat", 0, specific),
  specific = ifelse(response == "bird", 0, specific),
  specific = ifelse(response == "building", 0, specific),
  specific = ifelse(response == "cake", 0, specific),
  specific = ifelse(response == "concert", 0, specific),
  specific = ifelse(response == "flower", 0, specific),
  specific = ifelse(response == "guitar", 0, specific)
)

d.tidy.resps.full.handClassified.as.super <- d.tidy.resps.full.handClassified.as.super %>% mutate(
  specific = ifelse(response == "berries", 0, specific),
  specific = ifelse(response == "boat", 0, specific),
  specific = ifelse(response == "bird", 0, specific),
  specific = ifelse(response == "building", 0, specific),
  specific = ifelse(response == "cake", 0, specific),
  specific = ifelse(response == "concert", 0, specific),
  specific = ifelse(response == "flower", 0, specific),
  specific = ifelse(response == "guitar", 0, specific)
)
 
```


``` {r}
# check
d.tidy.resps.classified.full %>%
  filter((specific == 1) & (matchingSuper == 1)) %>%
  View()
# all the responses that are classified as both are composite subordinates

# check the full data set items which have mean 1 or 0

d.tidy.resps.classified.full %>%
  group_by(stim_id, np_expectations, adj_polarity) %>%
  mutate(meanSub = mean(specific), ) %>%
  filter((meanSub == 0) | (meanSub == 1)) %>%
  select(stim_id, degree, np_match, adj_polarity, np_expectations, originalResponse, cat_cleaned, meanSub) %>%
  distinct() %>%
  View()
```

fabric . superordinate

```{r}
# d.tidy.phrase.specificMarking.bs <- d.tidy.phase.classifiedSuper %>%
#   filter(!((specific == 0) & (matchingSuper == 0)))  %>%
#   #mutate() %>%

# write_csv(d.tidy.clean.responses, path = "../models/data/comparison-class-inf_clean_coded.csv")

d.tidy.phrase.specificMarking.bs <- d.tidy.clean.responses %>%
  group_by(np_expectations, adj_polarity) %>%
  tidyboot_mean(column = specific)

# d.tidy.phrase.specificMarking.bs.item <- d.tidy.phase.classifiedSuper %>%
#   filter(!((specific == 0) & (matchingSuper == 0)))  %>%
#   mutate() %>%

d.tidy.phrase.specificMarking.bs.item <- d.tidy.clean.responses %>%
  group_by(stim_id, degree, superordinate, np_expectations, np, adj_polarity) %>%
  tidyboot_mean(column = specific)

d.tidy.phrase.specificMarking.bs %>%
  ungroup() %>%
  mutate(
    np_expectations = gsub('\"', "", np_expectations),
    adj_polarity = gsub('\"', "", adj_polarity),
    np_expectations = factor(np_expectations,
      levels = c("low", "medium", "high")
    )
  ) -> d.tidy.phrase.specificMarking.bs

d.tidy.phrase.specificMarking.bs.item %>%
  ungroup() %>%
  mutate(unique_id = paste(stim_id, np_expectations, sep = "-")) %>%
  mutate(np_expectations = factor(np_expectations,
    levels = c("low", "medium", "high")
  )) -> d.tidy.phrase.specificMarking.bs.item

# save(d.tidy.phrase.specificMarking.bs, d.tidy.phrase.specificMarking.bs.item, file = "../writing/paper/cached_results/class-elicitation-bs-byItem.RData")
load(file = "../writing/paper/cached_results/class-elicitation-bs-byItem.RData") # d.tidy.phrase.specificMarking.bs, d.tidy.phrase.specificMarking.bs.item, file =

set.seed(2020)

d.tidy.phrase.specificMarking.bs.item %>%
  left_join(
    .,
    data.frame(
      unique_id = unique(d.tidy.phrase.specificMarking.bs.item$unique_id),
      jitterVal = runif(270, min = -0.07, max = 0.07)
    )
  ) %>%
  mutate(
    jitterVal = jitterVal + ifelse(adj_polarity == "positive", 0.2, -0.2)
  ) %>%
  ggplot(
    .,
    aes(
      x = as.numeric(np_expectations) + jitterVal, y = mean,
      ymin = ci_lower, ymax = ci_upper, fill = adj_polarity
    )
  ) +
  geom_col(
    data = d.tidy.phrase.specificMarking.bs,
    aes(
      x = np_expectations, y = mean,
      ymin = ci_lower, ymax = ci_upper, fill = adj_polarity
    ),
    position = position_dodge(0.8), width = 0.8, alpha = 0.6, color = "black", size = 1
  ) +
  geom_point( # position = position_dodge(0.8),
    # position = position_jitterdodge(jitter.width = 0.2, jitter.height = 0),
    # data = d.tidy.phrase.specificMarking.bs.item,
    # aes( y = mean, fill = adj_polarity, x = np_expectations),
    shape = 21, alpha = 0.8
  ) +
  geom_path(aes(group = unique_id),
    # position = position_dodge(0.8),
    alpha = 0.15
  ) +
  geom_linerange(
    data = d.tidy.phrase.specificMarking.bs,
    aes(
      x = np_expectations, y = mean,
      ymin = ci_lower, ymax = ci_upper
    ),
    position = position_dodge(0.8), color = "black", size = 1.5
  ) +
  scale_fill_brewer(palette = "Set3") +
  theme( # axis.text.x = element_text(angle = 45, hjust = 1.0, vjust = 1),
    # axis.title.x = element_blank(),
    panel.grid.minor = element_blank(),
    panel.grid.major = element_blank(),
    axis.line = element_line(colour = "black")
  ) +
  guides(fill = guide_legend(title = "Adjective polarity", reverse = T)) +
  # theme_black()+
  scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1)) +
  ylab("Proportion paraphrases that contain Specific NP") +
  xlab("Subordinate Category General Expectations")

ggsave(
  filename = "../writing/paper/figs/bars_cc_finalExpt_prereg_bars_syncDodge.pdf",
  width = 6, height = 4
)

# save(d.tidy.phrase.specificMarking.bs.item, file = "d_comparisonClass_specific_bs_item.RData")
```


```{r}
# look at data matched automatically by-item
d.confident.phrase.specificMarking.bs.item <- d.matchedResponses %>%
  # mutate() %>%
  group_by(stim_id, degree, superordinate, np_expectations, np, adj_polarity) %>%
  mean(specific)

d.tidy.phrase.specificMarking.bs %>%
  ungroup() %>%
  mutate(
    np_expectations = gsub('\"', "", np_expectations),
    adj_polarity = gsub('\"', "", adj_polarity),
    np_expectations = factor(np_expectations,
      levels = c("low", "medium", "high")
    )
  ) %>%
  ggplot(
    .,
    aes(
      x = np_expectations, y = mean,
      ymin = ci_lower, ymax = ci_upper, fill = adj_polarity
    )
  ) +
  geom_col(position = position_dodge(0.8), width = 0.8, alpha = 0.6, color = "black", size = 1) +
  geom_point(
    position = position_jitterdodge(jitter.width = 0.2, jitter.height = 0),
    data = d.tidy.phrase.specificMarking.bs.item,
    aes(y = mean, fill = adj_polarity, x = np_expectations),
    shape = 21, alpha = 0.8
  ) +
  geom_linerange(position = position_dodge(0.8), color = "black", size = 1) +
  scale_fill_brewer(palette = "Set3") +
  theme( # axis.text.x = element_text(angle = 45, hjust = 1.0, vjust = 1),
    # axis.title.x = element_blank(),
    panel.grid.minor = element_blank(),
    panel.grid.major = element_blank(),
    axis.line = element_line(colour = "black")
  ) +
  # theme_black()+
  scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1)) +
  ylab("Proportion paraphrases that contain Specific NP") +
  xlab("Subordinate Category General Expectations")

# ggsave(filename = "../writing/paper/figs/bars_cc_finalExpt_prereg_bars.pdf",
#        width = 6, height = 4)
```

By-item plot

```{r figIndivItems}
# does not work
# d.tidy.resps.classified.full  %>%
#   #mutate() %>%
#   group_by( stim_id, np_expectations,  adj_polarity) %>%
#   mutate(mean = mean( specific)) %>%
#    ungroup() %>%
#    mutate(np_expectations = gsub('\"', "", np_expectations),
#           adj_polarity = gsub('\"', "", adj_polarity),
#           np_expectations = factor(np_expectations,
#                                    levels = c("low", "medium", "high")),
#           np = fct_reorder(np, as.numeric(np_expectations)),
#           item_set = paste(degree, " - ", superordinate, "-", stim_id, sep = "")) %>%

select.items <- d.tidy.phrase.specificMarking.bs.item %>%
  select(degree, np, stim_id, superordinate, np_expectations, adj_polarity, mean) %>%
  rowwise() %>%
  mutate(degree = first(strsplit(degree, "_")[[1]])) %>%
  spread(adj_polarity, mean) %>%
  mutate(delta = positive - negative) %>%
  ungroup() %>%
  group_by(degree, stim_id, superordinate) %>%
  summarize(mean_delta = mean(abs(delta)))

select.items %>%
  group_by(degree) %>%
  mutate(
    max_val = max(mean_delta),
    min_val = min(mean_delta)
  ) %>%
  ungroup() %>%
  filter(mean_delta == max_val | mean_delta == min_val) %>%
  pull(stim_id) -> select.item.ids

# swap tall/short people with tall/short flowers
select.item.ids <- c(select.item.ids[select.item.ids != 17], 18)

# 17 for 18

# select.items[with(select.items, order(mean_delta)), ][seq(1, 90, 3), ]

d.tidy.phrase.specificMarking.bs.item %>%
  filter(stim_id %in% select.item.ids) %>%
  ungroup() %>%
  rowwise() %>%
  mutate(degree = first(strsplit(degree, "_")[[1]])) %>%
  ungroup() %>%
  mutate(
    np_expectations = gsub('\"', "", np_expectations),
    adj_polarity = gsub('\"', "", adj_polarity),
    np_expectations = factor(np_expectations,
      levels = c("low", "medium", "high")
    ),
    np = fct_reorder(np, as.numeric(np_expectations)),
    item_set = paste(degree, " - ", superordinate, "-", stim_id, sep = ""),
    item_name = paste(superordinate, " (", degree, ")", sep = ""),
    item_name = factor(item_name),
    item_set = factor(item_set),
    item_name = fct_reorder(item_name, as.numeric(item_set))
  ) %>%
  ggplot(
    .,
    aes(x = np, y = mean, fill = adj_polarity)
  ) +
  geom_col(position = position_dodge(0.8), width = 0.8, alpha = 0.7, color = "black") +
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper),
    position = position_dodge(0.8), color = "black"
  ) +
  scale_fill_brewer(palette = "Set3") +
  theme(
    axis.text.x = element_text(angle = 30, hjust = 0.8, vjust = 0.85),
    # axis.title.x = element_blank(),
    panel.grid.minor = element_blank(),
    panel.grid.major = element_blank(),
    axis.line = element_line(colour = "black"),
    legend.position = "bottom"
  ) +
  facet_wrap(~item_name, scales = "free", nrow = 4) +
  # theme_black()+
  scale_y_continuous(limits = c(-0.02, 1.02), breaks = c(0, 0.5, 1)) +
  guides(fill = guide_legend(title = "Adjective polarity", reverse = T)) +
  ylab("Proportion paraphrases that contain Specific NP") +
  xlab("Specific Category") #-> bars_cc_finalExpt_prereg_confident_byItem

# ggsave("../analysis/figs/bars_cc_finalExpt_pilot_byItem.png",
#        width = 9, height = 9)
ggsave(
  filename = "../writing/paper/figs/bars_cc_finalExpt_prereg_byItem.pdf",
  width = 15, height = 10
)
```


The data points are grouped by stim id, NP expectation, adjective polarity and specificity and the number of occurances of each response is calculated. The most common responses (both subordinate and superordinate) will be used for the adjective endorsement task. 
``` {r}

# the superordinate for the NPs where the modal responses did not match the anticipated one are substituted to the modal participant response

# extract the mode response
d.tidy.resp.counts <- d.tidy.resps.classified.full %>%
  group_by(stim_id, superordinate, np_match, np_expectations, adj_polarity, specific, response_lemma) %>%
  count() %>%
  mutate(n_unique_resps = n) %>%
  ungroup()

# insert the mode NP (modal subordinate where participants gave subordinate response, modal superordinate where they gave superordinate response)
# in column mode
d.tidy.resp.counts <- d.tidy.resp.counts %>%
  group_by(stim_id, superordinate, np_match, adj_polarity, specific) %>%
  mutate(mode = response_lemma[which.max(n)])


# analysis of modal responses
d.tidy.resp.counts.analysis <- d.tidy.resp.counts %>%
  rowwise() %>%
  mutate(
    isModeNP = containsString_responses(
      as.character(paste("_", np_match, "_", sep = "")), as.character(mode),
      np_match, as.character(paste("_", mode, "_", sep = ""))
    ),
    isModeSuper = containsString_responses(
      as.character(paste("_", superordinate, "_", sep = "")), as.character(mode),
      superordinate, as.character(paste("_", mode, "_", sep = ""))
    ),
    isModeNeither = sum(isModeNP, isModeSuper),
    mode = gsub("_", "", mode)
  ) # isModeNeither = 0 means that the mode response is different from anticipated NPs
d.tidy.resp.counts.analysis %>%
  filter(isModeNeither == 0) %>%
  distinct(stim_id, degree, superordinate, np_match, specific, adj_polarity, mode) %>%
  View()

# the superordinate will be substituted for those items where the mode deviates for 6 or more items of a set (set is 12 variations of an item: 3 np_expectations x 2 adj_polarities x 2 CC types, specific and not ) and the deviating modal response is the same for 6 or more items
d.tidy.resp.counts.analysis %>%
  filter(isModeNeither == 0) %>%
  distinct(stim_id, degree, superordinate, np_match, specific, adj_polarity, mode) %>%
  count(stim_id, mode) %>% filter(n >= 6) %>%
  View()
# %>% filter(n >= 6) -> stim.ids.adjust

d.tidy.resp.counts.analysis %>%
  filter(isModeNeither == 0) %>%
  distinct(stim_id, degree, superordinate, np_match, specific, adj_polarity, mode) %>%
  right_join(., stim.ids.adjust, by = c("stim_id")) %>%
  View()
```

## Analysing superordinate responses

For the responses that are not the anticipated suboridnate or superoridnate NPs (n = 4.000), we investigate if there are several distinct salient responses (classified as superordinate: all the data points that remain not matched to a priori subordinates or superordinates after the analyses are tagged as superordinate) within each item. For example, we would like to see if for the item set 'food' (anticipated superordinate) - 'soup' - 'salad' - 'ice cream' more than three participants provided any superordinate responses other than 'food'. We collapse across single NPs and adjective conditions within an item, i.e. we count the response as salient if at least three participants provided the response given any NP of the item (e.g. any of 'soup', 'salad', 'ice cream') and any of the adjective (positive or negative). If the response provided by the participant was provided by at least two other participants, we keep the response, otherwise it is substituted by the a priori superordinate. The corresponding frequencies will be extracted for plurals of these salient responses.     

``` {r}
d.tidy.super.counts <- d.tidy.resps.classified.full %>%
  filter((specific == 0) & (matchingSuper == 0)) %>%
  group_by(stim_id, superordinate, response_lemma) %>%
  count() %>%
  mutate(n_unique_resps = n) %>%
  ungroup()

d.tidy.super.counts %>% filter(n_unique_resps >= 3) -> d.tidy.super.counts.common

d.tidy.super.counts %>%
  ungroup() %>%
  mutate(produced_super = ifelse(n_unique_resps >= 3, response_lemma, superordinate)) -> d.tidy.super.adjust
d.tidy.resps.classified.full %>%
  filter((specific == 0) & (matchingSuper == 0)) %>%
  left_join(., d.tidy.super.adjust, by = c("stim_id", "superordinate", "response_lemma")) -> d.nonMatch.adjustSuper

# get number of data points which passed the grab-3 criterion
d.nonMatch.adjustSuper %>% filter(produced_super != superordinate) # n = 2539

# get the distinct superordinates for the frequency extraction
d.nonMatch.adjustSuper %>% distinct(produced_super) -> distinctSuper
distinctSuper %>%
  rowwise() %>%
  filter(str_detect(produced_super, ".s$")) %>% as.list() %>% .$produced_super -> pluralSuper
#anti_join(distinctSuper, pluralSuper) %>% View()
super_plural <- function(n, pluralSuper) {
  if (n %in% c("music", "people", "food", "furniture", "decor", "jewelry", "wood", "weather", "fish", "transportation", "times of day", "cookware", "traffic")) {
    n_pl <- n
  } else if (n %in% pluralSuper) {
    n_pl <- n
  } else if (n == "box") {
    n_pl <- "boxes"
  } else if (n == "city") {
    n_pl <- "cities"
  } else {
    n_pl <- paste(n, "s", sep = "")
  }
  return(n_pl)
}

distinctSuper %>%
  rowwise() %>%
  mutate(produced_super_pl = super_plural(produced_super, pluralSuper)) -> allSuper

write_csv(allSuper, "../data/class-elicitation-prereg-final/cc-prod-distinct-super-pl.csv")

d.nonMatch.adjustSuper <- d.nonMatch.adjustSuper %>%
  rowwise() %>%
  mutate(produced_super_pl = super_plural(produced_super, pluralSuper))

d.nonMatch.adjustSuper.filter <- d.nonMatch.adjustSuper %>%
  rowwise() %>%
  mutate(
    degree = ifelse(degree == "length_duration", "length", degree),
    superordinate_pl = produced_super_pl,
    superordinate_pl = ifelse(superordinate_pl == "races", "rallies", superordinate_pl),
    superordinate_pl = ifelse(superordinate_pl == "dens", "animal dens", superordinate_pl),
    NP_pl = insert_plural_np(tolower(np), superordinate)
  ) %>%
  select(workerid, stim_id, degree, superordinate_pl, adj, adj_polarity, 
         NP_sg = np, NP_pl, np_expectations, response = produced_super_pl, specific)

df.produced.super.freqs <- read_csv("../data/class-elicitation-prereg-final/cc-prod-produced-super-pl-frequencies.csv")

d.nonMatch.adjustSuper.filter.w.freqs <- d.nonMatch.adjustSuper.filter %>%
  left_join(., df.frequencies, by = c("NP_pl" = "NPs")) %>%
  left_join(., df.produced.super.freqs, by = c("superordinate_pl" = "NPs"))

d.nonMatch.adjustSuper.filter.w.freqs <- d.nonMatch.adjustSuper.filter.w.freqs %>%
  select(workerid, stim_id, degree, superordinate_pl, adj, adj_polarity, NP_sg, 
         NP_pl, np_expectations, response, specific, subFreq = Frequencies.x, superFreq = Frequencies.y)

#write_csv(d.nonMatch.adjustSuper.filter.w.freqs, "../data/class-elicitation-prereg-final/nonmatched-produced-super-w-freqs.csv")
```

``` {r}
# exclusiopn of responses where reference fails based on non-matching superordinate analysis above
d.tidy.resps.classified.full %>% filter((specific == 0) & (matchingSuper == 0)) %>%
  filter(
  ((stim_id == 90) & grepl('furniture', response_lemma)) |
  ((stim_id == 88) & grepl('bank', response_lemma)) |
  ((stim_id == 54) & grepl('vegetable', response_lemma)) |
  ((stim_id == 55) & grepl('bird', response_lemma)) |
  ((stim_id == 67) & grepl('box', response_lemma)) |  
  ((stim_id == 26) & grepl('map', response_lemma)) |
  ((stim_id == 9) & grepl('fruit', response_lemma)) 
) -> d.tidy.resp.failedRef
#write_csv(d.tidy.resp.failedRef, '../data/class-elicitation-prereg-final/data-classified-failing-reference.csv')
```

``` {r}
# the data is adjusted to the human modal responses for stim_ids 5 and 77

# plural noun phrases are adjusted to the frequency queries
d.tidy.resps.classified.full.adjust.Super <- d.tidy.resps.classified.full %>%
  anti_join(., d.tidy.resp.failedRef) %>%
  mutate(
    # substitutions made based on human modal responses
    superordinate = ifelse(stim_id == 5, "scripts", superordinate),
    superordinate = ifelse(stim_id == 77, "food", superordinate)
  ) %>%
  # if the response is specific (subordinate), the modal NP is inserted, otherwise the modal superordinate is inserted
  mutate(mode_np = ifelse(specific == 1, np, superordinate))

# write_csv(d.tidy.resps.classified.full.adjust.Super, '../data/class-elicitation-prereg-final/class-elicitation-final-full_analysis_w_adjusted_super.csv')

d.tidy.resps.full.handClassified.as.super.adjust <- d.tidy.resps.full.handClassified.as.super %>%
  anti_join(., d.tidy.resp.failedRef) %>%
  mutate(
    # substitutions made based on human modal responses
    superordinate = ifelse(stim_id == 5, "scripts", superordinate),
    superordinate = ifelse(stim_id == 77, "food", superordinate)
  ) %>%
  # if the response is specific (subordinate), the modal NP is inserted, otherwise the modal superordinate is inserted
  mutate(mode_np = ifelse(specific == 1, np, superordinate))
``` 

``` {r}
# TO BE RUN ON ONLY AUTOMATICALLY CLASSIFIED DATA
d.tidy.resps.auto.classified.full.adjust.Super <- d.matchedResponses %>%
  mutate(
    # substitutions made based on human modal responses
    superordinate = ifelse(stim_id == 5, "scripts", superordinate),
    superordinate = ifelse(stim_id == 77, "food", superordinate)
  ) %>%
  # if the response is specific (subordinate), the modal NP is inserted, otherwise the modal superordinate is inserted
  mutate(mode_np = ifelse(specific == 1, np, superordinate))
```


``` {r frequencies}
# data is prepared for frequency extraction: the freuqncies for plural forms of the NPs and the most superordinatesare pulled, so the plural NPs are added

# THE ORIGINAL NPs ARE USED, NOT THE SUBSTITUTED ONES
insert_plural_np <- function(np, superordinate) {
  if (np %in% c("piece of chocolate")) {
    np_pl <- "chocolates"
  } else if (np %in% c("piece of chalk")) {
    np_pl <- "chalks"
  } else if (np %in% c("story")) {
    np_pl <- "stories"
  } else if (np %in% c("daisy")) {
    np_pl <- "daisies"
  } else if (np %in% c("library")) {
    np_pl <- "libraries"
  } else if (np %in% c("party")) {
    np_pl <- "parties"
  } else if (np %in% c("bush")) {
    np_pl <- "bushes"
  } else if (np %in% c("finch")) {
    np_pl <- "finches"
  } else if (np %in% c("pansy")) {
    np_pl <- "pansies"
  } else if (np %in% c("documentary")) {
    np_pl <- "documentaries"
  } else if (np %in% c("pantry")) {
    np_pl <- "pantries"
  } else if (np %in% c("choral concert")) {
    np_pl <- "choirs"
  } else if (np %in% c("elderly person")) {
    np_pl <- "elderly people"
  } else if (np %in% c("mouse")) {
    np_pl <- "mice"
  } else if (np %in% c("church")) {
    np_pl <- "churches"
  } else if (np %in% c("tile")) {
    np_pl <- "tile floors"
  } else if (np %in% c("wood") & (superordinate == "floors")) {
    np_pl <- "wood floors"
  } else if (np %in% c("carpet") & (superordinate == "floors")) {
    np_pl <- "carpet floors"
  } else if (np %in% c("summer")) {
    np_pl <- "summer days"
  } else if (np %in% c("fall")) {
    np_pl <- "fall days"
  } else if (np %in% c("winter")) {
    np_pl <- "winter days"
  } else if (np %in% c("couch")) {
    np_pl <- "couches"
  } else if (np %in% c("tomato")) {
    np_pl <- "tomatoes"
  } else if (np %in% c("jolly rancher")) {
    np_pl <- "jollies"
  } else if (np %in% c("peach")) {
    np_pl <- "peaches"
  } else if (np %in% c("city")) {
    np_pl <- "cities"
  } else if (np %in% c("auditorium")) {
    np_pl <- "auditoria"
  } else if (np %in% c("bottle of top-shelf liquor")) {
    np_pl <- "liquors"
  } else if (np %in% c("six-pack of beer")) {
    np_pl <- "beers"
  } else if (np %in% c("bottle of wine")) {
    np_pl <- "wine bottles"
  } else if (np %in% c("bush")) {
    np_pl <- "bushes"
  } else if (np %in% c("mouse den")) {
    np_pl <- "mouse holes"
  } else if (np %in% c("sprinting race")) {
    np_pl <- "sprints"
  } else if (np %in% c("child")) {
    np_pl <- "children"
  } else if (np %in% c("baby")) {
    np_pl <- "babies"
  } else if (np %in% c("platinum")) {
    np_pl <- "platinum statue"
  } else if (np %in% c("bronze")) {
    np_pl <- "bronze statues"
  } else if (np %in% c("pick-up truck")) {
    np_pl <- "pick up trucks"
  } else if ((np %in% c("plastic")) & (superordinate == "bracelets")) {
    np_pl <- "plastic bracelets"
  } else if (np %in% c("gold")) {
    np_pl <- "gold bracelets"
  } else if (np %in% c("metal")) {
    np_pl <- "metal bracelets"
  } else if ((np %in% c("plastic")) & (superordinate == "statues")) {
    np_pl <- "plastic statues"
  } else if (np %in% c(
    "wool", "wood", "fish", "ice cream", "garlic", "saffron", "coffee", "raspberries",
    "boysenberries",
    "strawberries", "sneakers", "chicken", "boots", "tuna", "pork", "sandals", "plastic", "instant pot"
  )) {
    np_pl <- np # the items left singular
  } else {
    np_pl <- paste(np, "s", sep = "")
  }
  return(np_pl)
}

d.tidy.resps.w.pl.np <- d.tidy.resps.classified.full.adjust.Super %>%
  rowwise() %>%
  mutate(np_pl = insert_plural_np(tolower(np), superordinate))

# adjust some superordinates
d.tidy.resps.w.pl.np <- d.tidy.resps.w.pl.np %>%
  mutate(
    superordinate.freq = superordinate,
    superordinate.freq = ifelse(superordinate == "venue", "venues", superordinate.freq),
    superordinate.freq = ifelse(superordinate == "races", "rallies", superordinate.freq),
    superordinate.freq = ifelse(superordinate == "dens", "animal dens", superordinate.freq) # avois polysemy
  )
# this data can be fed into python frequency extractor
# write_csv(d.tidy.resps.w.pl.np, '../data/class-elicitation-prereg-final/class-elicitation-final-full_analysis_w_pl_np.csv'
```

``` {r}
# TO BE RUN ON AUTOMATICALLY CLASSIFIED DATA ONLY
d.tidy.auto.classified.w.pl.np <- d.tidy.resps.auto.classified.full.adjust.Super %>%
  rowwise() %>%
  mutate(np_pl = insert_plural_np(tolower(np), superordinate))
d.tidy.auto.classified.w.pl <- d.tidy.auto.classified.w.pl.np %>%
  mutate(
    superordinate.freq = superordinate,
    superordinate.freq = ifelse(superordinate == "venue", "venues", superordinate.freq),
    superordinate.freq = ifelse(superordinate == "races", "rallies", superordinate.freq),
    superordinate.freq = ifelse(superordinate == "dens", "animal dens", superordinate.freq) # avois polysemy
  )
```

The frquencies are appended to the cleaned data for the model. 

``` {r}
df.frequencies <- read_csv("../data/class-elicitation-prereg-final/class-elicitation-final-plural_frequencies.csv")

d.tidy.phrase.w.original.mode.pl <- d.tidy.resps.w.pl.np %>%
  left_join(., df.frequencies, by = c("np_pl" = "NPs")) %>% # add subordinate frequencies
  left_join(., df.frequencies, by = c("superordinate.freq" = "NPs")) %>%
  mutate(
    degree = ifelse(degree == "length_duration", "length", degree)
  ) # add superordinate frequencies

df.mode.final <- d.tidy.phrase.w.original.mode.pl %>%
  select(workerid, stim_id, degree, superordinate.freq, adj, adj_polarity, np, np_pl, np_expectations, mode_np, specific, Frequencies.x, Frequencies.y) %>%
  mutate(superordinate_pl = superordinate.freq, NP_sg = np, NP_pl = np_pl, response = mode_np, subFreq = Frequencies.x, superFreq = Frequencies.y) %>%
  select(workerid, stim_id, degree, superordinate_pl, adj, adj_polarity, NP_sg, NP_pl, np_expectations, response, specific, subFreq, superFreq)

# check if singular matches original
df.sg <- read_csv("../data/pilot-classElicitation-free-4/class-elicitation-free-4-cleaned-data-w-sub2.csv")

#anti_join(df.mode.final, df.sg, by = c("specific" = "specific")) %>% View()

#write_csv(df.mode.final, "../data/class-elicitation-prereg-final/full-classified-data-w-freqs-no-filedRef.csv")
```

``` {r}
# create full df with produced grab-3 superordinates
d.tidy.phrase.w.original.mode.pl %>%
  filter((specific == 1) | (matchingSuper == 1)) %>%
  select(workerid, stim_id, degree, superordinate_pl = superordinate.freq, 
         adj, adj_polarity, NP_sg = np, NP_pl = np_pl, np_expectations, 
         response = mode_np, specific, subFreq = Frequencies.x, superFreq = Frequencies.y) %>%
  rbind(., d.nonMatch.adjustSuper.filter.w.freqs) -> d.full.w.produced.super

#write_csv(d.full.w.produced.super, "../data/class-elicitation-prereg-final/full-classified-data-w-produced-super-no-failedRef.csv")

# data frame with hand classified responses being a priori superordinates
d.tidy.resps.full.handClassified.as.super.adjust.w.freq <- d.tidy.resps.full.handClassified.as.super.adjust %>%  anti_join(., d.tidy.resp.failedRef)%>% 
  rowwise() %>%
   mutate(np_pl = insert_plural_np(tolower(np), superordinate))
d.tidy.resps.full.handClassified.as.super.adjust.w.freq <-
  d.tidy.resps.full.handClassified.as.super.adjust.w.freq %>% 
  mutate(
    superordinate.freq = superordinate,
    superordinate.freq = ifelse(superordinate == "venue", "venues", superordinate.freq),
    superordinate.freq = ifelse(superordinate == "races", "rallies", superordinate.freq),
    superordinate.freq = ifelse(superordinate == "dens", "animal dens", superordinate.freq) # avois polysemy
  ) %>%
  left_join(., df.frequencies, by = c("np_pl" = "NPs")) %>% # add subordinate frequencies
  left_join(., df.frequencies, by = c("superordinate.freq" = "NPs")) %>%
  mutate(
    degree = ifelse(degree == "length_duration", "length", degree)
  ) %>% select(workerid, stim_id, degree, superordinate_pl = superordinate.freq, 
         adj, adj_polarity, NP_sg = np, NP_pl = np_pl, np_expectations, 
         response = mode_np, specific, subFreq = Frequencies.x, superFreq = Frequencies.y)
#write_csv(d.tidy.resps.full.handClassified.as.super.adjust.w.freq, '../data/class-elicitation-prereg-final/full-data-w-handResps-as-super-no-filedRef.csv')
```


``` {r}
# FOR AUTO CALSSIFIED DATA
df.frequencies <- read_csv("../data/class-elicitation-prereg-final/class-elicitation-final-plural_frequencies.csv")

d.tidy.auto.classified.w.frequency <- d.tidy.auto.classified.w.pl %>%
  left_join(., df.frequencies, by = c("np_pl" = "NPs")) %>% # add subordinate frequencies
  left_join(., df.frequencies, by = c("superordinate.freq" = "NPs")) %>% # add superordinate frequencies
  mutate(
    degree = ifelse(degree == "length_duration", "length", degree)
  )

df.mode.auto.final <- d.tidy.auto.classified.w.frequency %>%
  select(workerid, stim_id, degree, superordinate.freq, adj, adj_polarity, 
         np, np_pl, np_expectations, mode_np, specific, Frequencies.x, Frequencies.y) %>%
  mutate(superordinate_pl = superordinate.freq, NP_sg = np, NP_pl = np_pl, 
         response = mode_np, subFreq = Frequencies.x, superFreq = Frequencies.y) %>%
  select(workerid, stim_id, degree, superordinate_pl, adj, adj_polarity, NP_sg, NP_pl, np_expectations, response, specific, subFreq, superFreq)

write_csv(df.mode.auto.final, "../data/class-elicitation-prereg-final/auto-classified-data-w-freqs-final.csv")
```


# Regression modeling


### Simulate data to get contrast coding right

```{r}
simulated.data <- bind_rows(
  data.frame(
    np = "mid",
    adj = "short",
    x = rnorm(n = 20, mean = 1, sd = 0.5)
  ),
  data.frame(
    np = "mid",
    adj = "tall",
    x = rnorm(n = 20, mean = 1, sd = 0.5)
  ),
  data.frame(
    np = "low",
    adj = "short",
    x = rnorm(n = 20, mean = 0.5, sd = 0.5)
  ),
  data.frame(
    np = "low",
    adj = "tall",
    x = rnorm(n = 20, mean = 1.5, sd = 0.5)
  ),
  data.frame(
    np = "high",
    adj = "short",
    x = rnorm(n = 20, mean = 1.5, sd = 0.5)
  ),
  data.frame(
    np = "high",
    adj = "tall",
    x = rnorm(n = 20, mean = 0.5, sd = 0.5)
  )
) %>%
  mutate(
    np = factor(np, levels = c("mid", "low", "high")),
    adj = factor(adj, levels = c("short", "tall"))
  )

simulated.data.means <- simulated.data %>%
  group_by(np, adj) %>%
  summarize(m = mean(x))

simulated.data.means %>%
  ggplot(., aes(x = np, y = m, fill = adj)) +
  geom_col(position = position_dodge())


contrasts(simulated.data$adj) <- c(-0.5, 0.5)

contrasts(simulated.data$np)

lm.sim <- lm(x ~ np * adj, data = simulated.data)

lm.sim.summ <- summary(lm.sim)

sim.int <- lm.sim.summ$coefficients[["(Intercept)", "Estimate"]]
sim.beta_adj <- lm.sim.summ$coefficients[["adj1", "Estimate"]]
sim.beta_npLow <- lm.sim.summ$coefficients[["nplow", "Estimate"]]
sim.beta_npHigh <- lm.sim.summ$coefficients[["nphigh", "Estimate"]]
sim.beta_npLow_adj <- lm.sim.summ$coefficients[["nplow:adj1", "Estimate"]]
sim.beta_npHigh_adj <- lm.sim.summ$coefficients[["nphigh:adj1", "Estimate"]]

print(
  paste(
    "actual mean of MID tall",
    simulated.data.means %>% filter(np == "mid", adj == "tall") %>% pull(m),
    "model prediction",
    sim.int + 0.5 * sim.beta_adj
  )
)

print(
  paste(
    "actual mean of MID short",
    simulated.data.means %>% filter(np == "mid", adj == "short") %>% pull(m),
    "model prediction",
    sim.int - 0.5 * sim.beta_adj
  )
)

print(
  paste(
    "actual mean of HIGH tall",
    simulated.data.means %>% filter(np == "high", adj == "tall") %>% pull(m),
    "model prediction",
    sim.int + 0.5 * sim.beta_adj + sim.beta_npHigh + 0.5 * sim.beta_npHigh_adj
  )
)

print(
  paste(
    "actual mean of HIGH short",
    simulated.data.means %>% filter(np == "high", adj == "short") %>% pull(m),
    "model prediction",
    sim.int - 0.5 * sim.beta_adj + sim.beta_npHigh - 0.5 * sim.beta_npHigh_adj
  )
)

print(
  paste(
    "actual mean of LOW tall",
    simulated.data.means %>% filter(np == "low", adj == "tall") %>% pull(m),
    "model prediction",
    sim.int + 0.5 * sim.beta_adj + sim.beta_npLow + 0.5 * sim.beta_npLow_adj
  )
)

print(
  paste(
    "actual mean of LOW short",
    simulated.data.means %>% filter(np == "low", adj == "short") %>% pull(m),
    "model prediction",
    sim.int - 0.5 * sim.beta_adj + sim.beta_npLow - 0.5 * sim.beta_npLow_adj
  )
)
```


#### Full model


```{r}
d.tidy.clean.responses.fac <- d.tidy.clean.responses %>%
  mutate(
    adj_polarity = factor(adj_polarity,
      levels = c("negative", "positive")
    ),
    np_expectations = factor(np_expectations,
      levels = c("medium", "low", "high")
    )
  )

d.tidy.clean.responses.fac$stim_id <- as.factor(d.tidy.clean.responses.fac$stim_id)
d.tidy.clean.responses.fac$workerid <- as.factor(d.tidy.clean.responses.fac$workerid)

contrasts(d.tidy.clean.responses.fac$adj_polarity) <- c(-1 / 2, 1 / 2)

rs.glm.brm <- brm(
  formula = specific ~ np_expectations * adj_polarity +
    (1 + np_expectations * adj_polarity | workerid) +
    (1 + np_expectations * adj_polarity | stim_id),
  family = bernoulli(), chains = 3, cores = 3, iter = 1000,
  data = d.tidy.clean.responses.fac
)


rs.glm.brm.summary <- summary(rs.glm.brm)

rs.glm.brm.summary
```

```{r}
write_csv(data.frame(rs.glm.brm.summary[["fixed"]]) %>%
  mutate(Rowname = row.names(.)),
path = "../writing/paper/csv_data_4_tex/expt3_brm_pilot.csv"
)
```


#### Simple effects


```{r}
rs.glm <- glmer(
  formula = specific ~ np_positiveness * adj_positiveness +
    (1 | workerid) +
    (1 | superordinate),
  family = "binomial",
  data = d.tidy.phrase.w.original.fac
)

contrasts(d.tidy.phrase.w.original.fac$np_positiveness)

summary(rs.glm)
```

