```{r libraries, echo=F}
library(knitr)
```

# Summary

- There's a lot of variability in the degree of specifity for the comparison class for the subcategory "days in Fall". This creates two issues:
  1. Is "days" supposed to mean days of the year or a more specific window of time?
  2. How should we extract frequencies for "fall" due to polsemy? To merge it with other, more specific terms, we need to answer the first questoin.
- Participants never included "flower" in their response to the questions on flower vases
- Some participants interpreted "wardrobe" to mean clothing.
- Routes is tricky because of the colloquial usage of "drives" and "trips"; do we collapse "drives" with "trips" or with "driving routes"?

# Results

```{r results, echo=F}
a.results = read.csv("results.csv")
a.type = read.csv("types.csv")
a.total = data.frame(a.results, a.type["type"])
kable(a.total)
```

# Change Log

- Collapsed rows 1 (chimpanzees) and 2 (chimps)
- Collapsed rows 5 (chimpanzees) and 7 (chimps)
- Collapsed rows 13 (elephants) and 14 (elephant)
- Collapsed rows 21 (cups coffee) and 23 (coffee)
- Collapsed rows 28 (cups coffee) and 30 (coffee)
- Collapsed rows 33 (cups iced tea), 35 (iced tea), and 36 (iced teas)
- Collapsed rows 41 (cups iced tea), 43 (ice teas), 45 (iced tea), and 46 (iced teas)
- Collapsed rows 38 (cups tea) and 47 (tea)
- Collapsed rows 50 (water) and 52 (cups water)
- Collapsed rows 92 (muscle cars) and 95 (hot rod cars)
- Collapsed rows 104 (sports cars) and 105 (sport cars)
- Collapsed rows 107 (suvs) and 109 (suv)
- Collapsed rows 110 (suvs) and 112 (sus)
- Collapsed rows 152 (vases) and 157 (vaes)
- Collapsed rows 171 (plastic vases) and 173 (vases plastic)
- Collapsed rows 176 (apples) and 178 (apple)
- Collapsed rows 180 (fruit) and 181 (fruits)
- Collapsed rows 184 (fruit) and 185 (fruits)
- Collapsed rows 187 (watermelons) and 189 (watermelon)
- Collapsed rows 191 (fruit) and 192 (fruits)
- Collapsed rows 190 (watermelons), 194 (watermellons), and 195 (watermelon)
- Collapsed rows 226 (basketball players) and 228 (players)
- Collapsed rows 227 (people) and 229 (humans)
- Collapsed rows 231 (gymnasts) and 233 (gymnast)
- Collapsed rows 267 (bike routes) and 268 (bike route)
- Collapsed rows 286 (flights) and 287 (flightws)
- Changed row 115 from "fall" to "fall days"
- Changed row 249 from "living" to "living room"
- Changed row 256 from "middle day" to "middle of the day" or "midday"
- Changed row 258 from "times day" to "times of day"
