---
title: "Comparison class elicitation (final) pilot"
author: "MH Tessler"
date: "October 29, 2019"
---

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Load libraries.
library(knitr)
library(tidyverse)
library(jsonlite)
library(tidyboot)
library(tidytext)
library(lme4)
library(ggthemes)
library(brms)
theme_set(theme_few())
```

## Results


```{r load data from json, eval = F}
data.path <- "../mturk/class-elicitation-free-4-pilot/production-results/"
result.files <- list.files(data.path, pattern="json")

df.subject <- data.frame()
df.trials <- data.frame()
df.attention <- data.frame()
for (result_file in result.files) {
  result_json = fromJSON(paste(data.path, result_file, sep ="/"))
  worker.id = result_json$WorkerId
  condition = result_json$answers$condition
  
  df.attention = bind_rows(
    df.attention, 
    data.frame(result_json$answers$catch_trials) %>%
      mutate(workerid = worker.id)
  )
    
  df.subject = bind_rows(
    df.subject, 
    data.frame(result_json$answers$subject_information) %>% 
      mutate(
        workerid = worker.id,
        language = gsub("\"", "", language),
        enjoyment = gsub("\"", "", enjoyment),
        age = gsub("\"", "", age),
        gender = gsub("\"", "", gender),
        problems = gsub("\"", "", problems),
        comments = gsub("\"", "", comments)
      ) 
  )
    
  df.trials = bind_rows(
    df.trials, 
    data.frame(result_json$answers$trials) %>%
      mutate(workerid = worker.id)
  )
}

# write_csv(df.trials, "../data/pilot-classElicitation-free-4/class-elicitation-free-4-pilot-trials.csv")
# write_csv(df.subject, "../data/pilot-classElicitation-free-4/class-elicitation-free-4-pilot-subject_information.csv")
# write_csv(df.attention, "../data/pilot-classElicitation-free-4/class-elicitation-free-4-pilot-catch_trials.csv")
```


```{r load data from csv}
df.trials <- read_csv("../data/pilot-classElicitation-free-4/class-elicitation-free-4-pilot-trials.csv")
df.subject <- read_csv("../data/pilot-classElicitation-free-4/class-elicitation-free-4-pilot-subject_information.csv")
df.attention <- read_csv("../data/pilot-classElicitation-free-4/class-elicitation-free-4-pilot-catch_trials.csv")
```


### Catch trials

```{r}
df.attention %>%
  group_by(incorrect) %>%
  count()
```

```{r summarize catch trials}
df.attention.summary <- df.attention %>%
  group_by(workerid) %>%
  summarize(n_memory_correct = sum(correct,na.rm = T),
            n_check_incorrect = sum(incorrect, na.rm = T))

df.attention.summary %>%
  group_by(n_memory_correct) %>%
  count()
```

```{r}
# paste in the superordinate that was not recorded 
insert_super = function(np) {
  if (np %in% c("seagull", "parrot", "crow")) {
    super = "birds"
  }  else if (np %in% c("day", "dusk", "night")) {
    super = "times of day"
  } else if (np %in% c("jolly rancher", "piece of chocolate", "marshmallow")) {
    super = "sweets"
  } else if (np %in% c("tile", "wood", "carpet")) {
    super = "floor materials"
  } else if (np %in% c("giraffe", "monkey", "bird", "donkey", "dog", "cat", "elephant", "mouse", "cheetah", "sloth", "fish")) {
    super = "animals"
  } else if (np %in% c("basketball player", "golfer", "jockey", "runner", "jogger", "walker")) {
    super = "athletes"
  } else if (np %in% c("dachshund", "bassett hound", "chihuahua")) {
    super = "dogs"
  } else if( np %in% c("novel", "story", "poem")) {
    super = "readings"
  } else if( np %in% c("auditorium", "classroom", "study hall")) {
    super = "rooms"
  } else if ( np %in% c("platinum", "bronze", "plastic")) {
    super = "statues"
  } else if (np %in% c("bottle of top-shelf liquor", "six-pack of beer", "bottle of wine")) {
    super = "alcoholic drinks"
  } else if (np %in% c("tree", "bush", "flower")) {
    super = "plants"
  } else if(np %in% c("adult", "teenager", "child", "kid", "baby")) {
    super = "people"
  } else if (np %in% c("hurricane", "thunderstorm", "rain")) {
    super = "storms"
  } else if (np %in% c("soup", "salad", "ice cream")) {
    super = "food"
  } else if( np %in% c("summer", "fall", "winter")) {
    super = "seasons"
  } else if (np %in% c("cave", "cavern", "fox hole")) {
    super = "holes"
  } else {
    super = "roads"
  }
  return (super)
}
df.trials.w.super <- df.trials %>% rowwise() %>% mutate(superordinate = insert_super(np))
```


Those multi-word NPs are substituted by one-word expressions where the expressions of this subordinate category are highly likely to include and depend on this one word. 
```{r filtered main trails}
df.trials.filtered <- df.trials.w.super %>%
  left_join(., df.attention.summary) %>%
  filter(n_memory_correct > 8, n_check_incorrect < 2)  %>% 
  rowwise() %>%
  mutate(
    np_match = np, # additional column where we put the NP to be matched against, such that the original NPs can be accessed if necessary
    np_match = gsub("bottle of top-shelf liquor", "liquor", np_match),
    np_match = gsub("piece of chocolate", "chocolate", np_match),
    np_match = gsub("piece of chalk", "chalk", np_match),
    np_match = gsub("six-pack of beer", "beer", np_match),
    np_match = gsub("bottle of wine", "wine", np_match),
    np_match = gsub("pine tree", "pine", np_match),
    np_match = gsub("redwood tree", "redwood", np_match),
    np_match = gsub("alpine tree", "alpine", np_match),
    np_match = gsub("bonsai tree", "bonsai", np_match),
    np_match = gsub("bassett hound", "bassett", np_match),
    np_match = gsub("pick-up truck", "pick-up", np_match),
    np_match = gsub("relay race", "relay", np_match),
    np_match = gsub("podcast episode", "podcast", np_match),
    np_match = gsub("kettle ball", "ball", np_match),
    np_match = gsub("basketball player", "basketball", np_match),
    np_match = gsub("study hall", "study", np_match),
    np_match = gsub("electric car", "electric", np_match),
    np_match = gsub("bass guitar", "bass", np_match),
    np_match = gsub("rock concert", "rock", np_match),
    np_match = gsub("rap concert", "rap", np_match),
    )

df.trials.filtered %>% group_by(np) %>%
  count()
```

Plurals of all irregular nouns in the stimuli set are converted to singulars to match the seed noun phrase. Common misspellings are also controlled for in this code. Based on pilot data, specific mistakes and synonyms are converted to the seed NPs.

```{r codeForSubCatTerms}

# extended function to check matching between strings either way 
containsString <- function(strng, substrng){
  return(ifelse(length(strsplit(strng, substrng)[[1]]) > 1, 1, ifelse( length(strsplit(substrng, strng)[[1]]) > 1, 1, 0)))
}

#stop_words <- stopwords()
my_stop_words <-# bind_rows(
  
  stop_words %>%
  
    filter(., !(stop_words %in% c("rooms", "year", "side", "area", "of")))#,
  # data.frame(
  #   word = c("relative", "compare"),
  #   lexicon = 'mh'
  # )
#)

d.tidy.phrase.w.original2 <- df.trials.filtered %>% 
  mutate(response = as.character(response),
         response = gsub("&quotechar", "", response),
         response = gsub("biking", "bike", response),
         response = gsub("bicycle", "bike", response),
         response = gsub("car ride", "drive", response),
         response = gsub("babies", "baby", response),
         response = gsub("stories", "story", response),
         response = gsub("6 packs", "beer", response),
         response = gsub("six-packs", "beer", response),
         response = gsub("six packs", "beer", response),
         response = gsub("basset", "bassett", response),
         response = gsub("dasies", "daisy", response),
         response = gsub("pansies", "pansy", response),
         response = gsub("mice", "mouse", response),
         response = gsub("documentaries", "documentary", response),
         response = gsub("parties", "party", response),
         response = gsub("libraries", "library", response),
         response = gsub("cities", "city", response),
         response = gsub("auditoria", "auditorium", response),
         response = gsub("gymnasia", "gymnasium", response),
         response = gsub("cacti", "cactus", response),
         response = gsub("pantries", "pantry", response),
         response = gsub("bonzai", "bonsai", response),
         response = gsub("seagul", "seagull", response),
         response = gsub("seagulll", "seagull", response),
         response = gsub("dalia", "dahlia", response),
         response = gsub("pitbul", "pitbull", response),
         response = gsub("panter", "panther", response),
         response = gsub("icecream", "ice cream", response),
         response = gsub("ice-cream", "ice cream", response),
         response = gsub("bed board", "bedboard", response),
         response = gsub("jocky", "jockey", response),
         response = gsub("jockie", "jockey", response),
         response = gsub("smart car", "smartcar", response),
         response = gsub("gym", "gymnasium", response),
         response = gsub("beverage", "drink", response),
         response = gsub("dog house", "doghouse", response),
         response = gsub("fridge", "refrigerator", response),
         response = gsub("chihuaua", "chihuahua", response),
         response = gsub("zuccini", "zucchini", response),
         response = gsub("cheeta", "cheetah", response),
         response = gsub("skiier", "skier", response),
         response = gsub("old", "elderly", response),
         response = gsub("teen", "teenager", response),
         response = gsub("cooking", "cookware", response),
         response = gsub("mobile", "cell", response),
         
         response = gsub("candies", "sweets", response),
         response = gsub("candy", "sweets", response),
         response = gsub("dachund", "dachshund", response),
         response = gsub("floor surfaces", "floors", response),
         response = gsub("floor materials", "floors", response),
         response = gsub("flooring", "floors", response),
         response = gsub("humans", "people", response),
         response = gsub("brands of beer", "beer", response),
         response = gsub("players that play a different sport", "athletes", response),
         response = gsub("liquors", "liquor", response),
         response = gsub("monkies", "monkeys", response),
         response = gsub("hours of the day", "times of day", response),
         response = gsub("books", "readings", response),
         response = gsub("brushes", "bushes", response),
         response = gsub("writing", "reading", response),
         response = gsub("poetry", "peom", response),
         response = gsub("marshmellow", "marshmallow", response),
         response = gsub("ape", "monkey", response),
         response = gsub("cow", "crow", response),
         response = gsub("burrow", "hole", response),
         response = gsub("times of the year", "seasons", response),
         response = gsub("times of year", "seasons", response),
         response = gsub("jokceys", "jockeys", response),
         response = gsub("golf player", "golfer", response),
         response = gsub("marshamallow", "marshmallow", response),
        
         superordinate = gsub("times of day", "times day", superordinate),
         superordinate = gsub("floor materials", "floors", superordinate)
        
         ) %>%
  unnest_tokens(word, response)  %>% 
  #anti_join(stop_words)  %>% # remove stop words
  anti_join(my_stop_words) %>%  # remove stop words
  group_by(workerid, trial_num) %>% # next four functions are to put phrases back together again
  mutate(wordNumber = paste("word_", row_number(), sep = "")) %>%
  spread(wordNumber, word) %>%
  unite(phrase, starts_with("word_"), sep = " ") %>%
  mutate(phrase = gsub(" NA", "", phrase)) %>%
  left_join(
     df.trials.filtered %>% select(workerid, trial_num, response)) %>% 
  rename(cleanedPhrase = phrase, originalResponse = response) %>% 
  rowwise() %>%
  mutate(
    cleanedPhrase = paste("_", as.character(cleanedPhrase), "_", sep = ""), # add buffer to allow for split to occur at beginning or end
    np_match = as.character(np_match),
    np_match = gsub('\"', "", np_match),
    specific = containsString(as.character(cleanedPhrase), as.character(np_match)),
    matchingSuper = containsString(as.character(cleanedPhrase), as.character(superordinate))
  ) %>%
  select(workerid, trial_num, stim_id, context, np_positiveness, adj, degree, superordinate, adj_positiveness, np_match, cleanedPhrase, originalResponse, specific, matchingSuper)

```
The data points are grouped by NP, adjective and scale condition and the number of occurances of each response is calculated. The most common responses (both subordinate and superordinate) will be used for the adjective endorsement task. 

``` {r}
# extract the mode response 
d.tidy.resp.counts <- d.tidy.phrase.w.original %>% 
  group_by(degree, superordinate, np_match, np_positiveness, adj, adj_positiveness, diff, matchingSuper, matchingSuperResp, cleanedPhrase) %>% count() %>%
  mutate(n_unique_resps = n)

#
d.tidy.resp.counts <- d.tidy.resp.counts %>% group_by(np_match, adj) %>% mutate(mode = cleanedPhrase[which.max(n)])

d.tidy.resp.counts <- d.tidy.resp.counts %>% rowwise() %>%  mutate(isModeNP = containsString(as.character(mode), as.character(np_match)),
                                                                   isModeSuper = containsString(as.character(mode), as.character(superordinate)),
                                                                   isModeNeither = sum(isModeNP, isModeSuper)) # isModeNeither = 0 means that the mode response is different from anticipated NPs

non-matching-mode-resps <- d.tidy.resp.counts %>% filter(isModeNeither == 0) %>% mutate(mode = gsub("_", "", mode)) %>% select(degree, superordinate, np_match, np_positiveness, adj, adj_positiveness, n_unique_resps, mode)
#%>% write_csv(., '../data/pilot-classElicitation-free-4/class-elicitation-free-4-nonmatching-mode-resps.csv')

# substitute mode responses with typos or not mathcing equivalent seed NPs
d.tidy.resp.counts <- d.tidy.resp.counts%>% rowwise() %>% mutate(cleanMode = gsub("_", "", mode),
                                                                 cleanMode = gsub("baby", "babies", cleanMode),
                                                                 cleanMode = gsub("days fall", "days in fall",
                                                                                 cleanMode),
                                                                 cleanMode = gsub("ice cream", "ice creams",
                                                                                 cleanMode),
                                                                 cleanMode = gsub("times day", "times of day",
                                                                                  cleanMode),
                                                                 cleanMode = gsub("story", "stories", cleanMode),
                                                                 cleanMode = gsub("bottles wine", 
                                                                                  "bottles of wine", cleanMode),
                                                                 cleanMode = gsub("mouse", "mice", cleanMode),
                                                                 cleanMode = gsub("cheetahhs", "cheetahs",
                                                                                  cleanMode),
                                                                 cleanMode = gsub("days fall", "fall days",
                                                                                  cleanMode),
                                                                 cleanMode = gsub("teenageragers", "teenagers", cleanMode)
                                                                 )

#write_csv(d.tidy.resp.counts, '../data/pilot-classElicitation-free-4/class-elicitation-free-4-modal-responses.csv')
```

# Viz: First prass

```{r figCollapseItems}
d.tidy.phrase.specificMarking.bs <- d.tidy.phrase.w.original %>% 
  mutate() %>%
  group_by(np_positiveness,  adj_positiveness) %>%
  tidyboot_mean(column = specific)

d.tidy.phrase.specificMarking.bs %>%
  ungroup() %>%
  mutate(np_positiveness = gsub('\"', "", np_positiveness),
         adj_positiveness = gsub('\"', "", adj_positiveness),
         np_positiveness = factor(np_positiveness,
                               levels = c("negative", "neither-nor", "positive"),
                               labels = c("low", "medium", "high")
)) %>%
  rename(adj_polarity = adj_positiveness) %>%
  ggplot(., 
       aes( x = np_positiveness, y = mean, 
            ymin = ci_lower, ymax = ci_upper, fill = adj_polarity))+  
  geom_col(position = position_dodge(0.8), width = 0.8, alpha = 0.7, color = 'black')+
  geom_linerange(position = position_dodge(0.8), color = 'black')+  
  scale_fill_brewer(palette = "Set3")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1.0, vjust = 1),
        #axis.title.x = element_blank(),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.line = element_line(colour = "black"))+
 # theme_black()+
  scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
  ylab("Proportion paraphrases that contain NP")+
  xlab("Subordinate Category Prior Mean")

# ggsave("../analysis/figs/bars_cc_finalExpt_pilot.png",
#        width = 5, height = 3.6)
```


# by item

```{r figCollapseItems}
d.tidy.phrase.specificMarking.bs.item <- d.tidy.phrase.w.original %>% 
  mutate() %>%
  group_by(np_positiveness,  np, degree, adj_positiveness) %>%
  tidyboot_mean(column = specific)

d.tidy.phrase.specificMarking.bs.item %>%
  ungroup() %>%
  mutate(np_positiveness = gsub('\"', "", np_positiveness),
         adj_positiveness = gsub('\"', "", adj_positiveness),
         np_positiveness = factor(np_positiveness,
                               levels = c("negative", "neither-nor", "positive"),
                               labels = c("low", "medium", "high")
)) %>%
  rename(adj_polarity = adj_positiveness) %>%
  ggplot(., 
       aes( x = np, y = mean, 
            ymin = ci_lower, ymax = ci_upper, fill = adj_polarity))+  
  geom_col(position = position_dodge(0.8), width = 0.8, alpha = 0.7, color = 'black')+
  geom_linerange(position = position_dodge(0.8), color = 'black')+  
  scale_fill_brewer(palette = "Set3")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1.0, vjust = 1),
        #axis.title.x = element_blank(),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.line = element_line(colour = "black"))+
  facet_wrap(~degree, scales = 'free')+
 # theme_black()+
  scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
  ylab("Proportion paraphrases that contain NP")+
  xlab("Subordinate Category Prior Mean")

# ggsave("../analysis/figs/bars_cc_finalExpt_pilot_byItem.png",
#        width = 7, height = 7)
```

# Regression modeling

```{r}
d.tidy.phrase.w.original.fac <- d.tidy.phrase.w.original %>%
  mutate(adj_positiveness = factor(adj_positiveness, 
                                   levels = c("negative", "positive")),
         np_positiveness = factor(np_positiveness, 
                                  levels = c("neither-nor", "negative", "postiive")))

rs.glm.brm <- brm(
  formula = specific ~ np_positiveness * adj_positiveness + 
    (1 +  np_positiveness*adj_positiveness | workerid) + 
    (1 +  np_positiveness*adj_positiveness | degree),
  family = bernoulli(), 
  data = d.tidy.phrase.w.original.fac)

summary(rs.glm.brm)

contrasts(d.tidy.phrase.w.original.fac$adj_positiveness)
```


```{r}
rs.glm <- glmer(
  formula = specific ~ np_positiveness * adj_positiveness + 
    (1 | workerid) + 
    (1| degree),
  family = 'binomial', 
  data = d.tidy.phrase.w.original.fac)

summary(rs.glm)
```


