---
title: "Class Elicitation Free Production"
author: "mht"
date: "7/12/2017"
output: github_document
---

```{r global_options, include=FALSE}
project.path <- "/Users/mht/Documents/research/comparison-class/"
data.path <- paste(project.path, "data/pilot-classElicitation-free-2/", sep = "")
knitr::opts_chunk$set(fig.width=3, fig.height=3, fig.crop=F, fig.pos="tb", fig.path='figs/', echo=F, warning=F, cache=F, message=F, sanitize=T)
```

```{r libraries}
library(langcog)
library(tidyverse)
library(tidytext)
library(knitr)
library(tidyboot)
#setDict("/Users/mht/Documents/research/tools/WordNet-3.0/dict")
library(wordnet)
```


### Pilot data (n = 27)

#### Subject enjoyment (0 - 2 scale)

There was an error in recording *subject information* for the first 9 subjects and those were not parsed properly. Kind of hard to recover (and it's only the survey infor).


```{r subjinfo}
d.subject <- read.csv(paste(data.path, "class-elicitation-free-2-subject_information.csv", sep = ""))
table(d.subject$enjoyment)
```


Preview of raw data 

```{r loadData}
d <- read.csv(paste(data.path, 
                    "class-elicitation-free-2-trials.csv", sep = ""))

sample_n(d, 10) %>%
  select(super_category, sub_category, adjective, response)
```

#### Grouping based on raw data

```{r}
d.counts <- d %>%
  group_by(degree, super_category, sub_category, target) %>%
  count(response)

d.counts[with(d.counts, order(super_category, sub_category, target, -n)),] %>%
  kable()
```



```{r}
my_stop_words <-# bind_rows(
  stop_words %>%
    filter(!(word %in% c("rooms", "year")))#,
  # data.frame(
  #   word = c("relative", "compare"),
  #   lexicon = 'mh'
  # )
#)


d.tidy <- d %>%
  mutate(response = as.character(response),
         response = gsub("&quotechar", "", response),
         response = gsub("biking", "bike", response),
         response = gsub("car ride", "drive", response)
         ) %>%
  unnest_tokens(word, response)  %>% 
  anti_join(stop_words)  # remove stop words
  #anti_join(my_stop_words)  # remove stop words
```

## Analysis by words

```{r}
d.tidy.wordCounts <- d.tidy %>%
  group_by(degree, super_category, sub_category, target) %>%
  count(word)

d.tidy.wordCounts[with(d.tidy.wordCounts, order(super_category, sub_category, target, -n)),] %>%
  kable()
```


## Analysis by phrases

After removing stop words, I reconstruct the phrases...

```{r}
d.tidy.phrase <- d.tidy %>%
  group_by(workerid, trial_num) %>% # next four functions are to put phrases back together again
  mutate(wordNumber = paste("word_", row_number(), sep = "")) %>%
  spread(wordNumber, word) %>%
  unite(phrase, starts_with("word_"), sep = " ") %>%
  mutate(phrase = gsub(" NA", "", phrase))
```

#### How well do we do cleaning the phrases?

```{r}
d.tidy.phrase.w.original <- left_join(d.tidy.phrase, 
                           d %>% select(workerid, trial_num, response)) %>% 
  rename(cleanedPhrase = phrase, originalResponse = response)

d.tidy.phrase.w.original %>% 
  ungroup() %>%
  select(sub_category, adjective, originalResponse, cleanedPhrase) %>% 
  sample_n(40) %>% kable()
```

### Results

```{r}
d.tidy.phraseCounts <- d.tidy.phrase %>%
  group_by(degree, super_category, sub_category, target) %>%
  count(phrase)

d.tidy.phraseCounts[with(d.tidy.phraseCounts, order(super_category, sub_category, target, -n)),] %>%
  kable()
```



### Can we track "specificity" by word count?

```{r}
d.wordCountFromCleanedPhrase <- left_join(
  left_join(
    d.tidy %>%
      group_by(workerid, target, degree, contextWithSuper, adjective, super_category,
               form, condition, sub_category, strength) %>%
      summarize(nWords = n()) %>% 
      ungroup(),
    d %>% select(workerid, target, degree, contextWithSuper, adjective, super_category,
               form, condition, sub_category, response)
  ),
  d.tidy.phrase %>%
    select(workerid, target, degree, contextWithSuper, adjective, super_category,
               form, condition, sub_category, phrase)
) %>% 
  group_by(strength, degree, adjective, super_category,
               form, sub_category) %>%
  summarize(nWordsPerResponse = sum(nWords) / n()) 

str()

ggplot(d.wordCountFromCleanedPhrase, 
       aes( x = strength, y = nWordsPerResponse, fill = form))+
  geom_col(position = position_dodge())+
  facet_wrap(~degree)
```

Not clear that number of words is going to be correlated with specificity.


### look for sub_category keyterms (to mark as specific in a binary sense)


```{r}
subcat_keyterms <- list(
  apple = "apple",
   grape = "grape",
  watermelon = "watermelon",

  "day in Fall" = "fall",
  "day in Summer" = "summer",
  "day in Winter" = "winter",
  
  "basketball player" = "basketball", # also "players"? (implicit domain restriction)
  gymnast = "gymnast",
  "runner"= "runner",
  "soccer player" = "soccer",
  
  basement = "basement",
  "living room" = "living",
  "sunroom" = "sunroom",
  
  "bike route from Los Angeles to San Francisco" = "bike",
  "flight from Los Angeles to San Francisco" = "flight",
  "driving route from Los Angeles to San Francisco" = "driv",#,c("driving", "drive", "car"),
  
  "chimpanzee" = "chimp",
  "elephant" = "elephant",
  "porcupine" = "porcupine",
  
  "city bike" = "city bike",
  "electric bike" = "electric bike",
  "kids bike" = "kid",
  
  "coffee table" = "coffee table",
  "reading lamp" = "lamp",
  "wardrobe"= "wardrobe",
  
  "crystal flower vase" = "crystal",
  "plastic flower vase" = "plastic",
  "glass flower vase" = "glass",
  
  "cup of coffee" = "coffee",
  "cup of iced tea" = "ice",
  "cup of water" = "water",
  
  "electric car"  = "electric car",
  "muscle car" = "muscle car",
  "sedan"   =  "sedan",
  "SUV" = "suv",
  "sports car" = "sports car",
  "family car" = "family car" 
)

levelsOfSubCategory = c(
  "grape",
  "apple",
  "watermelon",

  "day in Winter",
  "day in Fall",
  "day in Summer",
  
  "gymnast",
  "runner",
  "basketball player",
  
  "basement",
  "living room",
  "sunroom",
  
  "bike route from Los Angeles to San Francisco",
  "driving route from Los Angeles to San Francisco",
  "flight from Los Angeles to San Francisco",
  
  "porcupine",
  "chimpanzee",
  "elephant",
  
  "kids bike",
  "city bike",
  "electric bike",
  
  "reading lamp",
  "coffee table",
  "wardrobe",
  
  "plastic flower vase",
  "glass flower vase",
  "crystal flower vase",
  
  "cup of iced tea",
  "cup of water",
  "cup of coffee",
  
  "electric car",
  "family car",
  "muscle car",
 
  "sports car",
  "sedan" ,
  "SUV"
)

containsString <- function(strng, substrng){
  return(ifelse(length(strsplit(strng, substrng)[[1]]) > 1, 1, 0))
}

d.tidy.phrase.specificMarking <- d.tidy.phrase.w.original %>% 
  rowwise() %>%
  mutate(
    cleanedPhrase = paste("_", cleanedPhrase, "_", sep = ""), # add buffer to allow for split to occur at beginning or end
    subcatKeyterm = subcat_keyterms[[as.character(sub_category)]],
    specific = containsString(
      as.character(cleanedPhrase), 
      subcat_keyterms[[as.character(sub_category)]]
    )
  )
```



```{r fig.height=4, fig.width=5}
d.tidy.phrase.specificMarking.summarized <- d.tidy.phrase.specificMarking %>% 
  mutate(sub_category = factor(sub_category, levels = levelsOfSubCategory)) %>%
  group_by(strength, degree, adjective, super_category,
               form, sub_category) %>%
  tidyboot_mean(column = specific)
  #summarize(propSpecific = sum(specific) / n())

ggplot(d.tidy.phrase.specificMarking.summarized, 
       aes( x = sub_category, y = empirical_mean, 
            ymin = ci_lower, ymax = ci_upper, fill = form))+
  geom_col(position = position_dodge(), color = 'black')+
  geom_errorbar(position = position_dodge())+
  facet_wrap(~degree + super_category, scales = 'free', nrow = 2)+
  scale_fill_solarized()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1.0, vjust = 1),
        axis.title.x = element_blank(),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.line = element_line(colour = "black"))+
  scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
  ylab("Proportion Specific paraphrase   ")

ggsave("~/Documents/research/talks/vagueness/roger-labmtg-2017-09/freeProduciton-binarzed-results.pdf", width = 12, height = 8)
```


- "basketball player" gets a lot of "players" responses, which is ambiguous but probably means "basketball players"
- many responses outside of the category
  - 
  - other "times of day"
- "reading lamps" ... "lamps" vs. "reading lamps"
- people just say "days" for warm for winter


```{r}
 d.tidy.phrase.specificMarking %>% 
  mutate(sub_category = factor(sub_category, levels = levelsOfSubCategory)) %>%
  group_by(strength, 
               form) %>%
  summarize(propSpecific = sum(specific) / n()) %>% 
  ggplot(., 
       aes( x = strength, y = propSpecific, fill = form))+  
  geom_col(position = position_dodge(), color = 'black')+
  scale_fill_solarized()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1.0, vjust = 1),
        axis.title.x = element_blank(),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.line = element_line(colour = "black"))+
  scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
  ylab("Proportion Specific paraphrase   ")
```

```{r}
b2 <- data_frame(value = rbinom(n = 20, size = 1, prob = 0.5), condition = 1)
b1 <- data_frame(value = rbinom(n = 20, size = 1, prob = 0.7), condition = 2)
df.boot <- bind_rows(b1, b2) %>%
  group_by(condition) %>%
  tidyboot_mean(column = value)
df.boot
```

