---
title: "Comparison class elicitation (final) pilot"
author: "MH Tessler"
date: "October 29, 2019"
---

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Load libraries.
library(knitr)
library(tidyverse)
library(jsonlite)
library(tidyboot)
library(tidytext)
library(lme4)
library(ggthemes)
library(brms)
theme_set(theme_few())
```

## Results


```{r load data from json, eval = F}
data.path <- "../mturk/class-elicitation-free-4-pilot/production-results/"
result.files <- list.files(data.path, pattern="json")

df.subject <- data.frame()
df.trials <- data.frame()
df.attention <- data.frame()
for (result_file in result.files) {
  result_json = fromJSON(paste(data.path, result_file, sep ="/"))
  worker.id = result_json$WorkerId
  condition = result_json$answers$condition
  
  df.attention = bind_rows(
    df.attention, 
    data.frame(result_json$answers$catch_trials) %>%
      mutate(workerid = worker.id)
  )
    
  df.subject = bind_rows(
    df.subject, 
    data.frame(result_json$answers$subject_information) %>% 
      mutate(
        workerid = worker.id,
        language = gsub("\"", "", language),
        enjoyment = gsub("\"", "", enjoyment),
        age = gsub("\"", "", age),
        gender = gsub("\"", "", gender),
        problems = gsub("\"", "", problems),
        comments = gsub("\"", "", comments)
      ) 
  )
    
  df.trials = bind_rows(
    df.trials, 
    data.frame(result_json$answers$trials) %>%
      mutate(workerid = worker.id)
  )
}

# write_csv(df.trials, "../data/pilot-classElicitation-free-4/class-elicitation-free-4-pilot-trials.csv")
# write_csv(df.subject, "../data/pilot-classElicitation-free-4/class-elicitation-free-4-pilot-subject_information.csv")
# write_csv(df.attention, "../data/pilot-classElicitation-free-4/class-elicitation-free-4-pilot-catch_trials.csv")
```


```{r load data from csv}
df.trials <- read_csv("../data/pilot-classElicitation-free-4/class-elicitation-free-4-pilot-trials.csv")
df.subject <- read_csv("../data/pilot-classElicitation-free-4/class-elicitation-free-4-pilot-subject_information.csv")
df.attention <- read_csv("../data/pilot-classElicitation-free-4/class-elicitation-free-4-pilot-catch_trials.csv")
```


### Catch trials

```{r}
df.attention %>%
  group_by(incorrect) %>%
  count()
```
```{r summarize catch trials}
df.attention.summary <- df.attention %>%
  group_by(workerid) %>%
  summarize(n_memory_correct = sum(correct,na.rm = T),
            n_check_incorrect = sum(incorrect, na.rm = T))

df.attention.summary %>%
  group_by(n_memory_correct) %>%
  count()
```

```{r}
# paste in the superordinate that was not recorded 
insert_super = function(np) {
  if (np %in% c("seagull", "parrot", "crow")) {
    super = "birds"
  }  else if (np %in% c("day", "dusk", "night")) {
    super = "times of day"
  } else if (np %in% c("jolly rancher", "piece of chocolate", "marshmallow")) {
    super = "sweets"
  } else if (np %in% c("tile", "wood", "carpet")) {
    super = "floor materials"
  } else if (np %in% c("giraffe", "monkey", "bird", "donkey", "dog", "cat", "elephant", "mouse", "cheetah", "sloth", "fish")) {
    super = "animals"
  } else if (np %in% c("basketball player", "golfer", "jockey", "runner", "jogger", "walker")) {
    super = "athletes"
  } else if (np %in% c("dachshund", "bassett hound", "chihuahua")) {
    super = "dogs"
  } else if( np %in% c("novel", "story", "poem")) {
    super = "readings"
  } else if( np %in% c("auditorium", "classroom", "study hall")) {
    super = "rooms"
  } else if ( np %in% c("platinum", "bronze", "plastic")) {
    super = "statues"
  } else if (np %in% c("bottle of top-shelf liquor", "six-pack of beer", "bottle of wine")) {
    super = "alcoholic drinks"
  } else if (np %in% c("tree", "bush", "flower")) {
    super = "plants"
  } else if(np %in% c("adult", "teenager", "child", "kid", "baby")) {
    super = "people"
  } else if (np %in% c("hurricane", "thunderstorm", "rain")) {
    super = "storms"
  } else if (np %in% c("soup", "salad", "ice cream")) {
    super = "food"
  } else if( np %in% c("summer", "fall", "winter")) {
    super = "seasons"
  } else if (np %in% c("cave", "cavern", "fox hole")) {
    super = "holes"
  } else {
    super = "roads"
  }
  return (super)
}
df.trials.w.super <- df.trials %>% rowwise() %>% mutate(superordinate = insert_super(np))
```


Those multi-word NPs are substituted by one-word expressions where the expressions of this subordinate category are highly likely to include and depend on this one word. 
```{r filtered main trails}
df.trials.filtered <- df.trials.w.super %>%
  left_join(., df.attention.summary) %>%
  filter(n_memory_correct > 8, n_check_incorrect < 2)  %>% 
  rowwise() %>%
  mutate(
    np = gsub("bottle of top-shelf liquor", "liquor", np),
    np = gsub("piece of chocolate", "chocolate", np),
    np = gsub("piece of chalk", "chalk", np),
    np = gsub("six-pack of beer", "beer", np),
    np = gsub("bottle of wine", "wine", np),
    np = gsub("pine tree", "pine", np),
    np = gsub("redwood tree", "redwood", np),
    np = gsub("alpine tree", "alpine", np),
    np = gsub("bonsai tree", "bonsai", np),
    np = gsub("bassett hound", "bassett", np),
    np = gsub("pick-up truck", "pick-up", np),
    np = gsub("relay race", "relay", np),
    np = gsub("podcast episode", "podcast", np),
    np = gsub("kettle ball", "ball", np),
    np = gsub("basketball player", "basketball", np),
    np = gsub("study hall", "study", np),
    np = gsub("electric car", "electric", np),
    np = gsub("bass guitar", "bass", np),
    np = gsub("rock concert", "rock", np),
    np = gsub("rap concert", "rap", np),
    )

df.trials.filtered %>% group_by(np) %>%
  count()
```

Plurals of all irregular nouns in the stimuli set are converted to singulars to match the seed noun phrase. Common misspellings are also controlled for in this code.  

```{r codeForSubCatTerms}
containsString <- function(strng, substrng){
  return(ifelse(length(strsplit(strng, substrng)[[1]]) > 1, 1, 0))
}

my_stop_words <-# bind_rows(
  stop_words %>%
    filter(!(word %in% c("rooms", "year", "side")))#,
  # data.frame(
  #   word = c("relative", "compare"),
  #   lexicon = 'mh'
  # )
#)

d.tidy.phrase.w.original <- df.trials.filtered %>% 
  mutate(response = as.character(response),
         response = gsub("&quotechar", "", response),
         response = gsub("biking", "bike", response),
         response = gsub("bicycle", "bike", response),
         response = gsub("car ride", "drive", response),
         response = gsub("babies", "baby", response),
         response = gsub("stories", "story", response),
        response = gsub("6 packs", "beer", response),
        response = gsub("six-packs", "beer", response),
        response = gsub("six packs", "beer", response),
        response = gsub("basset", "bassett", response),
        response = gsub("dasies", "daisy", response),
        response = gsub("pansies", "pansy", response),
        response = gsub("mice", "mouse", response),
         response = gsub("documentaries", "documentary", response),
         response = gsub("parties", "party", response),
         response = gsub("libraries", "library", response),
         response = gsub("cities", "city", response),
         response = gsub("auditoria", "auditorium", response),
         response = gsub("gymnasia", "gymnasium", response),
         response = gsub("cacti", "cactus", response),
         response = gsub("pantries", "pantry", response),
        response = gsub("bonzai", "bonsai", response),
         response = gsub("seagul", "seagull", response),
        response = gsub("dalia", "dahlia", response),
        response = gsub("pitbul", "pitbull", response),
        response = gsub("panter", "panther", response),
        response = gsub("icecream", "ice cream", response),
        response = gsub("ice-cream", "ice cream", response),
        response = gsub("bed board", "bedboard", response),
        response = gsub("jocky", "jockey", response),
        response = gsub("jockie", "jockey", response),
        response = gsub("smart car", "smartcar", response),
        response = gsub("gym", "gymnasium", response),
        response = gsub("beverage", "drink", response),
        response = gsub("dog house", "doghouse", response),
        response = gsub("fridge", "refrigerator", response),
        response = gsub("chihuaua", "chihuahua", response),
        response = gsub("zuccini", "zucchini", response),
        response = gsub("cheeta", "cheetah", response),
        response = gsub("skiier", "skier", response),
        response = gsub("old", "elderly", response),
        response = gsub("teen", "teenager", response),
        response = gsub("cooking", "cookware", response),
        response = gsub("mobile", "cell", response)
         ) %>%
  unnest_tokens(word, response)  %>% 
  #anti_join(stop_words)  %>% # remove stop words
  anti_join(my_stop_words) %>%  # remove stop words
  group_by(workerid, trial_num) %>% # next four functions are to put phrases back together again
  mutate(wordNumber = paste("word_", row_number(), sep = "")) %>%
  spread(wordNumber, word) %>%
  unite(phrase, starts_with("word_"), sep = " ") %>%
  mutate(phrase = gsub(" NA", "", phrase)) %>%
  left_join(
     df.trials.filtered %>% select(workerid, trial_num, response)) %>% 
  rename(cleanedPhrase = phrase, originalResponse = response) %>% 
  rowwise() %>%
  mutate(
    cleanedPhrase = paste("_", as.character(cleanedPhrase), "_", sep = ""), # add buffer to allow for split to occur at beginning or end
    np = as.character(np),
    np = gsub('\"', "", np),
    specific = containsString(as.character(cleanedPhrase), as.character(np)),
    specificRespNP = containsString(as.character(np), gsub("_", "", as.character(cleanedPhrase))),
    diff = specific - specificRespNP
  ) %>%
  select(workerid, trial_num, stim_id, context, np_positiveness, adj, degree, adj_positiveness, np, cleanedPhrase, originalResponse, specific, specificRespNP, diff)

```




# Viz: First prass

```{r figCollapseItems}
d.tidy.phrase.specificMarking.bs <- d.tidy.phrase.w.original %>% 
  mutate() %>%
  group_by(np_positiveness,  adj_positiveness) %>%
  tidyboot_mean(column = specific)

d.tidy.phrase.specificMarking.bs %>%
  ungroup() %>%
  mutate(np_positiveness = gsub('\"', "", np_positiveness),
         adj_positiveness = gsub('\"', "", adj_positiveness),
         np_positiveness = factor(np_positiveness,
                               levels = c("negative", "neither-nor", "positive"),
                               labels = c("low", "medium", "high")
)) %>%
  rename(adj_polarity = adj_positiveness) %>%
  ggplot(., 
       aes( x = np_positiveness, y = mean, 
            ymin = ci_lower, ymax = ci_upper, fill = adj_polarity))+  
  geom_col(position = position_dodge(0.8), width = 0.8, alpha = 0.7, color = 'black')+
  geom_linerange(position = position_dodge(0.8), color = 'black')+  
  scale_fill_brewer(palette = "Set3")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1.0, vjust = 1),
        #axis.title.x = element_blank(),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.line = element_line(colour = "black"))+
 # theme_black()+
  scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
  ylab("Proportion paraphrases that contain NP")+
  xlab("Subordinate Category Prior Mean")

# ggsave("../analysis/figs/bars_cc_finalExpt_pilot.png",
#        width = 5, height = 3.6)
```


# by item

```{r figCollapseItems}
d.tidy.phrase.specificMarking.bs.item <- d.tidy.phrase.w.original %>% 
  mutate() %>%
  group_by(np_positiveness,  np, degree, adj_positiveness) %>%
  tidyboot_mean(column = specific)

d.tidy.phrase.specificMarking.bs.item %>%
  ungroup() %>%
  mutate(np_positiveness = gsub('\"', "", np_positiveness),
         adj_positiveness = gsub('\"', "", adj_positiveness),
         np_positiveness = factor(np_positiveness,
                               levels = c("negative", "neither-nor", "positive"),
                               labels = c("low", "medium", "high")
)) %>%
  rename(adj_polarity = adj_positiveness) %>%
  ggplot(., 
       aes( x = np, y = mean, 
            ymin = ci_lower, ymax = ci_upper, fill = adj_polarity))+  
  geom_col(position = position_dodge(0.8), width = 0.8, alpha = 0.7, color = 'black')+
  geom_linerange(position = position_dodge(0.8), color = 'black')+  
  scale_fill_brewer(palette = "Set3")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1.0, vjust = 1),
        #axis.title.x = element_blank(),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.line = element_line(colour = "black"))+
  facet_wrap(~degree, scales = 'free')+
 # theme_black()+
  scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
  ylab("Proportion paraphrases that contain NP")+
  xlab("Subordinate Category Prior Mean")

# ggsave("../analysis/figs/bars_cc_finalExpt_pilot_byItem.png",
#        width = 7, height = 7)
```

# Regression modeling

```{r}
d.tidy.phrase.w.original.fac <- d.tidy.phrase.w.original %>%
  mutate(adj_positiveness = factor(adj_positiveness, 
                                   levels = c("negative", "positive")),
         np_positiveness = factor(np_positiveness, 
                                  levels = c("neither-nor", "negative", "postiive")))

rs.glm.brm <- brm(
  formula = specific ~ np_positiveness * adj_positiveness + 
    (1 +  np_positiveness*adj_positiveness | workerid) + 
    (1 +  np_positiveness*adj_positiveness | degree),
  family = bernoulli(), 
  data = d.tidy.phrase.w.original.fac)

summary(rs.glm.brm)

contrasts(d.tidy.phrase.w.original.fac$adj_positiveness)
```


```{r}
rs.glm <- glmer(
  formula = specific ~ np_positiveness * adj_positiveness + 
    (1 | workerid) + 
    (1| degree),
  family = 'binomial', 
  data = d.tidy.phrase.w.original.fac)

summary(rs.glm)
```


