---
title: "Frequency and length for comparison class prior"
output: html_notebook
---

We imagine the utterance "He is tall" is an incomplete utterance, which gets expanded to "He is a tall man" or "He is tall for a man" assuming a noisy channel-style reconstruction.
The prior distribution on comparison classes (say, between "people" and "basketball players"), then, can be imagined as a prior distribution on the two completions ("He is tall relative to other basketball players" vs. "He is tall relative to other people").

We can thus adopt a "production prior" for the comparison class prior, and can estimate the relative cost of these two utterances by their length and log-frequency.

We will use the `ngramr` package in R to get frequency information from the Google Books corpus, from 1960 - present following Graf, Degen, Hawkins and Goodman (2016, cogsci). 


```{r}
#library(devtools)
#devtools::install_github("chrismeserole/gbNgram")
project.path <- "/Users/mht/Documents/research/comparison-class/"
library(ggplot2)
library(tidyr)
library(dplyr)
library(gbNgram)
```

```{r, eval = F}
data.path <- paste(project.path, "data/classElicitation-1/", sep = "")
d <- read.csv(paste(data.path, "class-elicitation-full-trials.csv", sep = ""))

#sub_categories <- levels(factor(d$sub_category))
#super_categories <- levels(factor(d$super_category))
#write.csv(sub_categories, paste(project.path, "analysis/ngrams_subcat.csv", sep = ""))
#write.csv(super_categories, paste(project.path, "analysis/ngrams_supercat.csv", sep = ""))
```

```{r}
sub_categories <- read.csv(paste(project.path, "analysis/ngrams_subcat3.csv", sep = ""))
super_categories <- read.csv(paste(project.path, "analysis/ngrams_supercat3.csv", sep = ""))
```


```{r}
words <- as.list(bind_rows(
  sub_categories %>% select(-X) %>% gather(key, val) %>%
    filter(!is.na(val)) %>%
    filter(!(val == "")) %>%
    select(val),
  super_categories %>% select(-X) %>% gather(key, val) %>%
    filter(!is.na(val)) %>%
    filter(!(val == "")) %>%
    select(val)
  ))$val

# ngram only seems to work for 12 or 13 terms at a time...
df.all <- data.frame()

for (i in 1:ceiling(length(words)/10)){
  targets <- words[seq((i-1)*10 + 1, i*10)]
  terms <- targets[!is.na(targets)]
  df <- gbNgram::ngram(terms, 
                     yr.start = 1960, yr.end = 2008)
  df.all <- if (length(df.all) == 0) { df } else { left_join(df.all, df) }
  print(i)
}


df.tidy <- df.all %>% select(-year) %>%
  gather(word, val) %>%
  group_by(word) %>%
  summarize(freq = sum(val))


df.cat.freq <- bind_rows(
  left_join(sub_categories %>% select(X, x), 
    left_join( # join df.tidy to sub_category label
      sub_categories %>% gather(key, word, -X) %>%
        filter(!is.na(word)) %>%
        filter(!(word == "")) %>% select(-key),
        df.tidy) %>%
      group_by(X) %>%
      summarize(totalFreq = sum(freq))) %>%
    ungroup() %>% rename(cat = x) %>% 
    mutate(category = "sub"),
  left_join(super_categories %>% select(X, cat), 
    left_join( # join df.tidy to sub_category label
      super_categories %>% gather(key, word, -X) %>%
        filter(!is.na(word)) %>%
        filter(!(word == "")) %>% select(-key),
        df.tidy) %>%
      group_by(X) %>%
      summarize(totalFreq = sum(freq))) %>%
    mutate(category = "super")
)

#df.subcat <- data.frame(word = sub_categories %>% strsplit(" ") %>% unlist()) %>%
# df.subcat <- data.frame(word = sub_categories %>% strsplit(" ") %>% unlist()) %>%
#   rowwise() %>%
#   mutate(subcat_1 = sub_categories[grepl(word, sub_categories)][1],
#          ncats = length(sub_categories[grepl(word, sub_categories)]),
#          subcat_2 = ifelse(ncats > 1, sub_categories[grepl(word, sub_categories)][2], NA),
#          subcat_3 = ifelse(ncats > 2, sub_categories[grepl(word, sub_categories)][3], NA)) %>%
#   select(-ncats)
# 
# df.supercat <- data.frame(word = super_categories %>% strsplit(" ") %>% unlist()) %>%
#   rowwise() %>%
#   mutate(supercat_1 = super_categories[grepl(word, super_categories)][1],
#          ncats = length(super_categories[grepl(word, super_categories)]))


```


```{r}
df.cat.freq %>%
  mutate(logfreq = log(totalFreq),
         cat = factor(cat, levels = cat[order(logfreq)])) %>%
  ggplot(., aes( x = cat, y = logfreq, fill = category))+
  geom_bar(stat = 'identity', position = position_dodge())+
  coord_flip()
```


```{r}


cc.all <- left_join(
  left_join(
  #           mutate(superResponse = ifelse(paraphrase == "super", 1, 0)) %>% 
  #   group_by(strength, target, degree, adjective, form, sub_category, super_category) %>%
  #   multi_boot_standard(column = "superResponse"), 
  d,
          df.cat.freq %>% filter(category == "super") %>%
            select(-X, -category) %>% rename(superFreq = totalFreq, super_category = cat) %>%
            mutate(super_category = factor(super_category, 
                                           levels = c("things you watch online","kitchen appliances",
                                                      "people", "fruits and vegetables",
                                                      "days of the year"),
                                           labels = c("things you watch online","kitchen appliances",
                                                      "people", "produce",
                                                      "days of the year")
                                           ))
  ),
  df.cat.freq %>% filter(category == "sub") %>%
   select(-X, -category) %>% rename(subFreq = totalFreq, sub_category = cat) %>%
    mutate(sub_category = factor(sub_category, 
                                 levels = c("apples","basketball players",
                                     "bottle openers","days in Fall",       
                                      "days in Summer","days in Winter",         
                                      "dishwashers","grapes",       
                                      "gymnasts","movies",
                                     "music videos","soccer players",
                                     "toasters","video of the cute animal",
                                     "watermelons"),
                                 labels = c("apple","basketball player",
                                     "bottle opener","day in Fall",       
                                      "day in Summer","day in Winter",         
                                      "dishwasher","grape",       
                                      "gymnast","movie",
                                     "music video","soccer player",
                                     "toaster","video of the cute animal",
                                     "watermelon"))
 ))

#cc.summary %>%
  #mutate(logFreqRatio = exp(log(superFreq)  - log(subFreq))) %>% View()

# %>%
#   gather(key, val, mean, logFreqRatio) %>%
#     ggplot(., 
#          aes( x = sub_category, 
#               y = val,
#               group = form, fill = form ) )+
#   geom_bar(stat = 'identity', position = position_dodge())+
#   facet_grid(key~degree, scales = 'free')+#, nrow = 1)+
#   ylim(0, 1) + 
#   theme(axis.text.x = element_text(angle = 90) )
```
```{r}
cc.wFreq.Length <- cc.all %>%
  mutate(logSuperFreq = log(superFreq),
         logSubFreq = log(subFreq),
         logSuperFreq = ifelse(logSuperFreq == -Inf, -20, logSuperFreq),
         superLength = nchar(as.character(super_category)),
         subLength = nchar(as.character(sub_category)))

#write.csv(cc.wFreq.Length, paste(project.path,
                                 #"data/classElicitation-1/class-elicitation-full-trials-freq-length.csv", 
                                 #sep = ""), row.names = F)
```

