---
title: "Comparison class models (RSA + BDA)"
author: "M. H. Tessler"
date: "7/21/2017"
output: github_document
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=6, fig.height=4, fig.crop=F, fig.pos="tb", fig.path='figs/', echo=F, warning=F, cache=F, message=F, sanitize=T)
theme_set(theme_few())
```

```{r libraries}
library(langcog)
library(tidyverse)
library(data.table)
library(coda)
library(knitr)

project.path <- "/Users/mht/Documents/research/comparison-class/"

estimate_mode <- function(s) {
  d <- density(s)
  return(d$x[which.max(d$y)])
}
hdi_upper<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","upper"])
}
hdi_lower<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","lower"])
}
```


```{r ce.data}
data.path <- paste(project.path, "data/classElicitation-1/", sep = "")

d.catch <- read.csv(paste(data.path, "class-elicitation-full-catch_trials.csv", sep = ""))

d.catch <- d.catch %>% 
  mutate(pass = response == "relative to other buildings") %>%
  select(workerid, pass)

d <- read.csv(paste(data.path, "class-elicitation-full-trials.csv", sep = ""))


df.bayes <- left_join(d, d.catch) %>%
  filter(pass) %>%
  mutate(subResponse = ifelse(paraphrase == "super", 0, 1)) %>%
  group_by(strength, target, degree, adjective, form, sub_category, super_category) %>%
  summarize(k = sum(subResponse), n = n()) %>%
  ungroup() %>%
  mutate(a = 1 + k,
         b = 1 + n - k,
         low  = qbeta(.025, a, b),
         high = qbeta(.975, a, b),
         MAP_h = (a-1)/(a+b-2),
         mean = a / (a + b))

```

```{r vs.data}
project.name <- "vague-prior-elicitation-1"
data.path <- paste(project.path, "data/vagueSpeaker-1/", sep = "")
d.catch <- read.csv(paste(data.path, project.name, "-catch_trials.csv", sep = ""))
d.catch <- d.catch %>% 
  mutate(pass = response == "Yes")

d <- read.csv(paste(data.path, project.name, "-trials.csv", sep = ""))



vs.bayes <- left_join(d, d.catch %>% select(workerid, pass)) %>%
  filter(pass) %>%
  group_by(strength, target, degree, adjective, 
           form, sub_category, super_category) %>%
  summarize(k = sum(response), n = n()) %>%
  ungroup() %>%
  mutate(a = 1 + k,
         b = 1 + n - k,
         low  = qbeta(.025, a, b),
         high = qbeta(.975, a, b),
         MAP_h = (a-1)/(a+b-2),
         mean = a / (a + b))
```



## Model results

#### CogSci results (L1 model)

```{r load_model_results, cache = T}
load(paste(
   project.path,
   "writing/cogsci17/model_results/fbt-L1-explAlt-noSilence-empiricalCC-disc3-mcmc50000_burn25000_2chain.RData",
   sep = ""))

m.samp.tidy <-left_join(
  m.samp %>% filter(param == "prior"),
  d %>% select(degree, sub_category, strength) %>% unique() %>%
  rename(cat = sub_category)
) %>% 
  mutate(strength = factor(strength, levels = c(1,2,3),
                           labels = c("low","medium","high")))



m.freq.summary <- m.samp %>% filter(param == "frequency") %>%
  group_by(param) %>%
  summarize( MAP = estimate_mode(val),
             cred_upper = hdi_upper(val),
             cred_lower = hdi_lower(val) )

m.pp <- m.samp %>% 
  filter(param %in% c("superCC", "superSpeaker")) %>%
  # rowwise() %>%
  # mutate(val = ifelse(param == "superCC", 1 - val, val)) %>%  
  group_by(param, cat,form) %>%
  summarize( MAP = estimate_mode(val),
             cred_upper = hdi_upper(val),
             cred_lower = hdi_lower(val) )
```

```{r l1.model.figure}
md.pp <- left_join(
  bind_rows(vs.bayes %>% 
             mutate(expt = "superSpeaker"),
           df.bayes %>%
             mutate(expt = "superCC")) %>% 
             ungroup() %>%
             rename(cat = sub_category),
  m.pp %>% rename(expt = param)) %>%
  rowwise() %>%
  mutate(
         form = factor(form, levels = c("positive", "negative")),
         MAP = ifelse(expt == "superCC", 1 - MAP, MAP),
         cred_lower = ifelse(expt == "superCC", 1 - cred_lower, cred_lower),
         cred_upper = ifelse(expt == "superCC", 1 - cred_upper, cred_upper),
         degree = factor(degree,
                         levels = c("height", "temperature", "weight",
                                    "time", "price"),
                         labels = c("short / tall","cold / warm",
                                    "light / heavy", "short / long", 
                                    "cheap / expensive" )),
         expt = factor(expt, 
                       levels = c("superCC", "superSpeaker"),
                       labels = c('Experiment 1 \n (Comparison class inference)', ' Experiment 2 \n (Adjective production)'))) 

         
fill.colors <- RColorBrewer::brewer.pal(5, "Set3")
names(fill.colors) <- levels(md.pp$degree)

scatterFig <- ggplot(md.pp, aes(x = MAP, xmin = cred_lower, xmax = cred_upper,
                  y = MAP_h, ymin = low, ymax = high,
                  shape = form, fill = degree))+
  geom_abline(intercept = 0, slope = 1, lty = 3, color = 'black')+
  geom_errorbar(size = 0.5, alpha = 0.4, color = 'black')+
  geom_errorbarh(size = 0.5, alpha =0.4, color = 'black')+
  geom_point(size = 2.5, color = 'black')+
  scale_shape_manual(values = c(24, 25))+
  scale_fill_brewer(palette = "Set3")+
  facet_wrap(~expt)+
  coord_fixed(ratio = 1)+
  scale_x_continuous(limits = c(0, 1), breaks = c(0,1))+
  scale_y_continuous(limits = c(0, 1), breaks = c(0,1))+
  ylab("Human judgment")+
  xlab("Model prediction")+
  theme(legend.box = "horizontal",
        panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.line = element_line(colour = "black"),
        #legend.position = "bottom",
        #legend.direction = "horizontal",
        legend.title = element_blank())+
        #legend.position = c(0.57, -0.2))+
  guides(fill=guide_legend(override.aes=list(colour=fill.colors)),
         shape = guide_legend(override.aes= list(colour = 'black')))
        
scatterFig
#ggsave(scatterFig, 
 #      file = paste(talk.fig.path, "model-scatters.pdf"), width = 7, height = 5)

```

### L0 model

```{r cache = T}
n_chains  = 3
n_samples = 100000
burn <- n_samples / 2
m.samp <- data.frame()

file.prefix <- "fbt-L0-empiricalCC-disc3-mcmc"

for (i in seq(1, n_chains)){
  m <- as.data.frame(fread(paste(project.path,
                                 "models/sherlock/results/",
                                 file.prefix, n_samples, "_burn", 
                                 burn, "_chain", 
                                 i, ".csv", sep="")))
  m.samp <- bind_rows(m.samp, m)
  print(i)
}

```

#### Posterior predictives

```{r}
m.pp <- m.samp %>% 
  filter(param %in% c("superCC", "superSpeaker")) %>%
  group_by(param, cat, form) %>%
  summarize( MAP = estimate_mode(val),
             cred_upper = hdi_upper(val),
             cred_lower = hdi_lower(val) )
```

```{r}
md.pp <- left_join(
  bind_rows(vs.bayes %>% 
             mutate(expt = "superSpeaker"),
           df.bayes %>%
             mutate(expt = "superCC")) %>% 
             ungroup() %>%
             rename(cat = sub_category),
  m.pp %>% rename(expt = param)) %>%
  rowwise() %>%
  mutate(
         form = factor(form, levels = c("positive", "negative")),
         MAP = ifelse(expt == "superCC", 1 - MAP, MAP),
         cred_lower = ifelse(expt == "superCC", 1 - cred_lower, cred_lower),
         cred_upper = ifelse(expt == "superCC", 1 - cred_upper, cred_upper),
         degree = factor(degree,
                         levels = c("height", "temperature", "weight",
                                    "time", "price"),
                         labels = c("short / tall","cold / warm",
                                    "light / heavy", "short / long", 
                                    "cheap / expensive" )),
         expt = factor(expt, 
                       levels = c("superCC", "superSpeaker"),
                       labels = c('Experiment 1 \n (Comparison class inference)', ' Experiment 2 \n (Adjective production)'))) 

         
fill.colors <- RColorBrewer::brewer.pal(5, "Set3")
names(fill.colors) <- levels(md.pp$degree)

ggplot(md.pp, aes(x = MAP, xmin = cred_lower, xmax = cred_upper,
                  y = MAP_h, ymin = low, ymax = high,
                  shape = form, fill = degree))+
  geom_abline(intercept = 0, slope = 1, lty = 3,color = 'black')+
  geom_errorbar(size = 0.5, alpha = 0.4, color = 'black')+
  geom_errorbarh(size = 0.5, alpha =0.4, color = 'black')+
  geom_point(size = 2.5, color = 'black')+
  scale_shape_manual(values = c(24, 25))+
  scale_fill_brewer(palette = "Set3")+
  facet_wrap(~expt)+
  coord_fixed(ratio = 1)+
  scale_x_continuous(limits = c(0, 1), breaks = c(0,1))+
  scale_y_continuous(limits = c(0, 1), breaks = c(0,1))+
  ylab("Human judgment")+
  xlab("Model prediction")+
  theme(legend.box = "horizontal",
        panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.line = element_line(colour = "black"),
        #legend.position = "bottom",
        #legend.direction = "horizontal",
        legend.title = element_blank())+
        #legend.position = c(0.57, -0.2))+
  guides(fill=guide_legend(override.aes=list(colour=fill.colors)),
         shape = guide_legend(override.aes= list(colour = 'black')))




# md.pp <- left_join(
#   bind_rows(vs.summary %>% 
#              mutate(expt = "superSpeaker"),
#            ce.summary %>%
#              mutate(expt = "superCC")) %>% 
#              ungroup() %>%
#              rename(cat = sub_category),
#   m.pp %>% rename(expt = param))
# 
# ggplot(md.pp, aes(x = MAP, xmin = cred_lower, xmax = cred_upper,
#                   y = mean, ymin = ci_lower, ymax = ci_upper,
#                   shape = form, color = degree))+
#   geom_abline(intercept = 0, slope = 1, lty = 3)+
#   geom_errorbar()+
#   geom_errorbarh()+
#   geom_point()+
#   facet_wrap(~expt)+
#   coord_fixed(ratio = 1)+
#   xlim(0, 1)+
#   ylim(0, 1)

```


```{r}
print(paste("ccRSA model & cc inference task r^2= ", with(md.pp %>%
       filter(expt == 'Experiment 1 \n (Comparison class inference)'), cor(MAP, MAP_h))^2, sep = ""))

print(paste("adjective s2 & vs task r^2= ", with(md.pp %>%
       filter(expt == ' Experiment 2 \n (Adjective production)'), cor(MAP, MAP_h))^2))
```

### Comparison class inference task

```{r}
md.pp.long <- bind_rows(
  md.pp %>% 
    select(-MAP_h, -low, -high) %>%
    mutate(src = "model"),
  md.pp %>%
    select(-MAP, -cred_lower, -cred_upper) %>%
    rename(MAP = MAP_h, cred_lower = low, cred_upper = high) %>%
    mutate(src = "human")
)

md.pp.long %>%
  ungroup() %>%
  filter(expt == 'Experiment 1 \n (Comparison class inference)') %>%
  mutate(cat = factor(cat, levels = cat[order(strength)])) %>%
  ggplot(., 
         aes( x = cat, 
              y = MAP, ymin = cred_lower, ymax = cred_upper, 
              group = form, fill = form ) )+
  geom_bar(stat = 'identity', position = position_dodge())+
  geom_errorbar(position = position_dodge())+
  facet_grid(src~degree, scales = 'free')+#, nrow = 1)+
  scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1)) + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1) )+
  ylab("Proportion Subordinate response")
```


It looks that the L0 model is making the exact wrong prediction (i.e., the interaction). The L0 model doesn't have a way of separating listener knowledge (i.e., the comparison class used in the listener's degree prior) from speaker's intent (i.e., the comparison class used by the speaker). In our setup, the listener knows the target is a basketball player. The L0 model doens't have a way of knowing this, so it instead just samples a comparison class from the comparison class prior. So when it hears "tall", it thinks "basketball player" is the more likely comparison class.  

Basically, the L0 model is answering "what do you think it is: Basketball player or person"? When it hears "he's tall", L0 thinks "basketball player!"



#### Speaker optimality parameters

```{r}
m.samp %>% 
  filter(cat %in% c("speakerOptimality_s1", "speakerOptimality_s2", "beta")) %>%
  separate(cat, into = c("cat", "speaker")) %>%
  ggplot(., aes(x = val))+
  geom_histogram()+
  facet_wrap(~ param  + speaker, scales = 'free')
```


Prior parameters

```{r}
m.samp %>% filter(param %in% c("mu", "sigma")) %>%
  filter(cat != "") %>%
  ggplot(., aes(x = val))+
  geom_histogram()+
  facet_grid(cat ~ param, scales = 'free')+
    theme_bw()+
  theme(strip.text.y = element_text(angle = 0))
```


```{r}
m.samp %>% filter(param %in% c("mu", "sigma")) %>%
  filter(cat != "") %>%
  group_by(cat, param) %>%
  summarize(MAP = estimate_mode(val),
            cred_upper = hdi_upper(val),
            cred_lower = hdi_lower(val)) %>%
  kable()
```




```{r eval = F}
# What do the priors look like?

left_join(
  m.samp %>% filter(param == "prior"),
  d %>% select(degree, sub_category, strength) %>% unique() %>%
  rename(cat = sub_category)
) %>% 
  mutate(strength = factor(strength, levels = c(1,2,3),
                           labels = c("low", "medium", "high"))
         ) %>%
  ggplot(., aes(x = val, y = ..scaled.., 
                color = strength, fill = strength))+
  geom_density(alpha=0.4)+
  facet_wrap(~degree, scales = 'fixed')+
  xlim(-4, 4)+
  theme_bw()+
  theme(strip.text.y = element_text(angle = 0)) 
```




```{r eval = F}
### Adjective speaker inference task

md.pp.long %>%
  ungroup() %>%
  filter(expt == "superSpeaker") %>%
  mutate(cat = factor(cat, levels = cat[order(strength)])) %>%
  ggplot(., 
         aes( x = cat, 
              y = mean, ymin = ci_lower, ymax = ci_upper, 
              group = form, fill = form ) )+
  geom_bar(stat = 'identity', position = position_dodge())+
  geom_errorbar(position = position_dodge())+
  facet_grid(src~degree, scales = 'free')+#, nrow = 1)+
  ylim(0, 1) + 
  theme(axis.text.x = element_text(angle = 90) )
```

