---
title: "Comparison class models (RSA + BDA)"
author: "M. H. Tessler"
date: "7/21/2017"
output: github_document
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=6, fig.height=4, fig.crop=F, fig.pos="tb", fig.path='figs/', echo=F, warning=F, cache=F, message=F, sanitize=T)
theme_set(theme_few())
```

```{r libraries}
library(tidyverse)
library(tidyboot)
library(coda)
library(knitr)
library(ggrepel)

project.path <- "~/projects/comparison-class/"
options(digits = 7)
estimate_mode <- function(s) {
  d <- density(s)
  return(d$x[which.max(d$y)])
}
hdi_upper<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","upper"])
}
hdi_lower<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","lower"])
}
logistic <- function(x){1 / (1 + exp(-x))}
```

# Behavioral data

```{r}
df.adj <- read_csv("../data/adjective-endorsement-prereg-final/adjective-endorsement-prereg-trials-tidy.csv")
df.cc <- read_csv("../data/class-elicitation-prereg-final/auto-classified-data-w-freqs-final.csv")

bind_rows(
  df.cc %>% 
    rename(val = specific) %>%
    select(workerid, degree, superordinate_pl, NP_sg, adj_polarity, val) %>%
    mutate(task = "comparisonClass"),
  df.adj %>%
    select(workerid, degree, superordinate_pl, NP_sg, adj_polarity, val) %>%
    mutate(
      #adj_polarity = ifelse(adj_polarity == "response_pos", "positive", "negative"),
      superordinate_pl = ifelse(superordinate_pl == "floor materials", "floors", superordinate_pl),
      task = "adjEndorse"
      )
) %>%
  rename(
    subordinate = NP_sg, 
    superordinate = superordinate_pl
  ) -> df.comb
```

```{r}
df.comb %>%
  group_by(degree, superordinate, subordinate, adj_polarity, task) %>%
  tidyboot_mean(column = val) -> df.comb.bs

df.comb.wide <- left_join(
  df.comb.bs %>% ungroup() %>% filter(task == "adjEndorse") %>% 
    select(-task, -empirical_stat, -n) %>%
    rename(adj_mean = mean, adj_lower = ci_lower, adj_upper = ci_upper),
  df.comb.bs %>% ungroup() %>% filter(task == "comparisonClass") %>% 
    select(-task, -empirical_stat, -n) %>%
    rename(cc_mean = mean, cc_lower = ci_lower, cc_upper = ci_upper)
)

df.comb.wide %>% drop_na() -> df.comb.wide

ggplot(df.comb.wide, aes( x = adj_mean, xmin = adj_lower, xmax = adj_upper,
                          y = cc_mean, ymin = cc_lower, ymax = cc_upper))+
  geom_point()+
  geom_errorbarh(alpha = 0.2)+
  geom_linerange(alpha = 0.2)
```

```{r}
with(df.comb.wide, cor.test(adj_mean, cc_mean))
```
### Split-half correlations

```{r}
all_workers <- unique(df.cc$workerid)
n_workers <- length(all_workers)

split_half <- function(){
  sampled_half <- sample(all_workers, size = n_workers/2)

  df.cc %>%
    rename(subordinate = NP_sg, 
         superordinate = superordinate_pl,
         val = specific) %>%
    select(workerid, degree, superordinate, subordinate, adj_polarity, val) %>%
    mutate(split_half = ifelse(workerid %in% sampled_half, "one", "two")) %>%
    group_by(degree, superordinate, subordinate, adj_polarity, split_half) %>%
    summarize(mean_response = mean(val, na.rm = T)) %>%
    spread(split_half, mean_response) %>%
    ungroup() %>%
    summarize(correlation = cor(one, two, use = "pairwise.complete.obs")) %>%
    pull(correlation)
}

split.half.corrs <- replicate(100, split_half())

mean(split.half.corrs)
2* mean(split.half.corrs) / (1 + mean(split.half.corrs))
```


# Model results

### Load main results

```{r load_model_results, cache = T}
m.samp <- data.frame()
n.chains = 1
model.variants = c("global", "intercept_slope")
n_samples = 5000
n_burn = 2500
n_lag = 2
model.prefix <- "results-L1-S1-silenceAlt-silenceCost-corpusFreqCCLogistic_byItem_"

# intercept_slope-mcmc-5000_burn2500_lag2_chain1.csv
# results-L1-S1-silenceAlt-silenceCost-corpusFreqCCLogistic_byItem_global-mcmc-5000_burn2500_lag2_chain1.csv

for (m in model.variants){
  for (i in 1:n.chains){
    model.result.file <- paste("../models/sherlock/results/", model.prefix, m, "-mcmc-", n_samples, "_burn", n_burn, "_lag", n_lag, "_chain", i, ".csv", sep = "")
    
    m.samp.i <- read_csv(model.result.file)
      # paste("../models/sherlock/results/results-L1-S1-silenceAlt-silenceCost-corpusFreqCC-mcmc-500000_burn250000_lag50_chain", i, ".csv", 
      #       sep = "")
      # paste("../models/sherlock/results/results-L1-S1-silenceAlt-silenceCost-subcatWeightBySub-mcmc-250000_burn125000_lag25_chain", i, ".csv",
      #   sep = "")
      # paste("../models/sherlock/results/results-L1-S1-silenceAlt-silenceCost-corpusFreqCCLogistic-mcmc-250000_burn125000_lag25_chain", i, ".csv",
      #   sep = "")

    m.samp <- bind_rows(m.samp, m.samp.i %>% mutate(model_variant = m, chain = i))
  }

}

m.samp.summary <- m.samp %>%
  #filter(degree == "parameter") %>%
  #filter(task == "sub_classprior") %>%
  group_by(model_variant, degree, superordinate, subordinate, task, adj_polarity) %>%
  summarize(MAP = estimate_mode(val),
            cred_upper = hdi_upper(val),
            cred_lower = hdi_lower(val))
```


### Posterior predictive

```{r}

m.samp.summary.predictive <- m.samp.summary %>%
#m.samp.summary.predictive <- m.samp.summary %>%
  filter(task %in% c("adjEndorse", "subordinateCC"))

md.summary <- left_join(
  df.comb.bs %>% 
    mutate(task = ifelse(task == "comparisonClass", 
                         "subordinateCC", 
                         task)),
  m.samp.summary.predictive
)

glimpse(md.summary)

md.summary <- md.summary %>% drop_na()
```

#### Scatterplots

```{r}
ggplot(md.summary, aes( x = MAP, xmin = cred_lower, xmax = cred_upper,
                          y = mean, ymin = ci_lower, ymax = ci_upper))+
  geom_abline(intercept = 0, slope = 1, lty = 3)+
  geom_point()+
  geom_errorbarh(alpha = 0.2)+
  geom_linerange(alpha = 0.2)+
  facet_grid(model_variant~task)+
  scale_x_continuous(limits = c(-0.01, 1.01))+
  scale_y_continuous(limits = c(-0.01, 1.01))+
  coord_fixed()

ggsave("~/projects/comparison-class/models/figs/model_scatters_pilot-corpusFreqCCLogisticSameSlopeByItemSetHeirarchy.png", width = 6, height = 5)
```

```{r}
md.summary %>%
  group_by(model_variant, task) %>%
  summarize(corr = cor(mean, MAP)) %>%
  kable()
```
#### Bar plots

```{r}
md.summary.long <- bind_rows(
  df.comb.bs %>% mutate(task = ifelse(task == "comparisonClass", "subordinateCC", task),
                        src = 'data'),
  m.samp.summary.predictive %>%
    mutate(src = 'model') %>%
    rename(mean = MAP, ci_lower = cred_lower, ci_upper = cred_upper)
)


df.adj.items <- df.adj %>%
  distinct(degree, superordinate_pl, item_sg, item_cond) %>%
  rename(subordinate = item_sg,
         superordinate = superordinate_pl)


md.summary.long %>%
  filter(task == "subordinateCC") %>%
  left_join(., df.adj.items) %>%
  ungroup() %>%
  mutate(item_cond = factor(item_cond,
                               levels = c("negative", "neutral", "positive"),
                               labels = c("low", "medium", "high")),
         subordinate = fct_reorder(subordinate, as.numeric(item_cond))) %>%
  ggplot(., 
       aes( x = subordinate, y = mean, 
            ymin = ci_lower, ymax = ci_upper, fill = adj_polarity))+  
  geom_col(position = position_dodge(0.8), width = 0.8, alpha = 0.7, color = 'black')+
  geom_linerange(position = position_dodge(0.8), color = 'black')+  
  scale_fill_brewer(palette = "Set3")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1.0, vjust = 1),
        #axis.title.x = element_blank(),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.line = element_line(colour = "black"))+
  facet_wrap(~degree + superordinate + src, scales = 'free', nrow = 4)+
 # theme_black()+
  scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
  ylab("Proportion paraphrases that contain NP")+
  xlab("Subordinate Category Prior Mean")

ggsave("../models/figs/bars_cc_finalExpt_pilot_byItem_wModel_corpusFreqCCLogisticSameSlopeByItemSetHeirarchy.png",
       width = 17, height = 9)
```


#### Residual analysis


```{r}
md.sum.sqErr <- md.summary %>% 
  filter(task == "subordinateCC") %>%
  group_by(degree, superordinate) %>%
  summarize(model_sSqErr = sum( (mean-MAP) ^ 2))
```


### Parameter posterior


Summarize all parameters

```{r}
m.samp.summary <- m.samp %>%
  group_by(model_variant, degree, superordinate, subordinate, task, adj_polarity) %>%
  summarize(MAP = estimate_mode(val),
            cred_upper = hdi_upper(val),
            cred_lower = hdi_lower(val))
```


#### Global parameters 

```{r}
m.samp.summary %>%
  filter(degree == "parameter") %>%
  select(-degree, -adj_polarity) %>%
  kable()
```


```{r}
m.samp %>%
#m.samp.simple %>%
  filter(degree == "parameter") %>%
  mutate(param = paste(superordinate, subordinate, task)) %>%
  ggplot(., aes( x = val, fill = factor(chain) ))+
  geom_histogram()+
  facet_grid(model_variant ~ param, 
             scales = 'free')

ggsave("~/projects/comparison-class/models/figs/model_parameters_pilot-corpusFreqCCLogisticSameSlopeByItemSetHeirarchy.png", width = 8, height = 6)
```



#### Comparison class priors

item-wise free parameter version: by-item subclass prior  vs. global estimate


```{r}
m.fitted.subclassprior.freq <- m.samp.summary %>%
  filter(task == "sub_classprior", model_variant != "global") %>% 
  left_join(., m.samp.summary %>%
                filter(task == "sub_classprior", model_variant == "global") %>%
              rename(global_MAP = MAP, global_lower = cred_lower, global_upper = cred_upper) %>%
              ungroup() %>%
              select(-model_variant)) %>%
  mutate(sqErr = (MAP - global_MAP)^2)


m.fitted.subclassprior.freq %>%
  ungroup() %>%
  select(degree, superordinate, subordinate, MAP, global_MAP, sqErr) %>%
  View()

m.fitted.subclassprior.freq %>%
  ggplot(., aes (y = MAP, ymin = cred_lower, ymax = cred_upper,
                 x = global_MAP, xmin = global_lower, xmax = global_upper))+
  geom_point()+
  geom_errorbar(alpha = 0.3) + geom_errorbarh(alpha = 0.3)s

# ggsave("~/projects/comparison-class/models/figs/cc_prior_fitted_vs_freq.png", 
#        width = 4, height = 5)
```

Average over subordinates with superordinate

```{r}
m.fitted.subclassprior.freq %>%
  ungroup() %>%
  select(degree, superordinate, subordinate, MAP, global_MAP, sqErr) %>%
  group_by(degree, superordinate) %>%
  summarize(fitted = mean(MAP),
            freq = mean(global_MAP),
            sse = sum(sqErr)) %>%
  View()

m.fitted.subclassprior.freq %>%
  ungroup() %>%
  select(degree, superordinate, subordinate, MAP, cred_lower, cred_upper, global_MAP, global_lower, global_upper, sqErr) %>%
  group_by(degree, superordinate) %>%
  summarize(fitted = mean(MAP), 
            fitted_lower = mean(cred_lower), 
            fitted_upper = mean(cred_upper),
            freq = mean(global_MAP), 
            freq_lower = mean(global_lower), 
            freq_upper = mean(global_upper),
            sse = sum(sqErr)) %>%
  mutate(item_set = paste(superordinate, '(', degree,  ')', sep ="")) -> m.fitted.subclassprior.itemset.freq
  
  
ggplot(m.fitted.subclassprior.itemset.freq, 
       aes (y = fitted, ymin = fitted_lower, ymax = fitted_upper,
                 x = freq, xmin = freq_lower, xmax = freq_upper,
                 label = item_set))+
  geom_point()+
  geom_text_repel(size = 2)+
  geom_vline(xintercept = 0.5, lty = 3)+
  geom_errorbar(alpha = 0.3) + geom_errorbarh(alpha = 0.3)+
  labs(x = "Frequency constrained cc prior", y = "Unconstrained inferred cc prior",
       title = "point = item set average (3 subordinates w/ superordinate)")

ggsave("~/projects/comparison-class/models/figs/cc_prior_fitted_vs_freq_itemSet.png", 
       width = 8, height = 5)
```


##### Item_set_hiearchy

```{r}
m.samp.simple.item_set <- m.samp %>%
    filter(subordinate == "item_set_heirarchy") %>%
    group_by(model_variant, degree, superordinate, task) %>%
    summarize(n = mean(val))


m.samp.simple.item_set %>%
  ungroup() %>%
  mutate(item = paste(superordinate, degree, sep = "-")) %>%
  mutate(item = factor(item, levels =  item[order(n)])) %>%
  ggplot(., aes(x = item, y = n))+
  geom_col()+
  labs(y = "probability of subordinate vs. basic relation")+
  coord_flip()+
  facet_wrap(~model_variant)

ggsave("~/projects/comparison-class/models/figs/model_pilot-ItemSetHeirarchy.png", width = 5, height = 5)
```




Relative frequencies

```{r}
df.cc.freq.ave <- df.cc %>%
  rename(subordinate = NP, adj_polarity = adj_positiveness, val = specific) %>%
  #distinct(degree, superordinate, NP,subFreq, superFreq) %>%
  mutate(norm_freq = 0.1*log(subFreq) / (0.1*log(subFreq) + 0.1*log(superFreq)),
         exp_ratio = exp(subFreq / superFreq)) %>%
  group_by(degree, superordinate, subordinate) %>%
  summarize(mean_sub = mean(val),
            norm_freq = mean(norm_freq),
            sqErr = (mean_sub - norm_freq)^2)

df.cc.freq.ave.sum <- df.cc.freq.ave %>%
  ungroup() %>%
  group_by(degree, superordinate) %>%
  summarize(
    mean_norm_freq = mean(norm_freq),
    mean_cc_sub = mean(mean_sub),
    freq_sSqErr = sum(sqErr))

md.sum.sqErr.freq <- left_join(md.sum.sqErr, df.cc.freq.ave.sum) %>%
  mutate(err = freq_sSqErr - model_sSqErr)

ggplot(md.sum.sqErr.freq, aes( x = freq_sSqErr, y = model_sSqErr))+
  geom_point()
```






