---
title: "Comparison class models (RSA + BDA)"
author: "M. H. Tessler"
date: "7/21/2017"
output: github_document
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=6, fig.height=4, fig.crop=F, fig.pos="tb", fig.path='figs/', echo=F, warning=F, cache=F, message=F, sanitize=T)
```

```{r libraries}
library(tidyverse)
library(tidyboot)
library(coda)
library(knitr)
library(ggrepel)
library(ggthemes)
theme_set(theme_few())

project.path <- "~/projects/comparison-class/"
options(digits = 7)
estimate_mode <- function(s) {
  d <- density(s)
  return(d$x[which.max(d$y)])
}
hdi_upper<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","upper"])
}
hdi_lower<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","lower"])
}
logistic <- function(x){1 / (1 + exp(-x))}
```

# Behavioral data

```{r}
df.adj <- read_csv("../data/adjective-endorsement-prereg-final/adjective-endorsement-prereg-trials-w-freqs.csv")
# df.adj <- read_csv("../data/adjective-endorsement-prereg-final/adjective-endorsement-prereg-trials-tidy.csv")
# df.cc <- read_csv("../data/class-elicitation-prereg-final/auto-classified-data-w-freqs-final.csv")
#df.cc <- read_csv("../data/class-elicitation-prereg-final/full-classified-data-w-produced-super.csv")
## df.cc <- read_csv("../data/class-elicitation-prereg-final/full-classified-data-w-freqs.csv")
df.cc <- read_csv("../data/class-elicitation-prereg-final/full-classified-data-w-freqs-no-failedRef.csv")

bind_rows(
  df.cc %>% 
    rename(val = specific) %>%
    select(workerid, stim_id, degree, superordinate_pl, NP_sg, np_expectations, adj_polarity, val, subFreq, superFreq) %>%
    mutate(task = "comparisonClass"),
  df.adj %>%
    select(workerid, stim_id, degree, superordinate_pl, NP_sg, np_expectations, adj_polarity, val, subFreq, superFreq) %>%
    mutate(
      #adj_polarity = ifelse(adj_polarity == "response_pos", "positive", "negative"),
      superordinate_pl = ifelse(superordinate_pl == "floor materials", "floors", superordinate_pl),
      task = "adjEndorse"
      )
) %>%
  rename(
    subordinate = NP_sg, 
    superordinate = superordinate_pl
  ) -> df.comb
```

```{r}
df.cc %>%
  #filter(stim_id == 90) %>%
  group_by(stim_id, np_expectations, NP_sg, adj_polarity) %>%
  count() %>%#, NP_sg == "adult")
  filter(n < 35)
```


```{r}
df.comb %>%
  filter(task == "comparisonClass") %>%
  group_by(stim_id, subordinate, adj_polarity) %>%
  tidyboot_mean(column = val) -> df.cc.bs

df.comb %>%
  filter(task == "adjEndorse") %>%
  group_by(stim_id, subordinate, adj_polarity) %>%
  tidyboot_mean(column = val) -> df.adj.bs

bind_rows(
  df.cc.bs %>%
    mutate(task = "comparisonClass"), 
  df.adj.bs %>%
    mutate(task = "adjEndorse")
) %>%
  left_join(., 
            df.comb %>% distinct(degree, stim_id, superordinate, subordinate, adj_polarity, np_expectations, subFreq, superFreq)) -> df.comb.bs

df.comb.wide <- left_join(
  df.comb.bs %>% ungroup() %>% filter(task == "adjEndorse") %>%
    select(-task, -empirical_stat, -n) %>%
    rename(adj_mean = mean, adj_lower = ci_lower, adj_upper = ci_upper),
  df.comb.bs %>% ungroup() %>% filter(task == "comparisonClass") %>%
    select(-task, -empirical_stat, -n) %>%
    rename(cc_mean = mean, cc_lower = ci_lower, cc_upper = ci_upper)
)

# save(df.comb, df.comb.wide, file = "cached_results/cc-adj-combined-bootstrapped.RData")
# load("cached_results/cc-adj-combined-bootstrapped.RData") # df.comb, df.comb.wide

ggplot(df.comb.wide, aes( x = adj_mean, xmin = adj_lower, xmax = adj_upper,
                          y = cc_mean, ymin = cc_lower, ymax = cc_upper))+
  geom_point()+
  geom_errorbarh(alpha = 0.2)+
  geom_linerange(alpha = 0.2)
```


```{r}
with(df.comb.wide, cor.test(adj_mean, cc_mean))
```
### Split-half correlations

```{r}
all_workers <- unique(df.cc$workerid)
n_workers <- length(all_workers)

split_half <- function(){
  sampled_half <- sample(all_workers, size = n_workers/2)

  df.cc %>%
    rename(subordinate = NP_sg, 
         superordinate = superordinate_pl,
         val = specific) %>%
    select(workerid, degree, superordinate, subordinate, adj_polarity, val) %>%
    mutate(split_half = ifelse(workerid %in% sampled_half, "one", "two")) %>%
    group_by(degree, superordinate, subordinate, adj_polarity, split_half) %>%
    summarize(mean_response = mean(val, na.rm = T)) %>%
    spread(split_half, mean_response) %>%
    ungroup() %>%
    summarize(correlation = cor(one, two, use = "pairwise.complete.obs")) %>%
    pull(correlation)
}

split.half.corrs <- replicate(100, split_half())

mean(split.half.corrs)
2* mean(split.half.corrs) / (1 + mean(split.half.corrs))
```


# Model results

### Load main results

```{r load_model_results, cache = T}
m.samp <- data.frame()
n.chains = 3
# model.variants = c("global", "intercept", "intercept_slope", "slope")
# model.variants = c("slope", "intercept_slope")
 model.variants = c("flat", "intercept", "intercept_slope", "slope")
# model.variants <- c("byItemSet_intercept_slope", "byNP_intercept_slope")
n_samples = 300000
n_burn = n_samples / 2
n_lag = 150
# model.prefix <- "results-L1-S1-silenceAlt-silenceCost-corpusFreqCCLogistic_byItem_"
# model.prefix <- "results-L1-S1-silenceAlt-sansSilence-corpusFreqCCLogistic_byItem_"
#model.prefix <- "results-L1-S1-fullClassified-sansSilence-corpusFreqCCLogistic_"
#model.prefix <- "results-L1-S1-fullClassified-sansSilence-corpusFreqCCLogistic_byNP_"
model.prefix <- "results-L1-S1-fullClassifiedOneSuperNoRefFail-sansSilence-corpusFreqCCLogistic_byNP_"

for (m in model.variants){
  for (i in 1:n.chains){
    model.result.file <- paste("../models/sherlock/results/", model.prefix, m, "-mcmc-", 
                               format(n_samples, scientific = F), "_burn", 
                               format(n_burn, scientific = F), "_lag", n_lag, "_chain", i, ".csv", sep = "")
    
    m.samp.i <- read_csv(model.result.file)
      # paste("../models/sherlock/results/results-L1-S1-silenceAlt-silenceCost-corpusFreqCC-mcmc-500000_burn250000_lag50_chain", i, ".csv", 
      #       sep = "")
      # paste("../models/sherlock/results/results-L1-S1-silenceAlt-silenceCost-subcatWeightBySub-mcmc-250000_burn125000_lag25_chain", i, ".csv",
      #   sep = "")
      # paste("../models/sherlock/results/results-L1-S1-silenceAlt-silenceCost-corpusFreqCCLogistic-mcmc-250000_burn125000_lag25_chain", i, ".csv",
      #   sep = "")

    m.samp <- bind_rows(m.samp, m.samp.i %>% mutate(model_variant = m, chain = i))
  }

}

# m.samp.single <- read_csv("../models/sherlock/results/results-L1-S1-fullClassified-sansSilence-corpusFreqCCLogistic_byNP_intercept_slope-mcmc-100_burn50_lag1_chain1.csv")

m.samp.summary <- m.samp %>%
  #filter(!(model_variant == "slope_intercept" && chain == 1)) %>%
  #filter(degree == "parameter") %>%
  #filter(task == "sub_classprior") %>%
  #group_by(model_variant, degree, superordinate, subordinate, task, adj_polarity) %>%
  group_by(model_variant, stim_id, subordinate, task, adj_polarity) %>%
  summarize(MAP = estimate_mode(val),
            cred_upper = hdi_upper(val),
            cred_lower = hdi_lower(val))

m.samp.summary.chain <- m.samp %>%
  #filter(!(model_variant == "slope_intercept" && chain == 1)) %>%
  #filter(degree == "parameter") %>%
  #filter(task == "sub_classprior") %>%
  group_by(model_variant, stim_id, subordinate, task, adj_polarity, chain) %>%
  # group_by(model_variant, degree, superordinate, subordinate, task, adj_polarity, chain) %>%
  summarize(MAP = estimate_mode(val),
            cred_upper = hdi_upper(val),
            cred_lower = hdi_lower(val))
```


### Posterior predictive

```{r}

m.samp.summary.predictive <- m.samp.summary %>% mutate(chain = "collapsed") %>%
# m.samp.summary.predictive <- m.samp.summary.chain %>%
  filter(task %in% c("adjEndorse", "subordinateCC"))



md.summary <- right_join(
df.comb.bs %>%
  ungroup() %>%
  mutate(stim_id = paste("stim_", stim_id, sep = "")) %>%
    mutate(task = ifelse(task == "comparisonClass", 
                         "subordinateCC", 
                         task)),
  m.samp.summary.predictive
)

glimpse(md.summary)

# md.summary <- md.summary %>% drop_na()
```

#### Scatterplots

```{r}
md.summary %>%
  ungroup() %>%
  mutate(model_variant = factor(model_variant, levels = c("flat", "intercept", "slope", "intercept_slope"),
                                labels = c("Flat Prior", "Basic-level bias", "Frequency effect", "Basic-level bias\n and Frequency effect")),
         task = factor(task, levels = c("subordinateCC", "adjEndorse"),
                       labels = c("Comparison Class Inference\n(Experiment 2)",
                                  "Adjective Endorsement\n(Experiment 3)"))) %>%
ggplot(., aes( x = MAP, xmin = cred_lower, xmax = cred_upper,
                          y = mean, ymin = ci_lower, ymax = ci_upper))+
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 0.6)+
  geom_point(alpha = 0.3)+
  geom_errorbarh(alpha = 0.1)+
  geom_linerange(alpha = 0.1)+
  facet_grid(task ~ model_variant)+
  scale_x_continuous(limits = c(-0.01, 1.01), breaks = c(0, 1))+
  scale_y_continuous(limits = c(-0.01, 1.01), breaks = c(0, 1))+
  theme(strip.text.y = element_text(angle = 0))+
  coord_fixed()+
  labs(y = "Human Judgment", x = "Model Prediction")

#ggsave("~/projects/comparison-class/models/figs/model_scatters_pilot-corpusFreqCCLogisticSameSlopeByItemSetHeirarchy.png", width = 6, height = 5)
ggsave("../writing/paper/figs/model_scatters_modelVariants.pdf", width = 8, height = 5)
```

```{r}
md.summary %>%
  group_by(model_variant, task, chain) %>%
  summarize(
    r = cor(mean, MAP),
    r2 = cor(mean, MAP) ^ 2
    ) -> md.predictive.stats

md.predictive.stats %>%
  kable()
```
#### Bar plots

```{r}
md.summary.long <- bind_rows(
  df.comb.bs %>% mutate(task = ifelse(task == "comparisonClass", "subordinateCC", task),
                        src = 'data'),
  m.samp.summary.predictive %>%
    mutate(src = 'model') %>%
    rename(mean = MAP, ci_lower = cred_lower, ci_upper = cred_upper)
)


df.adj.items <- df.adj %>%
  distinct(degree, superordinate_pl, item_sg, item_cond) %>%
  rename(subordinate = item_sg,
         superordinate = superordinate_pl)


md.summary.long %>%
  filter(task == "subordinateCC") %>%
  left_join(., df.adj.items) %>%
  ungroup() %>%
  mutate(item_cond = factor(item_cond,
                               levels = c("negative", "neutral", "positive"),
                               labels = c("low", "medium", "high")),
         subordinate = fct_reorder(subordinate, as.numeric(item_cond))) %>%
  ggplot(., 
       aes( x = subordinate, y = mean, 
            ymin = ci_lower, ymax = ci_upper, fill = adj_polarity))+  
  geom_col(position = position_dodge(0.8), width = 0.8, alpha = 0.7, color = 'black')+
  geom_linerange(position = position_dodge(0.8), color = 'black')+  
  scale_fill_brewer(palette = "Set3")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1.0, vjust = 1),
        #axis.title.x = element_blank(),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.line = element_line(colour = "black"))+
  facet_wrap(~degree + superordinate + src, scales = 'free', nrow = 4)+
 # theme_black()+
  scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
  ylab("Proportion paraphrases that contain NP")+
  xlab("Subordinate Category Prior Mean")

ggsave("../models/figs/bars_cc_finalExpt_pilot_byItem_wModel_corpusFreqCCLogisticSameSlopeByItemSetHeirarchy.png",
       width = 17, height = 9)
```


#### Residual analysis


```{r}
md.sum.sqErr <- md.summary %>% 
  filter(task == "subordinateCC", model_variant == "intercept_slope") %>%
  group_by(stim_id, degree, superordinate) %>%
  summarize(model_sSqErr = sum( (mean-MAP) ^ 2))


bind_rows(
  md.sum.sqErr[with(md.sum.sqErr, order(-model_sSqErr)),] %>% 
  head(6),
  # md.sum.sqErr[with(md.sum.sqErr, order(-model_sSqErr)),] %>% 
  # tail(5)
) %>%
  distinct(stim_id, degree, superordinate) -> df.max.err
```

```{r}
md.summary.long <- bind_rows(
  df.comb.bs %>% 
      ungroup() %>%
    mutate(stim_id = paste("stim_", stim_id, sep = "")) %>%
    mutate(task = ifelse(task == "comparisonClass", "subordinateCC", task),
                        src = 'data') %>%
    select(-n, -empirical_stat),
  md.summary %>%
    filter(model_variant == "intercept_slope") %>%
    rename(src = model_variant) %>%
    select(stim_id, src, subordinate, adj_polarity, cred_lower, cred_upper, MAP, task, degree, superordinate, np_expectations, subFreq, superFreq) %>%
    # mutate(src = 'model') %>%
    rename(mean = MAP, ci_lower = cred_lower, ci_upper = cred_upper)
)


# df.adj.items <- df.adj %>%
#   distinct(degree, superordinate_pl, item_sg, item_cond) %>%
#   rename(subordinate = item_sg,
#          superordinate = superordinate_pl)


fig.residuals <- md.summary.long %>%
  inner_join(., df.max.err) %>%
  ungroup() %>%
  filter(task == "subordinateCC") %>%
  # left_join(., df.adj.items) %>%
  # ungroup() %>%
  mutate(np_expectations = factor(np_expectations,
                               levels = c("low", "medium", "high"),
                               labels = c("low", "medium", "high")),
         log_ratio = log(subFreq / superFreq),
         unique_id = paste(superordinate, " (", degree,")", sep = ""),
         subordinate_freq = paste(subordinate, "\n[", as.character(round(log_ratio, 1)), "]", sep = ""),
         src = factor(src, levels = c("intercept_slope", "data"),
                      labels = c("Model Prediction \n(w/ basic-level and  \nfrequency effects)",
                                 "Human Data"))) %>%
  mutate(subordinate_freq = factor(subordinate_freq)) %>%
  mutate(subordinate_freq = fct_reorder(subordinate_freq, as.numeric(np_expectations))) %>%
  ggplot(., 
       aes( x = subordinate_freq, y = mean, 
            ymin = ci_lower, ymax = ci_upper, fill = adj_polarity))+  
  geom_col(position = position_dodge(0.8), width = 0.8, alpha = 0.7, color = 'black')+
  geom_linerange(position = position_dodge(0.8), color = 'black')+  
  scale_fill_brewer(palette = "Set3")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1.0, vjust = 1),
        #axis.title.x = element_blank(),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.line = element_line(colour = "black"),
        strip.text.y = element_text(angle = 0),
        legend.position = 'bottom')+
  facet_grid(src ~ unique_id, scales = 'free')+
 # theme_black()+
  scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
  ylab("Proportion Specific-NP Comparison Class")+
  xlab("Specific NP Category")+
  guides(fill = guide_legend(title = "Adjective polarity", reverse = T))

ggsave(fig.residuals, 
       filename = "../writing/paper/figs/bars_ccinfOnly_finalExpt_byNP_topResdiuals_intercept_slope_300k.pdf",
       width = 10, height = 4.6)
```

```{r}
fig.residuals
```


### Parameter posterior


Summarize all parameters

```{r}
m.samp.summary <- m.samp %>%
  #group_by(model_variant, degree, superordinate, subordinate, task, adj_polarity) %>%
  group_by(model_variant, stim_id, subordinate, task, adj_polarity) %>%
  summarize(MAP = estimate_mode(val),
            cred_upper = hdi_upper(val),
            cred_lower = hdi_lower(val))
```


#### Global parameters 

```{r}
m.samp.summary %>%
  #filter(degree == "parameter") %>%
  filter(stim_id %in% c("beta", "speakerOptimality")) %>%
  #select(-degree, -adj_polarity) %>%
  kable()
```


```{r}
m.samp %>%
  #filter(degree == "parameter") %>%
  filter(stim_id %in% c("beta", "speakerOptimality")) %>%
  #mutate(param = paste(superordinate, subordinate, task)) %>%
  mutate(param = paste(stim_id, subordinate, task)) %>%
  ggplot(., aes( x = val, fill = factor(chain) ))+
  geom_histogram()+
  facet_grid(model_variant ~ param, 
             scales = 'free')

# ggsave("~/projects/comparison-class/models/figs/model_parameters_pilot-corpusFreqCCLogisticSameSlopeByItemSetHeirarchy.png", width = 8, height = 6)
```

Notes
- from the "auto" classified data
  - 300k: slope and slope_intercept
    - slope_intercept gets stronger correlation (r2 = 0.77, vs 0.70; 0.77 is comparable to "intercept" only model with 150k samples)
    - for slope_intercept:
      - one intercept ~ 2; other intercept ~ 0 (though 1 chain with both around 1)
      - slopes small, b1 ~ 0.2, b1a ~ 0.1 (though 1 chain with 0.3, -0.1)
      
Notes
- from the "full" classified data
  - 300k: slope_intercept, by item_set or by NP
    - by item_set, fit goes up to r2 = 0.8
    - by NP, r2 = 0.86
    
    
Notes
- from the "full-classified-data-w-freqs-no-failedRef.csv"
  - the inferred beta weight for frequency looks to be the same for the two sets of items
    - TO RUN: model with single beta_freq and two beta_ints


Check to see if parameters that should have the same value are indeed the same.

```{r param check}
m.samp %>%
  filter(degree == "parameter", model_variant == "slope", subordinate == "frequency") %>%
  spread(task, val) %>% 
  mutate(param_diff = basic_super - sub_basic) %>%
  summarize(mean(param_diff))
```


#### Comparison class priors

item-wise free parameter version: by-item subclass prior  vs. global estimate


```{r}
m.fitted.subclassprior.freq <- m.samp.summary %>%
  filter(task == "sub_classprior", model_variant != "global") %>% 
  left_join(., m.samp.summary %>%
                filter(task == "sub_classprior", model_variant == "global") %>%
              rename(global_MAP = MAP, global_lower = cred_lower, global_upper = cred_upper) %>%
              ungroup() %>%
              select(-model_variant)) %>%
  mutate(sqErr = (MAP - global_MAP)^2)


m.fitted.subclassprior.freq %>%
  ungroup() %>%
  select(degree, superordinate, subordinate, MAP, global_MAP, sqErr) %>%
  View()

m.fitted.subclassprior.freq %>%
  ggplot(., aes (y = MAP, ymin = cred_lower, ymax = cred_upper,
                 x = global_MAP, xmin = global_lower, xmax = global_upper))+
  geom_point()+
  facet_wrap(~model_variant)+
  geom_errorbar(alpha = 0.3) + geom_errorbarh(alpha = 0.3)

# ggsave("~/projects/comparison-class/models/figs/cc_prior_fitted_vs_freq.png", 
#        width = 4, height = 5)
```

Average over subordinates with superordinate

```{r}
m.fitted.subclassprior.freq %>%
  ungroup() %>%
  select(degree, superordinate, subordinate, MAP, global_MAP, sqErr) %>%
  group_by(degree, superordinate) %>%
  summarize(fitted = mean(MAP),
            freq = mean(global_MAP),
            sse = sum(sqErr)) %>%
  View()

m.fitted.subclassprior.freq %>%
  ungroup() %>%
  select(degree, superordinate, subordinate, MAP, cred_lower, cred_upper, global_MAP, global_lower, global_upper, sqErr) %>%
  group_by(degree, superordinate) %>%
  summarize(fitted = mean(MAP), 
            fitted_lower = mean(cred_lower), 
            fitted_upper = mean(cred_upper),
            freq = mean(global_MAP), 
            freq_lower = mean(global_lower), 
            freq_upper = mean(global_upper),
            sse = sum(sqErr)) %>%
  mutate(item_set = paste(superordinate, '(', degree,  ')', sep ="")) -> m.fitted.subclassprior.itemset.freq
  
  
ggplot(m.fitted.subclassprior.itemset.freq, 
       aes (y = fitted, ymin = fitted_lower, ymax = fitted_upper,
                 x = freq, xmin = freq_lower, xmax = freq_upper,
                 label = item_set))+
  geom_point()+
  geom_text_repel(size = 2)+
  geom_vline(xintercept = 0.5, lty = 3)+
  geom_errorbar(alpha = 0.3) + geom_errorbarh(alpha = 0.3)+
  labs(x = "Frequency constrained cc prior", y = "Unconstrained inferred cc prior",
       title = "point = item set average (3 subordinates w/ superordinate)")

ggsave("~/projects/comparison-class/models/figs/cc_prior_fitted_vs_freq_itemSet.png", 
       width = 8, height = 5)
```


##### Item_set_hiearchy

```{r}
m.samp.simple.item_set <- m.samp %>%
    filter(subordinate == "item_set_heirarchy") %>%
    group_by(model_variant, degree, superordinate, task) %>%
    summarize(n = mean(val))


m.samp.simple.item_set %>%
  ungroup() %>%
  mutate(item = paste(superordinate, degree, sep = "-")) %>%
  mutate(item = factor(item, levels =  item[order(n)])) %>%
  ggplot(., aes(x = item, y = n))+
  geom_col()+
  labs(y = "probability of subordinate vs. basic relation")+
  coord_flip()+
  facet_wrap(~model_variant)

ggsave("~/projects/comparison-class/models/figs/model_pilot-ItemSetHeirarchy.png", width = 5, height = 5)
```




Relative frequencies

```{r}
df.cc.freq.ave <- df.cc %>%
  rename(subordinate = NP, adj_polarity = adj_positiveness, val = specific) %>%
  #distinct(degree, superordinate, NP,subFreq, superFreq) %>%
  mutate(norm_freq = 0.1*log(subFreq) / (0.1*log(subFreq) + 0.1*log(superFreq)),
         exp_ratio = exp(subFreq / superFreq)) %>%
  group_by(degree, superordinate, subordinate) %>%
  summarize(mean_sub = mean(val),
            norm_freq = mean(norm_freq),
            sqErr = (mean_sub - norm_freq)^2)

df.cc.freq.ave.sum <- df.cc.freq.ave %>%
  ungroup() %>%
  group_by(degree, superordinate) %>%
  summarize(
    mean_norm_freq = mean(norm_freq),
    mean_cc_sub = mean(mean_sub),
    freq_sSqErr = sum(sqErr))

md.sum.sqErr.freq <- left_join(md.sum.sqErr, df.cc.freq.ave.sum) %>%
  mutate(err = freq_sSqErr - model_sSqErr)

ggplot(md.sum.sqErr.freq, aes( x = freq_sSqErr, y = model_sSqErr))+
  geom_point()
```




# Bayes Factors

```{r}
m.ais <- data.frame()
ais.n.chains = 3
model.variants = c("flat", "intercept", "intercept_slope", "slope")
n_steps = 30000
ais.model.prefix <- "ais-L1-S1-fullClassifiedOneSuperNoRefFail-sansSilence-corpusFreqCCLogistic_byNP_"

for (m in model.variants){
  for (i in 1:n.chains){
    model.result.file <- paste("../models/sherlock/results/marginal-likelihood/", ais.model.prefix, m, "-steps-", 
                               format(n_steps, scientific = F), "_iter", i, ".csv", sep = "")
    
    m.ais.i <- read_csv(model.result.file, col_names = F)

    m.ais <- bind_rows(m.ais, m.ais.i %>% mutate(model_variant = m, chain = i))
  }
}

m.ais %>%
    group_by(model_variant) %>%
    summarize(mll = mean(X1)) -> m.ais.mean

cbind(
  m.ais.mean,
  m.ais.mean %>%
    filter(model_variant == "intercept_slope") %>%
    rename(is_mll = mll) %>% select(-model_variant)
  ) %>%
  mutate(log_bf = mll - is_mll) %>%
  select(model_variant, log_bf) -> m.ais.bf
```


```{r}

md.predictive.stats # from above


left_join(
  md.predictive.stats %>%
    select(-chain, -r) %>%
    ungroup() %>%
    mutate(task = factor(task, levels = c("subordinateCC", "adjEndorse"))) %>%
    spread(task, r2),
    m.ais.bf
  ) -> md.predictive.stats.bf

md.predictive.stats.bf[with(md.predictive.stats.bf, order(log_bf)), ] %>%
  mutate(model_variant = factor(model_variant, levels = c("flat", "slope", "intercept", "intercept_slope"),
                                labels = c("Flat Prior", "Frequency effect", "Basic-level bias",
                                           "Basic-level bias\nand Frequency effect "))) %>%
  rename(Model = model_variant, "$r^2$ Comparison Class Inference\n(Experiment 2)" = subordinateCC,
         "$r^2$ Adjective Endorsement\n(Experiment 3)" = adjEndorse,
         "Log BF" = log_bf) %>%
  kable(.)

md.predictive.stats.bf[with(md.predictive.stats.bf, order(log_bf)), ] %>%
  mutate(model_variant = factor(model_variant, levels = c("flat", "slope", "intercept", "intercept_slope"),
                                labels = c("Flat Prior", "Frequency effect", "Basic-level bias",
                                           "Basic-level and Frequency"))) %>%
  # rename(Model = model_variant, "$r^2$ Comparison Class Inference\n(Experiment 2)" = subordinateCC,
  #        "$r^2$ Adjective Endorsement\n(Experiment 3)" = adjEndorse,
  #        "Log BF" = log_bf) %>%
  write_csv(., path = "../writing/paper/csv_data_4_tex/bf_r2_table.csv")

```


